---
title: "Normative modeling in Schizophrenia - Analysis"
author: "Noemi González Lois"
date: "`r Sys.Date()`"
output:
  pdf_document: default
  html_document: default
---

```{r setup I, include=F}
knitr::opts_chunk$set(
  include = TRUE,  
  echo=TRUE, 
  eval=TRUE, 
  warning=TRUE, 
  message = TRUE,
  cache = FALSE,
  fig.width = 12,
  fig.height = 8
  )
```

### Packages and libraries

We get a list of all the needed packages, then we load them all and also get the number of cores available in PC.

```{r, warning=F, message = F}

library("easypackages")

list.of.packages <- c("viridis", "tidyverse", "MatchIt", "grid", "png", 
                      "gridExtra", "parallel", "nlme", "JMbayes", "plyr",
                      "BiocManager", "Biostrings", "lme4", "ggplot2", "dplyr",
                      "Hmisc", "devtools", "longCombat", "neuroCombat", 
                      "tinytex", "knitr", "ggExtra", "variancePartition",
                      "Rmisc", "doParallel", "hrbrthemes", "cowplot")

new.packages <- list.of.packages[!(list.of.packages %in%
                                     installed.packages()[,"Package"])]
  if(length(new.packages)>0) { install.packages(new.packages)}

libraries(list.of.packages)
ncores <- detectCores()
rm(list.of.packages, new.packages)
```


```{r, eval = FALSE, include = FALSE}
install_github("jcbeer/longCombat")
install_github("jfortin1/neuroCombatData")
install_github("jfortin1/neuroCombat_Rpackage")
BiocManager::install("Biostrings")
BiocManager::install("variancePartition")
install_version("dplyr", version = "1.0.5", repos = "http://cran.us.r-project.org")
tinytex::install_tinytex()

install.packages("dplyr")           # Install dplyr package
library("dplyr")                    # Load dplyr package
```

### Set working directory and load functions

```{r, warning=F, message = F}
setwd("/data_J/Scripts")
source("1_DataPreparation.R")
source("2_RegressionModel.R")
source("3_Statistics.R")
source("4_EDA.R")
```

# Data preparation

```{r, warning = F, message = F}
df_lC_NO_matched <- DataPreparation(parc = "parc35",
                                    harmonization = "lC",
                                    match = F)

df_lC_matched <- DataPreparation(parc = "parc35",
                                 harmonization = "lC",
                                 match = T)
```
# Exploratory Data Analysis

```{r echo=FALSE, message=FALSE, warning=FALSE}

# NO MATCHED
male.df        <- subset(df_lC_NO_matched, scode==0)
male.pat.age   <- subset(male.df, dcode==1)$age
male.con.age   <- subset(male.df, dcode==0)$age
female.df        <- subset(df_lC_NO_matched, scode==1)
female.pat.age   <- subset(male.df, dcode==1)$age
female.con.age   <- subset(male.df, dcode==0)$age

data1 <- data.frame(
  name=c( rep("Male pat",length(male.pat.age)), 
          rep("Female pat",length(female.pat.age)), 
          rep("Male hc",length(male.con.age)), 
          rep("Female hc",length(female.con.age))),
  value=c(male.pat.age, female.pat.age,
          male.con.age, female.con.age))

plot1 <- data1 %>%
  ggplot( aes(x=name, y=value, fill=name)) +
    geom_boxplot() +
    scale_fill_viridis(discrete = TRUE, alpha=0.6) +
    geom_jitter(color="black", size=0.4, alpha=0.9) +
    theme(legend.position="none",
          plot.title = element_text(size=15)) +
    ggtitle("Age distribution (NO match)") +
    xlab("")

# MATCHED
male.df        <- subset(df_lC_matched, scode==0)
male.pat.age   <- subset(male.df, dcode==1)$age
male.con.age   <- subset(male.df, dcode==0)$age
female.df        <- subset(df_lC_NO_matched, scode==1)
female.pat.age   <- subset(male.df, dcode==1)$age
female.con.age   <- subset(male.df, dcode==0)$age

data2 <- data.frame(
  name=c( rep("Male pat",length(male.pat.age)), 
          rep("Female pat",length(female.pat.age)), 
          rep("Male hc",length(male.con.age)), 
          rep("Female hc",length(female.con.age))),
  value=c(male.pat.age, female.pat.age,
          male.con.age, female.con.age))

plot2 <- data2 %>%
  ggplot( aes(x=name, y=value, fill=name)) +
    geom_boxplot() +
    scale_fill_viridis(discrete = TRUE, alpha=0.6) +
    geom_jitter(color="black", size=0.4, alpha=0.9) +
    theme(legend.position="none",
          plot.title = element_text(size=15)) +
    ggtitle("Age distribution (match)") +
    xlab("")

plot_grid(plot1, plot2, labels = "AUTO")
```

### NO MATCHED DATASET

|  NO MATCHED| timepoint 1| timepoint 2 | timepoint 3 |
| -----------|:----------:|:-----------:|:-----------:|
| # controls | 298        | 293         | 109         |
| # patients | 169        | 168         | 50          |

| Timepoint 1| sex 0| sex 1|
| -----------|:----:|:----:|
| # controls | 131  | 167  |
| # patients |  38  | 131  |

| Timepoint 2| sex 0| sex 1|
| -----------|:----:|:----:|
| # controls | 130  | 163  |
| # patients |  38  | 130  |

| Timepoint 3| sex 0| sex 1|
| -----------|:----:|:----:|
| # controls |  50  |  59  |
| # patients |   7  |  43  |

```{r, eval=FALSE, include=FALSE}
table(df_lC_NO_matched$dcode, df_lC_NO_matched$timepoint)

for (i in 1:3) {
  print(knitr::kable(table(dcode=df_lC_NO_matched$dcode, sex=df_lC_NO_matched$scode,
                           timepoint=df_lC_NO_matched$timepoint)[,,i]))
}
```

### MATCHED DATASET

|  MATCHED   | timepoint 1| timepoint 2 | timepoint 3 |
| -----------|:----------:|:-----------:|:-----------:|
| # controls | 169        | 164         | 49          |
| # patients | 169        | 164         | 49          |

| Timepoint 1| sex 0| sex 1|
| -----------|:----:|:----:|
| # controls |  38  | 131  |
| # patients |  38  | 131  |


| Timepoint 2| sex 0| sex 1|
| -----------|:----:|:----:|
| # controls |  37  | 127  |
| # patients |  38  | 126  |


| Timepoint 3| sex 0| sex 1|
| -----------|:----:|:----:|
| # controls |   8  | 41   |
| # patients |   7  | 42   |


```{r, eval=FALSE, include=FALSE}

table(df_lC_matched$dcode, df_lC_matched$timepoint)

for (i in 1:3) {
  print(knitr::kable(table(dcode=df_lC_matched$dcode, sex=df_lC_matched$scode, 
                           timepoint=df_lC_matched$timepoint)[,,i]))
}
```

# Linear Mixed Effects Model Regresion

## NO Match-it

```{r}
Zs_NOmatch <- run_NormativeModel(df_lC_NO_matched,
                                 measure = "CT_freesurfer",
                                 parc = "parc35",
                                 match = "NOmatch",
                                 harmonization = "lC")
```

```{r echo=FALSE}
# Histogram overlaid with kernel density curve
ggplot(Zs_NOmatch, aes(x=z)) +  
    geom_histogram(aes(y=..density..),        # Histogram with density
                   binwidth=.3, colour="black", fill="white") +
    geom_density(alpha=.2, fill="#FF6666")  + # Transparent density plot
    geom_vline(aes(xintercept=mean(z, na.rm=T)),   # Ignore NA values for mean
               color="red", linetype="dashed", size=0.5) +
    labs(title="z-score distribution (NO MATCH)", 
         x = "z-score", 
         y = "density")
```
```{r echo=FALSE}
z_mean_reg_match <- Zs_NOmatch %>%
  group_by(region) %>%
  dplyr::summarise(media = mean(z))
x <- 1:length(z_mean_reg_match$media)
plot(x, z_mean_reg_match$media, type = "l", lwd=1, xlab="region", ylab="mean z-score", main="Mean z-score per region (NO MATCH)")
```

## Match-it dataframe

```{r}
Zs_match <- run_NormativeModel(df_lC_matched,
                               measure = "CT_freesurfer",
                               parc = "parc35",
                               match = "match",
                               harmonization = "lC")
```

```{r echo=FALSE}
# Histogram overlaid with kernel density curve
ggplot(Zs_match, aes(x=z)) +  
    geom_histogram(aes(y=..density..),        # Histogram with density
                   binwidth=.3, colour="black", fill="white") +
    geom_density(alpha=.2, fill="#FF6666")  + # Transparent density plot
    geom_vline(aes(xintercept=mean(z, na.rm=T)),   # Ignore NA values for mean
               color="red", linetype="dashed", size=0.5)+
    labs(title="z-score distribution (MATCH)", 
         x = "z-score", 
         y = "density")
```
```{r echo=FALSE}
z_mean_reg_match <- Zs_match %>%
  group_by(region) %>%
  dplyr::summarise(media = mean(z))
x <- 1:length(z_mean_reg_match$media)
plot(x, z_mean_reg_match$media, type = "l", lwd=1, xlab="region", ylab="mean z-score", main="Mean z-score per region (MATCH)")
```

## Match-it dataframe (Age*Diagnosis) BEFORE EXCLUDING DEVIANTS

```{r, message=F}
p_val <- run_AgeDiagnosisModel(df_lC_matched, 
                               measure = "CT_freesurfer",
                               Z = NULL, 
                               exclude_deviants = F)

p_val_FDR <- Apply_FDR_Correction(p_val)
```

```{r echo=FALSE, results='hold'}
cat("Without FDR correction:\n")
cat("Variable dcode has statistical significance for ", sum(p_val[,"dcode"]<0.05),"/",length(p_val[,"dcode"]), "regions\n")
cat("Variable dcode_age has statistical significance for ",sum(p_val[,"dcode_age"]<0.05),"/",length(p_val[,"dcode_age"]), "regions\n")
```

```{r echo=FALSE}
head(p_val, 4)  
```

```{r echo=FALSE, results='hold'}
cat("With FDR correction:\n")
cat("Variable dcode has statistical significance for ", sum(p_val_FDR[,"dcode"]<0.05),"/",length(p_val[,"dcode"]),"regions\n")
cat("Variable dcode_age has statistical significance for ",sum(p_val_FDR[,"dcode_age"]<0.05),"/",length(p_val[,"dcode_age"]),"regions")
```

```{r echo=FALSE}
head(p_val_FDR, 4)  
```

```{r, echo=FALSE}
# PLOT p-values
par(mfrow = c(2, 2), mai = c(0.9, 0.8, 0.2, 0.2))  # 2 rows and 2 columns
x1 <- p_val[,"dcode"]
x2 <- p_val_FDR[,"dcode"]
x3 <- p_val[,"dcode_age"]
x4 <- p_val_FDR[,"dcode_age"]

hist(x1, main="p-vals (dcode)", col="orange")
hist(x2, main="p-vals with FDR (dcode)", col="green")
hist(x3, main="p-vals (dcode_age)", col="orange")
hist(x4, main="p-vals with FDR (dcode_age)", col="green")
```


## Match-it dataframe (Age*Diagnosis) AFTER EXCLUDING DEVIANTS

```{r, message=F}
p_val <- run_AgeDiagnosisModel(df_lC_matched, 
                               measure = "CT_freesurfer",
                               Z = Zs_match, 
                               exclude_deviants = T)

p_val_FDR <- Apply_FDR_Correction(p_val)
```

```{r echo=FALSE, results='hold'}
cat("Without FDR correction:\n")
cat("Variable dcode has statistical significance for ",sum(p_val[,"dcode"]<0.05),"/",length(p_val[,"dcode"]),"regions\n")
cat("Variable dcode_age has statistical significance for ",sum(p_val[,"dcode_age"]<0.05),"/",length(p_val[,"dcode_age"]),"regions\n")
```

```{r echo=FALSE}
head(p_val, 4)  
```

```{r, echo=FALSE, results='hold'}
cat("With FDR correction:\n")
cat("Variable dcode has statistical significance for ", sum(p_val_FDR[,"dcode"]<0.05),"/",length(p_val[,"dcode"]),"regions\n")
cat("Variable dcode_age has statistical significance for ",sum(p_val_FDR[,"dcode_age"]<0.05),"/",length(p_val[,"dcode_age"]),"regions")
```

```{r echo=FALSE}
head(p_val_FDR, 4)  
```

```{r, echo=FALSE}
# PLOT p-values
par(mfrow = c(2, 2), mai = c(0.9, 0.8, 0.2, 0.2))  # 2 rows and 2 columns
x1 <- p_val[,"dcode"]
x2 <- p_val_FDR[,"dcode"]
x3 <- p_val[,"dcode_age"]
x4 <- p_val_FDR[,"dcode_age"]

hist(x1, main="p-vals (dcode)", col="orange")
hist(x2, main="p-vals with FDR (dcode)", col="green")
hist(x3, main="p-vals (dcode_age)", col="orange")
hist(x4, main="p-vals with FDR (dcode_age)", col="green")
```

# Analysis of z-scores and computation of global scores

```{r eval=FALSE, include=FALSE}
Z <- Zs_match %>% # change match / NOmatch
  mutate(deviant = ifelse(z < -1.96 | z > 1.96, 1, 0))

table(Z$timepoint) # 1st row
table(Z$deviant, Z$timepoint) # 1st row is 2nd row
t(table(Z$timepoint, Z$group))  # 1st row is 3rd row and 2nd row is 5th row
table(Z$deviant, Z$timepoint, Z$group)  # 2nd row is 4th and 6th row

t(round(t(table(Z$deviant, Z$timepoint))*100/c(nrow(subset(Z, timepoint==1)),nrow(subset(Z, timepoint==2)),nrow(subset(Z, timepoint==3))),2)) # Percentages of the 2nd row

round(t(table(Z$deviant, Z$timepoint, Z$group)[2,1:3,])[1,1:3]*100/t(table(Z$timepoint, Z$group))[1,1:3],2) # controls, percentages of the 4th row

round(t(table(Z$deviant, Z$timepoint, Z$group)[2,1:3,])[2,1:3]*100/t(table(Z$timepoint, Z$group))[2,1:3],2) # pats, percentages of the 6th row
```

The following tables represent, **in terms of samples**, the number of deviations ($|Z|>1.96$). The number of samples refers to the total number of regions, calculated for each timepoint ($timepoint=1,2,3$) and differentiated between controls and subjects.

|     NO MATCHED     | timepoint 1   | timepoint 2 | timepoint 3 |
| ----------------   |:-----------:  |:-----------:|:-----------:|
| # total samples    |   31.688      |   31.348    |  10.744     |
| # samples dev (%)  |  795 (2.51%)  |  696 (2.22%)|  275 (2.56%)|
| # controls samples |  20.264       |  19.924     |   7.412     |
| # controls dev  (%)|  450 (2.22%)  |  335 (1.68%)| 143 (1.93%) |
| # patients samples |  11.424       |   11.424    |  3.332      |
| # patients dev (%) |  345 (3.02%)  |  361 (3.16%)|  132 (3.96%)|


|     MATCHED        | timepoint 1   | timepoint 2   | timepoint 3 |
| ----------------   |:-----------:  |:-------------:|:-----------:|
| # total samples    |   22.916      |  22.304       |    6.664    |
| # samples dev (%)  |  617 (2.69%)  |    519 (2.33%)|  187 (2.81%)|
| # controls samples |  11.492       |  11.152       |  3.332      |
| # controls dev  (%)|   269 (2.34%) |  176 (1.58%)  |  71 (2.13%) |
| # patients samples |  11.424       |  11.152       |  3.332      |
| # patients dev (%) |  348 (3.05%)  |   343  (3.08%)|  116 (3.48%)|

In the following, we chose to work with the matched dataset and the Zs derived from its lme model, providing a better statistical support for the analysis.

***

We computed the number of deviant samples ($Z<-1.96$ and $Z>1.96$):

```{r, eval=FALSE, include=FALSE}
Z <- Zs_match %>%
  mutate(deviant = ifelse(z > -1.96 & z < 1.96, 0, z)) %>%
  mutate(deviant = ifelse(z < -1.96, -1, deviant)) %>%
  mutate(deviant = ifelse(z >  1.96, 1 , deviant))

t(table(Z$deviant, Z$timepoint))       # first 3x3 row-col (timepoint, dev)
table(Z$deviant, Z$timepoint, Z$group) # first 3x3 row-col (timepoint, dev) (differentiating between pat/controls)

t(table(Z$deviant==1 | Z$deviant==-1, Z$timepoint)) #2nd col is --> last column
table(Z$deviant==1 | Z$deviant==-1, Z$timepoint, Z$group) #2nd col is --> last column (differentiating between pat/controls)
c(t(table(Z$deviant==-1))[2],t(table(Z$deviant==0))[2], t(table(Z$deviant==1))[2], 
  t(table(Z$deviant==1 | Z$deviant==-1))[2])  #last row

# Percentages 3x4
cbind(round(t(table(Z$deviant==-1, Z$timepoint))*100/c(nrow(subset(Z, timepoint==1)),nrow(subset(Z, timepoint==2)),nrow(subset(Z, timepoint==3))),2)[,2],
      round(t(table(Z$deviant==0, Z$timepoint))*100/c(nrow(subset(Z, timepoint==1)),nrow(subset(Z, timepoint==2)),nrow(subset(Z, timepoint==3))),2)[,2], 
      round(t(table(Z$deviant==1, Z$timepoint))*100/c(nrow(subset(Z, timepoint==1)),nrow(subset(Z, timepoint==2)),nrow(subset(Z, timepoint==3))),2)[,2],
round(t(table(Z$deviant==1 | Z$deviant==-1, Z$timepoint))*100/c(nrow(subset(Z, timepoint==1)),nrow(subset(Z, timepoint==2)),nrow(subset(Z, timepoint==3))),2)[,2])

# Percentages of the last row
round(c(t(table(Z$deviant==-1))[2],t(table(Z$deviant==0))[2], t(table(Z$deviant==1))[2], 
  t(table(Z$deviant==1 | Z$deviant==-1))[2])*100/sum(table(Z$deviant)),2)


a <- table(Z$deviant, Z$timepoint)       # first 3x3 row-col (timepoint, dev)
b <- table(Z$deviant, Z$timepoint, Z$group) # first 3x3 row-col (timepoint, dev) (differentiating between pat/controls)

round(b[ , ,1]*100/a,2)  # CONTROL
round(b[ , ,2]*100/a,2)  # PATIENT


# Last column:
a<-t(table(Z$deviant==1 | Z$deviant==-1, Z$timepoint)) #2nd col is --> last column
b<-table(Z$deviant==1 | Z$deviant==-1, Z$timepoint, Z$group) #2nd col is --> last column (differentiating between pat/controls)

round(b[2,,1]*100/a[,2],2) # CONTROL
round(b[2,,2]*100/a[,2],2) # PATIENTS
```

# In terms of regions deviated:

|         | Infra-normal deviants|  Non deviants   | Supra-normal deviants | Deviants     |
|---------|:--------------------:|:---------------:|:---------------------:|:------------:|
|  tp 1   |      339 (1.48%)     | 22.299 (97.31%) |     278 (1.21%)       |  617 (2.69%) |
| controls|      172 (50.74%)    | 11.223 (50.33%) |      97 (34.89%)      |  269 (43.60%)|
| patients|      167 (49.26%)    | 11.076 (49.67%) |     181 (65.11%)      |  348 (56.40%)|
|  tp 2   |      322 (1.44%)     | 21.785 (97.67%) |     197 (0.88%)       |  519 (2.33%) |
| controls|       83 (25.78%)    | 10.976 (50.38%) |      93 (47.21%)      |  176 (33.91%)|
| patients|      239 (74.22%)    | 10.809 (49.62%) |     104 (52.79%)      |  343 (66.09%)|
|  tp 3   |      133 (2.00%)     |  6.477 (97.19%) |      54 (0.81%)       |  187 (2.81%) |
| controls|       39 (29.32%)    |  3.261 (50.35%) |      32 (59.26%)      |   71 (37.97%)|
| patients|       94 (70.68%)    |  3.216 (49.65%) |      22 (40.74%)      |  116 (62.03%)|
|  total  |      794 (1.53%)     | 50.561 (97.45%) |     529 (1.02%)       |1.323 (2.55%) |


```{r message=FALSE, warning=FALSE, echo=FALSE}
#library("ggExtra") #install.packages("ggExtra")
for (d in c("infra-dev","supra-dev")){
 for (tp in 1:3) {
  data <- Zs_match %>%
    mutate(deviant = ifelse(z > -1.96 & z < 1.96, 0, z)) %>%
    mutate(deviant = ifelse(z < -1.96, -1, deviant)) %>%
    mutate(deviant = ifelse(z >  1.96,  1, deviant)) %>% 
    mutate(deviant = factor(deviant, 
                            labels = c("infra-dev","normal","supra-dev"))) %>% 
    filter(deviant==d) %>% 
    filter(timepoint==tp) %>% 
    group_by(subID, group, deviant) %>%
    dplyr::summarise(n=n()) 
  
  p1 <- ggplot(data = data,
               mapping = aes(x = subID, y = n, colour = group)) +
    geom_point() +
    geom_smooth(method = "loess") +
    labs(title=paste0("Timepoint ", tp, ",  ",d), 
         x = "subject ID", 
         y = "Number of regions deviated") +
    theme_bw() +
    theme(legend.position = "bottom",
          legend.title = element_blank())

  # Replace "histogram" with "boxplot" or "density" for other types
  p2 <- ggMarginal(p1, type = "histogram", groupColour = TRUE, groupFill = TRUE)
  print(p2, newpage = TRUE) 
 }
}

```

```{r eval=FALSE, message=FALSE, warning=FALSE, include=FALSE}

# OTRO PLOT QUE POR AHORA NO MOSTRAMOS
for (g in c("patient", "control")){
  for(tp in 1:3){
  data <- Zs_match %>%
    filter(timepoint==tp) %>% 
    filter(group==g) %>% 
    mutate(deviant = ifelse(z > -1.96 & z < 1.96, 0, z)) %>%
    mutate(deviant = ifelse(z < -1.96, -1, deviant)) %>%
    mutate(deviant = ifelse(z >  1.96,  1, deviant)) %>%
    filter(deviant!=0) %>% 
    mutate(Z = factor(deviant, labels = c("infra-dev","supra-dev")),
           subID = factor(subID))
  
  # Bar chart side by side
  plot <- ggplot(data, aes(x = subID, fill = Z)) +
    geom_bar(position = position_dodge()) + # position_dodge() o "fill"
    labs(title=paste0(g,", timepoint ", tp), x= g , y = "n regions") + 
    scale_fill_manual(values=c("#999999", "#E69F00")) +
    theme_minimal() + 
    theme(axis.text.x = element_text(size = 5, angle = 90))   
  print(plot)
 }
}
```

We computed the number of subjects that are **deviant at timepoint 1** and stay **deviant in subsequent timepoints**, for each region. A maximum of 5 subjects (1.48% of total subjects) fulfill that condition for any region.

```{r, message=FALSE, warning=FALSE, eval=FALSE, include=FALSE}
Z <- Zs_match %>%
  mutate(dev = ifelse((z < -1.96 | z > 1.96), 1, 0)) %>%  # Si se desvía vale 1
  group_by(region, subID) %>%
  dplyr::summarise(mul = prod(dev)) %>% # Multiplicamos los dev de todos los tp de cada subject por cada región
  group_by(region) %>%                  # Así, sólo valen distinto de 0 los que tienen todos los tp=1
  dplyr::summarise(sol = sum(mul)) %>%
  dplyr::arrange(desc(sol))

round(Z[1:3,2]*100/length(unique(Zs_match$subID)),2) # Percentage in the text
head(Z,3)
```

|                                     | Condition|
|-------------------------------------|:--------:|
|rh_cuneus_CT_freesurfer              | 5 (1.48%)|
|lh_rostralmiddlefrontal_CT_freesurfer| 4 (1.19%)|
|lh_temporalpole_CT_freesurfer        | 4 (1.19%)|


We computed the number of subjects that are **not deviant at timepoint 1** but become **deviant in subsequent timepoints**, for each region. A maximum of 20 subjects (5.93% of total subjects) fulfill that condition for any region.


```{r, message=FALSE, warning=FALSE, eval=FALSE, include=FALSE}
# Los que cumplen la condición valen 1, el resto 0. Al multiplicar sólo dan 1 los que cumplen la condición.
Z <- Zs_match %>%
  mutate(non_dev_tp1 = ifelse((z > -1.96 | z < 1.96)&timepoint==1, 1, 0), # Si no se desvía en tp1 vale 1
         dev_fup = ifelse((z < -1.96 | z > 1.96)&timepoint>1, 1, 0)) %>%  # Si se desvía vale 1
  mutate(cond=non_dev_tp1+dev_fup)%>% # Sumamos ambas columnas para obtener una sólo
  group_by(region,subID) %>%
  dplyr::summarise(mul = prod(cond)) %>% # Multiplicamos todos los tp de cada subject para cada región
  group_by(region) %>%            # Así, sólo valen 1 los que tienen todos los tp=1
  dplyr::summarise(sol = sum(mul)) %>%
  dplyr::arrange(desc(sol))

round(Z[1:3,2]*100/length(unique(Zs_match$subID)),2) # Percentage in the text
head(Z,3)
```

|                                       | Condition|
|---------------------------------------|:--------:|
|lh_lateraloccipital_CT_freesurfer      |20 (5.93%)|
|rh_temporalpole_CT_freesurfer          |20 (5.93%)|
|lh_posteriorcingulate_CT_freesurfer    |18 (5.34%)|


***

**1. Percentage of patients deviated from the normative range for any single cortical region**

+ Timepoint 1: No more than 6.548% of patients deviated from the normative range for any single cortical region.

+ Timepoint 2: No more than 6.707% of patients deviated from the normative range for any single cortical region.

+ Timepoint 3: No more than 10.204% of patients deviated from the normative range for any single cortical region.


```{r, eval=FALSE, message=FALSE, warning=FALSE, include=FALSE}
# For 1

for (tp in 1:3){ # for each timepoint
  Z <- Zs_match %>%
    filter(group=="patient") %>%
    filter(timepoint==tp) %>%
    mutate(dev = ifelse(z < -1.96 | z > 1.96, 1, 0))%>%
    group_by(region)%>%
    dplyr::summarise(nreg_dev = sum(dev==1),
              nreg_nondev = sum(dev==0))%>%
    mutate(perc_dev = round(100* nreg_dev/(nreg_dev+nreg_nondev),3)) %>%
    dplyr::arrange(desc(perc_dev))
  # head(Z,3)
  perc <- as.numeric(Z[1,"perc_dev"])
  cat("Timepoint", tp,":", perc,"%\n")
  #length(unique(Z$subID)) # Number of patients for each timepoint
}
```

***
**2. Most common regions with infra-normal deviations. Percentage of patients.**

+ Timepoint 1: Infra-normal deviations in CT of subjects were most commonly located in **rh_fusiform_CT_freesurfer** cortices, although only 1.786% of patients showed significant deviations in these regions.

+ Timepoint 2: Infra-normal deviations in CT of subjects were most commonly located in **rh_temporalpole_CT_freesurfer** cortices, although only 4.268% of patients showed significant deviations in these regions.

+ Timepoint 3: Infra-normal deviations in CT of subjects were most commonly located in **lh_fusiform_CT_freesurfer** cortices, although only 8.163% of patients showed significant deviations in these regions.


```{r, eval=FALSE, message=FALSE, warning=FALSE, include=FALSE}
# For 2

for (tp in 1:3){ # for each timepoint
  cat("Timepoint",tp,":\n")
  Z_all <- Zs_match %>%
    #filter(group=="patient") %>% # only for patients ?????
    filter(timepoint==tp) %>%
    mutate(deviant = ifelse(z < -1.96, 1, 0)) %>% # Infra-normal
    group_by(region) %>%
    dplyr::summarise(nreg_dev     = sum(deviant==1),
              nreg_nondev  = sum(deviant==0)) %>%
    mutate(perc_dev = round(100* nreg_dev/(nreg_dev+nreg_nondev),3)) %>%
    arrange(desc(perc_dev))
  #print(head(Z_all,5))
  reg <- as.character(Z_all[1,"region"])
  cat("Region in subjects:", reg,"\n")

  Z_pat <- Zs_match %>%
    filter(group=="patient") %>% # only for patients
    filter(timepoint==tp) %>%
    mutate(deviant = ifelse(z < -1.96, 1, 0))%>% # Infra-normal
    group_by(region) %>%
    dplyr::summarise(nreg_dev     = sum(deviant==1),
              nreg_nondev  = sum(deviant==0)) %>%
    mutate(perc_dev = round(100* nreg_dev/(nreg_dev+nreg_nondev),3)) %>%
    arrange(desc(perc_dev))
  #print(head(Z_pat,5))
  perc <- as.numeric(subset(Z_pat, region==paste0(reg))[1,"perc_dev"])
  cat("Percentage in patients:",perc,"%\n\n")
}
```


***
**3. Most common regions with supra-normal deviations. Percentage of individuals.**

+ Timepoint 1: Supra-normal deviations in CT were most common in the **lh_lateraloccipital_CT_freesurfer** regions, 2.967% of individuals.

+ Timepoint 2: Supra-normal deviations in CT were most common in the **lh_lateraloccipital_CT_freesurfer** regions, 2.134% of individuals.

+ Timepoint 3: Supra-normal deviations in CT were most common in the **lh_parahippocampal_CT_freesurfer** regions, 3.061% of individuals.

```{r eval=FALSE, message=FALSE, warning=FALSE, include=FALSE}
# For 3

for (tp in 1:3){ # for each timepoint
  cat("Timepoint",tp,":\n")
  Z_all <- Zs_match %>%
    filter(timepoint==tp) %>%
    mutate(deviant = ifelse(z > 1.96, 1, 0))%>% # Supra-normal
    group_by(region) %>%
    dplyr::summarise(nreg_dev     = sum(deviant==1),
              nreg_nondev  = sum(deviant==0)) %>%
    mutate(perc_dev = round(100* nreg_dev/(nreg_dev+nreg_nondev),3)) %>%
    arrange(desc(perc_dev))
  #print(head(Z_all,5))
  reg  <- as.character(Z_all[1,"region"])
  perc <- as.numeric(Z_all[1,"perc_dev"])
  cat("Region:", reg,"with percentage: ",perc,"%\n\n")
}
```

***

```{r eval=FALSE, message=FALSE, warning=FALSE, include=FALSE}
# For 4 and 5

for (tp in 1:3){ # for each timepoint
  cat("\nTIMEPOINT",tp)

  Z_pat <- Zs_match %>%
    filter(group=="patient") %>% # only for patients
    filter(timepoint==tp)    %>%
    mutate(deviant_infra = ifelse(z < -1.96, 1, 0))%>% # Infra-normal
    mutate(deviant_supra = ifelse(z > 1.96, 1, 0)) %>% # Supra-normal
    group_by(subID) %>%
    dplyr::summarise(nreg_dev_infra    = sum(deviant_infra==1),   # At least one region deviated
              nreg_dev_supra    = sum(deviant_supra==1))   %>%
    mutate(deviant_infra = ifelse(nreg_dev_infra>0, 1, 0), # At least one region deviated
           deviant_supra = ifelse(nreg_dev_supra>0, 1, 0)) %>%
    dplyr::summarise(pat_dev_infra    = sum(deviant_infra==1),
              pat_nondev_infra = sum(deviant_infra==0),
              pat_dev_supra    = sum(deviant_supra==1),
              pat_nondev_supra = sum(deviant_supra==0)) %>%
    mutate(perc_dev_infra = round(100* pat_dev_infra/(pat_dev_infra+pat_nondev_infra),3),
           perc_dev_supra = round(100* pat_dev_supra/(pat_dev_supra+pat_nondev_supra),3))
  # porcentaje calculado con el total de pacientes para cada timepoint
  perc_infra_pac <- as.numeric(Z_pat[1,"perc_dev_infra"])
  perc_supra_pac <- as.numeric(Z_pat[1,"perc_dev_supra"])

  Z_hc <- Zs_match %>%
    filter(group=="control") %>% # only for controls
    filter(timepoint==tp)    %>%
    mutate(deviant_infra = ifelse(z < -1.96, 1, 0))%>% # Infra-normal
    mutate(deviant_supra = ifelse(z > 1.96, 1, 0)) %>% # Supra-normal
    group_by(subID) %>%
    dplyr::summarise(nreg_dev_infra    = sum(deviant_infra==1),
              nreg_dev_supra    = sum(deviant_supra==1))   %>%
    mutate(deviant_infra = ifelse(nreg_dev_infra>0, 1, 0),
           deviant_supra = ifelse(nreg_dev_supra>0, 1, 0)) %>%
    dplyr::summarise(hc_dev_infra    = sum(deviant_infra==1),
              hc_nondev_infra = sum(deviant_infra==0),
              hc_dev_supra    = sum(deviant_supra==1),
              hc_nondev_supra = sum(deviant_supra==0)) %>%
    mutate(perc_dev_infra = round(100* hc_dev_infra/(hc_dev_infra+hc_nondev_infra),3),
           perc_dev_supra = round(100* hc_dev_supra/(hc_dev_supra+hc_nondev_supra),3))
  # porcentaje calculado con el total de pacientes para cada timepoint
  perc_infra_hc <- as.numeric(Z_hc[1,"perc_dev_infra"])
  perc_supra_hc <- as.numeric(Z_hc[1,"perc_dev_supra"])
  
  cat('\nInfra-normal:')
  cat('\nPatients: ', perc_infra_pac,"%\n")
  cat('Healthy controls: ', perc_infra_hc,"%\n")
  cat('Supra-normal:')
  cat('\nPatients: ', perc_supra_pac,"%\n")
  cat('Healthy controls: ', perc_supra_hc,"%\n")
}
```

**4. Percentage of subjects with at least one region infra-normal deviated. Patients vs Healthy controls.**

+ Timepoint 1: Infra-normal deviations for at least one region were evident in 29.167% of patients, whereas this was the case for 26.036% of healthy individuals.

+ Timepoint 2: Infra-normal deviations for at least one region were evident in 35.366% of patients, whereas this was the case for 27.439% of healthy individuals.

+ Timepoint 3: Infra-normal deviations for at least one region were evident in 40.816% of patients, whereas this was the case for only 38.776% of healthy individuals.

***
**5. Percentage of subjects with at least one region supra-normal deviated. Patients vs Healthy controls.**

+ Timepoint 1: Supra-normal deviations for at least one region were evident in 32.143% of patients and 34.32% of healthy individuals.

+ Timepoint 2: Supra-normal deviations for at least one region were evident in 28.659% of patients and 29.878% of healthy individuals.

+ Timepoint 3: Supra-normal deviations for at least one region were evident in 30.612% of patients and 36.735% of healthy individuals.


***

### Percentage of deviant subjects for number of regions

**Figura B del paper de Bethlehem.**
En el eje de las x se representa el porcentaje de sujetos y en el eje y el número de regiones con el mismo ratio $\frac{|Z|>1.96}{|Z|<1.96}$. Se calcula para cada timepoint ($timepoint=1,2,3$).

```{r Ratio, warning=F, message = F}
getStatistics(Zs= Zs_match,  lab= "lC_match_parc35", parc= "parc35")
getStatistics(Zs= Zs_NOmatch, lab= "lC_NOmatch_parc35", parc= "parc35")
```

Show the results from the global ratios obtained:

## Match-it dataframe (longCombat):

```{r show-png-prev_match, echo=FALSE}
img1 <- rasterGrob(as.raster(readPNG("/data_J/Results/Plots/parc35/prevalence_wscores_1_lC_match_parc35.png")), interpolate = FALSE)
img2 <- rasterGrob(as.raster(readPNG("/data_J/Results/Plots/parc35/prevalence_wscores_2_lC_match_parc35.png")), interpolate = FALSE)
img3 <- rasterGrob(as.raster(readPNG("/data_J/Results/Plots/parc35/prevalence_wscores_3_lC_match_parc35.png")), interpolate = FALSE)

grid.arrange(img1, img2, img3, ncol = 1, nrow=3)
```

## NO Match-it dataframe (longCombat):

```{r show-png-prev-NOmatch, echo=FALSE}
img1 <- rasterGrob(as.raster(readPNG("/data_J/Results/Plots/parc35/prevalence_wscores_1_lC_NOmatch_parc35.png")), interpolate = FALSE)
img2 <- rasterGrob(as.raster(readPNG("/data_J/Results/Plots/parc35/prevalence_wscores_2_lC_NOmatch_parc35.png")), interpolate = FALSE)
img3 <- rasterGrob(as.raster(readPNG("/data_J/Results/Plots/parc35/prevalence_wscores_3_lC_NOmatch_parc35.png")), interpolate = FALSE)

grid.arrange(img1, img2, img3, ncol = 1, nrow=3)
```

# Variance contribution across measures

## NO Match-it dataframe (longCombat):


```{r message=FALSE, warning=FALSE}
variancePartition(df = df_lC_NO_matched,
                  measure = "CT_freesurfer",
                  lab = "lC_NO_matched_parc35",
                  par = "parc35")
```

```{r, echo=FALSE}
img1 <- rasterGrob(as.raster(readPNG("/data_J/Results/Plots/parc35/violin_tp1_lC_NO_matched_parc35.png")), interpolate = FALSE)
img2 <- rasterGrob(as.raster(readPNG("/data_J/Results/Plots/parc35/violin_tp2_lC_NO_matched_parc35.png")), interpolate = FALSE)
img3 <- rasterGrob(as.raster(readPNG("/data_J/Results/Plots/parc35/violin_tp3_lC_NO_matched_parc35.png")), interpolate = FALSE)

grid.arrange(img1, img2, img3, ncol = 1, nrow=3)
```



## Match-it dataframe (longCombat):

```{r message=FALSE, warning=FALSE}
variancePartition(df = df_lC_matched,
                  measure = "CT_freesurfer",
                  lab = "lC_matched_parc35",
                  par = "parc35")
```


```{r, echo=FALSE}
img1 <- rasterGrob(as.raster(readPNG("/data_J/Results/Plots/parc35/violin_tp1_lC_matched_parc35.png")), interpolate = FALSE)
img2 <- rasterGrob(as.raster(readPNG("/data_J/Results/Plots/parc35/violin_tp2_lC_matched_parc35.png")), interpolate = FALSE)
img3 <- rasterGrob(as.raster(readPNG("/data_J/Results/Plots/parc35/violin_tp3_lC_matched_parc35.png")), interpolate = FALSE)

grid.arrange(img1, img2, img3, ncol = 1, nrow=3)
```