---
title: "Normative modeling in Schizophrenia - External validation clinical measures"
author: "Noemi González Lois"
date: "`r Sys.Date()`"
output:
  pdf_document: default
  html_document: default
---


```{r, warning=F, message = F, echo = FALSE}
#install.packages("easypackages")
library("easypackages")

list.of.packages <- c("viridis", "tidyverse", "MatchIt", "grid", "png", 
                      "gridExtra", "parallel", "nlme", "JMbayes", "plyr",
                      "BiocManager", "Biostrings", "lme4", "ggplot2", "dplyr",
                      "Hmisc", "devtools", "longCombat", "neuroCombat", 
                      "tinytex", "knitr", "ggExtra", "variancePartition",
                      "Rmisc", "doParallel", "hrbrthemes", "cowplot", 
                      "BiocParallel", "effectsize", "ggpubr", "caret", "scorer",
                      "tidyr", "ggrepel")

new.packages <- list.of.packages[!(list.of.packages %in%
                                     installed.packages()[,"Package"])]
  if(length(new.packages)>0) { install.packages(new.packages)}

libraries(list.of.packages)

rm(list.of.packages, new.packages)
```


```{r, eval = F, include = FALSE}
tinytex::install_tinytex()
install_github("jcbeer/longCombat")
install_github("jfortin1/neuroCombatData")
install_github("jfortin1/neuroCombat_Rpackage")
BiocManager::install("BiocParallel")
BiocManager::install("Biostrings")
BiocManager::install("variancePartition")
# install_version("dplyr", version = "1.0.5", repos = "http://cran.us.r-project.org")
tinytex::install_tinytex()
devtools::install_github("paulhendricks/scorer")
```

```{r setup I, echo=F}
knitr::opts_chunk$set(
  include = TRUE,  
  echo    = TRUE, 
  eval    = TRUE, 
  warning = TRUE, 
  message = TRUE,
  cache   = T,
  fig.width  = 10,
  fig.height = 4,
  error   = TRUE)
```

## Global Z-score

The global Z-score for subject $j$, timepoint $t$ ($gZ_{jt}$) is achieved by computing a Z-score ratio of the number of regions ($i=1, ..., N$) deviated from the norm (1) divided by the number of regions inside the normative range (2):

$$gZ_{jt}=\frac{\sum_{i}^{N} (|Z_{jti}|>1.96) (1)}{\sum_{i}^{N} (|Z_{jti}|<1.96) (2)}$$ 
Also, there are two ratios that take into account the direction of the deviation (supra or infra).


$$gZ_{jt}supra=\frac{\sum_{i}^{N} (Z_{jti}>1.96)}{\sum_{i}^{N} (|Z_{jti}|<1.96)}$$ 
$$gZ_{jt}infra=\frac{\sum_{i}^{N} (Z_{jti}<-1.96)}{\sum_{i}^{N} (|Z_{jti}|<1.96)}$$ 

```{r include=FALSE, message=FALSE, warning=FALSE, comment=NA}
setwd("/data_J/Scripts")
gZ_df_tp <- read.csv("/data_J/Results/Files/global_Zs_tps.csv")
df_morphosim <- read.csv("/data_J/Data/planU_morphosim_rawdatabase.csv")
df_morphosim <- df_morphosim[colnames(df_morphosim)[1:97]] 
gZ_df_tp$diagnose <- NULL 
df_to_plot <- merge(gZ_df_tp, df_morphosim)
rm(gZ_df_tp, df_morphosim)
df_to_plot <- subset(df_to_plot, dcode==1) # only patients
df_tps <- df_to_plot[,c("subID","timepoint","gZ","gZ_infra","gZ_supra","IQ_total","scode", "dcode","diagnose", "age", "Age_of_Onset", "PANSS_total", "Total_P", "Total_N", "Total_G",colnames(df_to_plot)[43:72], "age_problems_started", "age_psychotic_problems", "SES_Education_level", "SES_occupational_status", "SES_Education_totalyears")]
df_tps[] <- lapply(df_tps, function(x) as.numeric(x))

df <- subset(df_tps, timepoint==1)
rm(df_to_plot, df_tps)
```

\newpage

## Missing values (patients group)

```{r echo=FALSE, message=FALSE, warning=FALSE}
df_temp <- df
df_temp$subID <- NULL
df_temp$timepoint <- NULL
df_temp$scode <- NULL
df_temp$dcode <- NULL
df_temp$acode <- NULL
DF_percNA <- NULL
for (cn in colnames(df_temp)) {
  percNA <- round(sum(is.na(df_temp[,cn]))/ (sum(is.na(df_temp[,cn]))+  sum(!is.na(df_temp[,cn])))*100,2)
  DF_percNA <- rbind(DF_percNA, data.frame("variable" = cn,
                                           "percNA" = percNA))}
DF_percNA <- DF_percNA[order(DF_percNA$percNA), ]
DF_percNA$percNA <- paste0(DF_percNA$percNA, "%")
kable(DF_percNA)
rm(df_temp)
```


\newpage
## Correlating the global Z-score at BL with change in clinical variables
## IQ (Timepoint 2 - timepoint 1)

```{r include=FALSE, message=FALSE, warning=FALSE, comment=NA}
setwd("/data_J/Scripts")
gZ_df_tp <- read.csv("/data_J/Results/Files/global_Zs_tps.csv")
df_morphosim <- read.csv("/data_J/Data/planU_morphosim_rawdatabase.csv")
df_morphosim <- df_morphosim[colnames(df_morphosim)[1:97]] 
gZ_df_tp$diagnose <- NULL 
df_to_plot <- merge(gZ_df_tp, df_morphosim)
rm(gZ_df_tp, df_morphosim)
df_to_plot <- subset(df_to_plot, dcode==1) # only patients
df_tps <- df_to_plot[,c("subID","timepoint","gZ","gZ_infra","gZ_supra","IQ_total","scode", "dcode","diagnose", "age", "Age_of_Onset", "PANSS_total", "Total_P", "Total_N", "Total_G",colnames(df_to_plot)[43:72], "age_problems_started", "age_psychotic_problems", "SES_Education_level", "SES_occupational_status", "SES_Education_totalyears")]
df_tps[] <- lapply(df_tps, function(x) as.numeric(x))
rm(df_to_plot, df)

df_tp1 <- df_tps[df_tps[,"timepoint"]==1, ] #"IQ_total"
df_tp1 <- df_tp1[,c("subID","IQ_total")]
colnames(df_tp1) <- c("subID", "IQ_total_tp1")

df_tp2 <- df_tps[df_tps[,"timepoint"]==2, ] #"IQ_total"
df_tp2 <- df_tp2[,c("subID","IQ_total")]
colnames(df_tp2) <- c("subID", "IQ_total_tp2")

df_tp3 <- df_tps[df_tps[,"timepoint"]==3, ] #"IQ_total"
df_tp3 <- df_tp3[,c("subID","IQ_total")]
colnames(df_tp3) <- c("subID", "IQ_total_tp3")

##### TP2-TP1
df_change_IQ <- merge(df_tp1, df_tp2)
df_change_IQ <- df_change_IQ[!is.na(!df_change_IQ$IQ_total_tp2),]
df_change_IQ <- df_change_IQ[!is.na(!df_change_IQ$IQ_total_tp1),]
df_change_IQ$change_IQ_tp2_tp1 <- df_change_IQ$IQ_total_tp2 - df_change_IQ$IQ_total_tp1
change_IQ_tp2_tp1 <- df_change_IQ
##### TP3-TP1
df_change_IQ <- merge(df_tp1, df_tp3)
df_change_IQ <- df_change_IQ[!is.na(!df_change_IQ$IQ_total_tp3),]
df_change_IQ <- df_change_IQ[!is.na(!df_change_IQ$IQ_total_tp1),]
df_change_IQ$change_IQ_tp3_tp1 <- df_change_IQ$IQ_total_tp3 - df_change_IQ$IQ_total_tp1
change_IQ_tp3_tp1 <- df_change_IQ
##### TP3-TP2
df_change_IQ <- merge(df_tp2, df_tp3)
df_change_IQ <- df_change_IQ[!is.na(!df_change_IQ$IQ_total_tp3),]
df_change_IQ <- df_change_IQ[!is.na(!df_change_IQ$IQ_total_tp2),]
df_change_IQ$change_IQ_tp3_tp2 <- df_change_IQ$IQ_total_tp3 - df_change_IQ$IQ_total_tp2
change_IQ_tp3_tp2 <- df_change_IQ


df_tps <- subset(df_tps, timepoint==1)
df_tps <- df_tps[ , c("subID","gZ", "gZ_infra", "gZ_supra")]
change_IQ_tp2_tp1 <- merge(change_IQ_tp2_tp1, df_tps)
change_IQ_tp2_tp1$IQ_total_tp1 <- NULL
change_IQ_tp2_tp1$IQ_total_tp2 <- NULL
change_IQ_tp3_tp1 <- merge(change_IQ_tp3_tp1, df_tps)
change_IQ_tp3_tp1$IQ_total_tp1 <- NULL
change_IQ_tp3_tp1$IQ_total_tp3 <- NULL
change_IQ_tp3_tp2 <- merge(change_IQ_tp3_tp2, df_tps)
change_IQ_tp3_tp2$IQ_total_tp2 <- NULL
change_IQ_tp3_tp2$IQ_total_tp3 <- NULL

colnames(change_IQ_tp2_tp1) <- c("subID", "change_IQ_tp2_tp1", "gZ_BL", "gZ_infra_BL", "gZ_supra_BL")    
colnames(change_IQ_tp3_tp1) <- c("subID", "change_IQ_tp3_tp1", "gZ_BL", "gZ_infra_BL", "gZ_supra_BL")
colnames(change_IQ_tp3_tp2) <- c("subID", "change_IQ_tp3_tp2", "gZ_BL", "gZ_infra_BL", "gZ_supra_BL")
  
rm(df_tp1, df_tp2, df_tp3, df_change_IQ, df_tps)
```

```{r echo=FALSE, message=FALSE, warning=FALSE, comment=NA, fig.width  = 10, fig.height = 10}
# Global deviance - CHANGE IN IQ (tp 2 - tp 1)
# gZ
df <- change_IQ_tp2_tp1
r <- round(as.numeric(cor.test(df$gZ_BL, df$change_IQ_tp2_tp1)$estimate),2)
p <- round(cor.test(df$gZ_BL, df$change_IQ_tp2_tp1)$p.value,2)
p1 <- ggplot(df, aes(x=gZ_BL, y=change_IQ_tp2_tp1)) +
  geom_point(col="green4") + 
  geom_smooth(method="lm", col="black") + 
  theme_bw() +
  labs(x = "Global deviance score at BL",
       y = "Change in IQ \n(tp2-tp1)" ,
       title = paste0("Deviance, patients r=",r,", p=",p))

# INFRA
r <- round(as.numeric(cor.test(df$gZ_infra_BL, df$change_IQ_tp2_tp1)$estimate),2)
p <- round(cor.test(df$gZ_infra_BL, df$change_IQ_tp2_tp1)$p.value,2)
p2 <- ggplot(df, aes(x=gZ_infra_BL, y=change_IQ_tp2_tp1)) +
  geom_point(col="green4") + 
  geom_smooth(method="lm", col="black") + 
  theme_bw() +
  labs(x = "Global deviance score at BL",
       y = "Change in IQ \n(tp2-tp1)" ,
       title = paste0("Infra-deviance, patients r=",r,", p=",p))

# SUPRA
r <- round(as.numeric(cor.test(df$gZ_supra_BL, df$change_IQ_tp2_tp1)$estimate),2)
p <- round(cor.test(df$gZ_supra_BL, df$change_IQ_tp2_tp1)$p.value,2)
p3 <- ggplot(df, aes(x=gZ_supra_BL, y=change_IQ_tp2_tp1)) +
  geom_point(col="green4") + 
  geom_smooth(method="lm", col="black") + 
  theme_bw() +
  labs(x = "Global deviance score at BL",
       y = "Change in IQ \n(tp2-tp1)" ,
       title = paste0("Supra-deviance, patients r=",r,", p=",p))

ggarrange(p1, p2, p3, ncol = 1, nrow = 3)
```

\newpage
## Correlating the global Z-score at BL with change in clinical variables
## IQ (Timepoint 3 - timepoint 1)

```{r echo=FALSE, message=FALSE, warning=FALSE, comment=NA, fig.width  = 10, fig.height = 10}
# Global deviance - CHANGE IN IQ (tp 3 - tp 1)
# gZ
df <- change_IQ_tp3_tp1
r <- round(as.numeric(cor.test(df$gZ_BL, df$change_IQ_tp3_tp1)$estimate),2)
p <- round(cor.test(df$gZ_BL, df$change_IQ_tp3_tp1)$p.value,2)
p1 <- ggplot(df, aes(x=gZ_BL, y=change_IQ_tp3_tp1)) +
  geom_point(col="green4") + 
  geom_smooth(method="lm", col="black") + 
  theme_bw() +
  labs(x = "Global deviance score at BL",
       y = "Change in IQ \n(tp3-tp1)" ,
       title = paste0("Deviance, patients r=",r,", p=",p))

# INFRA
r <- round(as.numeric(cor.test(df$gZ_infra_BL, df$change_IQ_tp3_tp1)$estimate),2)
p <- round(cor.test(df$gZ_infra_BL, df$change_IQ_tp3_tp1)$p.value,2)
p2 <- ggplot(df, aes(x=gZ_infra_BL, y=change_IQ_tp3_tp1)) +
  geom_point(col="green4") + 
  geom_smooth(method="lm", col="black") + 
  theme_bw() +
  labs(x = "Global deviance score at BL",
       y = "Change in IQ \n(tp3-tp1)" ,
       title = paste0("Infra-deviance, patients r=",r,", p=",p))

# SUPRA
r <- round(as.numeric(cor.test(df$gZ_supra_BL, df$change_IQ_tp3_tp1)$estimate),2)
p <- round(cor.test(df$gZ_supra_BL, df$change_IQ_tp3_tp1)$p.value,2)
p3 <- ggplot(df, aes(x=gZ_supra_BL, y=change_IQ_tp3_tp1)) +
  geom_point(col="green4") + 
  geom_smooth(method="lm", col="black") + 
  theme_bw() +
  labs(x = "Global deviance score at BL",
       y = "Change in IQ \n(tp3-tp1)" ,
       title = paste0("Supra-deviance, patients r=",r,", p=",p))

ggarrange(p1, p2, p3, ncol = 1, nrow = 3)
```

\newpage
## Correlating the global Z-score at BL with change in clinical variables
## IQ (Timepoint 3 - timepoint 2)

```{r echo=FALSE, message=FALSE, warning=FALSE, comment=NA, fig.width  = 10, fig.height = 10}
# Global deviance - CHANGE IN IQ (tp 3 - tp 2)
# gZ
df <- change_IQ_tp3_tp2
r <- round(as.numeric(cor.test(df$gZ_BL, df$change_IQ_tp3_tp2)$estimate),2)
p <- round(cor.test(df$gZ_BL, df$change_IQ_tp3_tp2)$p.value,2)
p1 <- ggplot(df, aes(x=gZ_BL, y=change_IQ_tp3_tp2)) +
  geom_point(col="green4") + 
  geom_smooth(method="lm", col="black") + 
  theme_bw() +
  labs(x = "Global deviance score at BL",
       y = "Change in IQ \n(tp3-tp2)" ,
       title = paste0("Deviance, patients r=",r,", p=",p))

# INFRA
r <- round(as.numeric(cor.test(df$gZ_infra_BL, df$change_IQ_tp3_tp2)$estimate),2)
p <- round(cor.test(df$gZ_infra_BL, df$change_IQ_tp3_tp2)$p.value,2)
p2 <- ggplot(df, aes(x=gZ_infra_BL, y=change_IQ_tp3_tp2)) +
  geom_point(col="green4") + 
  geom_smooth(method="lm", col="black") + 
  theme_bw() +
  labs(x = "Global deviance score at BL",
       y = "Change in IQ \n(tp3-tp2)" ,
       title = paste0("Infra-deviance, patients r=",r,", p=",p))

# SUPRA
r <- round(as.numeric(cor.test(df$gZ_supra_BL, df$change_IQ_tp3_tp2)$estimate),2)
p <- round(cor.test(df$gZ_supra_BL, df$change_IQ_tp3_tp2)$p.value,2)
p3 <- ggplot(df, aes(x=gZ_supra_BL, y=change_IQ_tp3_tp2)) +
  geom_point(col="green4") + 
  geom_smooth(method="lm", col="black") + 
  theme_bw() +
  labs(x = "Global deviance score at BL",
       y = "Change in IQ \n(tp3-tp2)" ,
       title = paste0("Supra-deviance, patients r=",r,", p=",p))

ggarrange(p1, p2, p3, ncol = 1, nrow = 3)
```



\newpage
## Correlating the global Z-score at BL with change in clinical variables
## PANSS (Timepoint 2 - timepoint 1)

```{r include=FALSE, message=FALSE, warning=FALSE, comment=NA}
setwd("/data_J/Scripts")
gZ_df_tp <- read.csv("/data_J/Results/Files/global_Zs_tps.csv")
df_morphosim <- read.csv("/data_J/Data/planU_morphosim_rawdatabase.csv")
df_morphosim <- df_morphosim[colnames(df_morphosim)[1:97]] 
gZ_df_tp$diagnose <- NULL 
df_to_plot <- merge(gZ_df_tp, df_morphosim)
rm(gZ_df_tp, df_morphosim)
df_to_plot <- subset(df_to_plot, dcode==1) # only patients
df_tps <- df_to_plot[,c("subID","timepoint","gZ","gZ_infra","gZ_supra","IQ_total","scode", "dcode","diagnose", "age", "Age_of_Onset", "PANSS_total", "Total_P", "Total_N", "Total_G",colnames(df_to_plot)[43:72], "age_problems_started", "age_psychotic_problems", "SES_Education_level", "SES_occupational_status", "SES_Education_totalyears")]
df_tps[] <- lapply(df_tps, function(x) as.numeric(x))
rm(df_to_plot, df)

df_tp1 <- df_tps[df_tps[,"timepoint"]==1, ] #"PANSS_total"
df_tp1 <- df_tp1[,c("subID","PANSS_total")]
colnames(df_tp1) <- c("subID", "PANSS_total_tp1")

df_tp2 <- df_tps[df_tps[,"timepoint"]==2, ] #"PANSS_total"
df_tp2 <- df_tp2[,c("subID","PANSS_total")]
colnames(df_tp2) <- c("subID", "PANSS_total_tp2")

df_tp3 <- df_tps[df_tps[,"timepoint"]==3, ] #"PANSS_total"
df_tp3 <- df_tp3[,c("subID","PANSS_total")]
colnames(df_tp3) <- c("subID", "PANSS_total_tp3")

##### TP2-TP1
df_change_PANSS <- merge(df_tp1, df_tp2)
df_change_PANSS <- df_change_PANSS[!is.na(!df_change_PANSS$PANSS_total_tp2),]
df_change_PANSS <- df_change_PANSS[!is.na(!df_change_PANSS$PANSS_total_tp1),]
df_change_PANSS$change_PANSS_tp2_tp1 <- df_change_PANSS$PANSS_total_tp2 - df_change_PANSS$PANSS_total_tp1
change_PANSS_tp2_tp1 <- df_change_PANSS
##### TP3-TP1
df_change_PANSS <- merge(df_tp1, df_tp3)
df_change_PANSS <- df_change_PANSS[!is.na(!df_change_PANSS$PANSS_total_tp3),]
df_change_PANSS <- df_change_PANSS[!is.na(!df_change_PANSS$PANSS_total_tp1),]
df_change_PANSS$change_PANSS_tp3_tp1 <- df_change_PANSS$PANSS_total_tp3 - df_change_PANSS$PANSS_total_tp1
change_PANSS_tp3_tp1 <- df_change_PANSS
##### TP3-TP2
df_change_PANSS <- merge(df_tp2, df_tp3)
df_change_PANSS <- df_change_PANSS[!is.na(!df_change_PANSS$PANSS_total_tp3),]
df_change_PANSS <- df_change_PANSS[!is.na(!df_change_PANSS$PANSS_total_tp2),]
df_change_PANSS$change_PANSS_tp3_tp2 <- df_change_PANSS$PANSS_total_tp3 - df_change_PANSS$PANSS_total_tp2
change_PANSS_tp3_tp2 <- df_change_PANSS


df_tps <- subset(df_tps, timepoint==1)
df_tps <- df_tps[ , c("subID","gZ", "gZ_infra", "gZ_supra")]
change_PANSS_tp2_tp1 <- merge(change_PANSS_tp2_tp1, df_tps)
change_PANSS_tp2_tp1$PANSS_total_tp1 <- NULL
change_PANSS_tp2_tp1$PANSS_total_tp2 <- NULL
change_PANSS_tp3_tp1 <- merge(change_PANSS_tp3_tp1, df_tps)
change_PANSS_tp3_tp1$PANSS_total_tp1 <- NULL
change_PANSS_tp3_tp1$PANSS_total_tp3 <- NULL
change_PANSS_tp3_tp2 <- merge(change_PANSS_tp3_tp2, df_tps)
change_PANSS_tp3_tp2$PANSS_total_tp2 <- NULL
change_PANSS_tp3_tp2$PANSS_total_tp3 <- NULL

colnames(change_PANSS_tp2_tp1) <- c("subID", "change_PANSS_tp2_tp1", "gZ_BL", "gZ_infra_BL", "gZ_supra_BL")     
colnames(change_PANSS_tp3_tp1) <- c("subID", "change_PANSS_tp3_tp1", "gZ_BL", "gZ_infra_BL", "gZ_supra_BL")
colnames(change_PANSS_tp3_tp2) <- c("subID", "change_PANSS_tp3_tp2", "gZ_BL", "gZ_infra_BL", "gZ_supra_BL")
  
rm(df_tp1, df_tp2, df_tp3, df_change_PANSS, df_tps)
```

```{r echo=FALSE, message=FALSE, warning=FALSE, comment=NA, fig.width  = 10, fig.height = 10}
# Global deviance - CHANGE IN PANSS (tp 2 - tp 1)
# gZ
df <- change_PANSS_tp2_tp1
r <- round(as.numeric(cor.test(df$gZ_BL, df$change_PANSS_tp2_tp1)$estimate),2)
p <- round(cor.test(df$gZ_BL, df$change_PANSS_tp2_tp1)$p.value,2)
p1 <- ggplot(df, aes(x=gZ_BL, y=change_PANSS_tp2_tp1)) +
  geom_point(col="green4") + 
  geom_smooth(method="lm", col="black") + 
  theme_bw() +
  labs(x = "Global deviance score at BL",
       y = "Change in PANSS \n(tp2-tp1)" ,
       title = paste0("Deviance, patients r=",r,", p=",p))

# INFRA
r <- round(as.numeric(cor.test(df$gZ_infra_BL, df$change_PANSS_tp2_tp1)$estimate),2)
p <- round(cor.test(df$gZ_infra_BL, df$change_PANSS_tp2_tp1)$p.value,2)
p2 <- ggplot(df, aes(x=gZ_infra_BL, y=change_PANSS_tp2_tp1)) +
  geom_point(col="green4") + 
  geom_smooth(method="lm", col="black") + 
  theme_bw() +
  labs(x = "Global deviance score at BL",
       y = "Change in PANSS \n(tp2-tp1)" ,
       title = paste0("Infra-deviance, patients r=",r,", p=",p))

# SUPRA
r <- round(as.numeric(cor.test(df$gZ_supra_BL, df$change_PANSS_tp2_tp1)$estimate),2)
p <- round(cor.test(df$gZ_supra_BL, df$change_PANSS_tp2_tp1)$p.value,2)
p3 <- ggplot(df, aes(x=gZ_supra_BL, y=change_PANSS_tp2_tp1)) +
  geom_point(col="green4") + 
  geom_smooth(method="lm", col="black") + 
  theme_bw() +
  labs(x = "Global deviance score at BL",
       y = "Change in PANSS \n(tp2-tp1)" ,
       title = paste0("Supra-deviance, patients r=",r,", p=",p))

ggarrange(p1, p2, p3, ncol = 1, nrow = 3)
```

\newpage
## Correlating the global Z-score at BL with change in clinical variables
## PANSS (Timepoint 3 - timepoint 1)

```{r echo=FALSE, message=FALSE, warning=FALSE, comment=NA, fig.width  = 10, fig.height = 10}
# Global deviance - CHANGE IN PANSS (tp 3 - tp 1)
# gZ
df <- change_PANSS_tp3_tp1
r <- round(as.numeric(cor.test(df$gZ_BL, df$change_PANSS_tp3_tp1)$estimate),2)
p <- round(cor.test(df$gZ_BL, df$change_PANSS_tp3_tp1)$p.value,2)
p1 <- ggplot(df, aes(x=gZ_BL, y=change_PANSS_tp3_tp1)) +
  geom_point(col="green4") + 
  geom_smooth(method="lm", col="black") + 
  theme_bw() +
  labs(x = "Global deviance score at BL",
       y = "Change in PANSS \n(tp3-tp1)" ,
       title = paste0("Deviance, patients r=",r,", p=",p))

# INFRA
r <- round(as.numeric(cor.test(df$gZ_infra_BL, df$change_PANSS_tp3_tp1)$estimate),2)
p <- round(cor.test(df$gZ_infra_BL, df$change_PANSS_tp3_tp1)$p.value,2)
p2 <- ggplot(df, aes(x=gZ_infra_BL, y=change_PANSS_tp3_tp1)) +
  geom_point(col="green4") + 
  geom_smooth(method="lm", col="black") + 
  theme_bw() +
  labs(x = "Global deviance score at BL",
       y = "Change in PANSS \n(tp3-tp1)" ,
       title = paste0("Infra-deviance, patients r=",r,", p=",p))

# SUPRA
r <- round(as.numeric(cor.test(df$gZ_supra_BL, df$change_PANSS_tp3_tp1)$estimate),2)
p <- round(cor.test(df$gZ_supra_BL, df$change_PANSS_tp3_tp1)$p.value,2)
p3 <- ggplot(df, aes(x=gZ_supra_BL, y=change_PANSS_tp3_tp1)) +
  geom_point(col="green4") + 
  geom_smooth(method="lm", col="black") + 
  theme_bw() +
  labs(x = "Global deviance score at BL",
       y = "Change in PANSS \n(tp3-tp1)" ,
       title = paste0("Supra-deviance, patients r=",r,", p=",p))

ggarrange(p1, p2, p3, ncol = 1, nrow = 3)
```

\newpage
## Correlating the global Z-score at BL with change in clinical variables
## PANSS (Timepoint 3 - timepoint 2)

```{r echo=FALSE, message=FALSE, warning=FALSE, comment=NA, fig.width  = 10, fig.height = 10}
# Global deviance - CHANGE IN PANSS (tp 3 - tp 2)
# gZ
df <- change_PANSS_tp3_tp2
r <- round(as.numeric(cor.test(df$gZ_BL, df$change_PANSS_tp3_tp2)$estimate),2)
p <- round(cor.test(df$gZ_BL, df$change_PANSS_tp3_tp2)$p.value,2)
p1 <- ggplot(df, aes(x=gZ_BL, y=change_PANSS_tp3_tp2)) +
  geom_point(col="green4") + 
  geom_smooth(method="lm", col="black") + 
  theme_bw() +
  labs(x = "Global deviance score at BL",
       y = "Change in PANSS \n(tp3-tp2)" ,
       title = paste0("Deviance, patients r=",r,", p=",p))

# INFRA
r <- round(as.numeric(cor.test(df$gZ_infra_BL, df$change_PANSS_tp3_tp2)$estimate),2)
p <- round(cor.test(df$gZ_infra_BL, df$change_PANSS_tp3_tp2)$p.value,2)
p2 <- ggplot(df, aes(x=gZ_infra_BL, y=change_PANSS_tp3_tp2)) +
  geom_point(col="green4") + 
  geom_smooth(method="lm", col="black") + 
  theme_bw() +
  labs(x = "Global deviance score at BL",
       y = "Change in PANSS \n(tp3-tp2)" ,
       title = paste0("Infra-deviance, patients r=",r,", p=",p))

# SUPRA
r <- round(as.numeric(cor.test(df$gZ_supra_BL, df$change_PANSS_tp3_tp2)$estimate),2)
p <- round(cor.test(df$gZ_supra_BL, df$change_PANSS_tp3_tp2)$p.value,2)
p3 <- ggplot(df, aes(x=gZ_supra_BL, y=change_PANSS_tp3_tp2)) +
  geom_point(col="green4") + 
  geom_smooth(method="lm", col="black") + 
  theme_bw() +
  labs(x = "Global deviance score at BL",
       y = "Change in PANSS \n(tp3-tp2)" ,
       title = paste0("Supra-deviance, patients r=",r,", p=",p))

ggarrange(p1, p2, p3, ncol = 1, nrow = 3)
```





\newpage
## Correlating the global Z-score with clinical variables (by timepoint)

```{r include=FALSE, message=FALSE, warning=FALSE, comment=NA}
setwd("/data_J/Scripts")
gZ_df_tp <- read.csv("/data_J/Results/Files/global_Zs_tps.csv")
df_morphosim <- read.csv("/data_J/Data/planU_morphosim_rawdatabase.csv")
df_morphosim <- df_morphosim[colnames(df_morphosim)[1:97]] 
gZ_df_tp$diagnose <- NULL 
df_to_plot <- merge(gZ_df_tp, df_morphosim)
rm(gZ_df_tp, df_morphosim)
df_to_plot <- subset(df_to_plot, dcode==1) # only patients
df_tps <- df_to_plot[,c("subID","timepoint","gZ","gZ_infra","gZ_supra","IQ_total","scode", "dcode","diagnose", "age", "Age_of_Onset", "PANSS_total", "Total_P", "Total_N", "Total_G",colnames(df_to_plot)[43:72], "age_problems_started", "age_psychotic_problems", "SES_Education_level", "SES_occupational_status", "SES_Education_totalyears")]
df_tps[] <- lapply(df_tps, function(x) as.numeric(x))
rm(df_to_plot, df)
```

## IQ total

```{r echo=FALSE, message=FALSE, warning=FALSE, comment=NA, fig.width  = 10, fig.height = 10}
# Global deviance - IQ_total
# TIMEPOINT 1
df <- subset(df_tps, timepoint==1)
r <- round(as.numeric(cor.test(df$gZ, df$IQ_total)$estimate),2)
p <- round(cor.test(df$gZ, df$IQ_total)$p.value,2)
p1 <- ggplot(df, aes(x=gZ, y=IQ_total)) +
  geom_point(col="green4") + 
  geom_smooth(method="lm", col="black") + 
  theme_bw() +
  labs(x = "Global deviance score",
       y = paste0("IQ total \n (",
                  round(sum(is.na(df$IQ_total))/
                        (sum(is.na(df$IQ_total))+
                           sum(!is.na(df$IQ_total)))*100,2),
                  "% NA values)"),
       title = paste0("Timepoint 1, patients r=",r,", p=",p))

# TIMEPOINT 2
df <- subset(df_tps, timepoint==2)
r <- round(as.numeric(cor.test(df$gZ, df$IQ_total)$estimate),2)
p <- round(cor.test(df$gZ, df$IQ_total)$p.value,2)
p2 <- ggplot(df, aes(x=gZ, y=IQ_total)) +
  geom_point(col="green4") + 
  geom_smooth(method="lm", col="black") + 
  theme_bw() +
  labs(x = "Global deviance score",
       y = paste0("IQ total \n (",
                  round(sum(is.na(df$IQ_total))/
                        (sum(is.na(df$IQ_total))+
                           sum(!is.na(df$IQ_total)))*100,2),
                  "% NA values)"),
       title = paste0("Timepoint 2, patients r=",r,", p=",p))

# TIMEPOINT 3
df <- subset(df_tps, timepoint==3)
r <- round(as.numeric(cor.test(df$gZ, df$IQ_total)$estimate),2)
p <- round(cor.test(df$gZ, df$IQ_total)$p.value,2)
p3 <- ggplot(df, aes(x=gZ, y=IQ_total)) +
  geom_point(col="green4") + 
  geom_smooth(method="lm", col="black") + 
  theme_bw() +
  labs(x = "Global deviance score",
       y = paste0("IQ total \n (",
                  round(sum(is.na(df$IQ_total))/
                        (sum(is.na(df$IQ_total))+
                           sum(!is.na(df$IQ_total)))*100,2),
                  "% NA values)"),
       title = paste0("Timepoint 3, patients r=",r,", p=",p))

ggarrange(p1, p2, p3, ncol = 1, nrow = 3)
rm(df, p1, p2, p3, p, r)
```


\newpage
## Correlating the global Z-score with clinical variables (by timepoint)
## PANSS_total

```{r echo=FALSE, message=FALSE, warning=FALSE, comment=NA, fig.width  = 10, fig.height = 10}
# Global deviance - PANSS_total
# TIMEPOINT 1
df <- subset(df_tps, timepoint==1)
r <- round(as.numeric(cor.test(df$gZ, df$PANSS_total)$estimate),2)
p <- round(cor.test(df$gZ, df$PANSS_total)$p.value,2)
p1 <- ggplot(df, aes(x=gZ, y=PANSS_total)) +
  geom_point(col="green4") + 
  geom_smooth(method="lm", col="black") + 
  theme_bw() +
  labs(x = "Global deviance score",
       y = paste0("PANSS total \n (",
                  round(sum(is.na(df$PANSS_total))/
                        (sum(is.na(df$PANSS_total))+
                           sum(!is.na(df$PANSS_total)))*100,2),
                  "% NA values)"),
       title = paste0("Timepoint 1, patients r=",r,", p=",p))

# TIMEPOINT 2
df <- subset(df_tps, timepoint==2)
r <- round(as.numeric(cor.test(df$gZ, df$PANSS_total)$estimate),2)
p <- round(cor.test(df$gZ, df$PANSS_total)$p.value,2)
p2 <- ggplot(df, aes(x=gZ, y=PANSS_total)) +
  geom_point(col="green4") + 
  geom_smooth(method="lm", col="black") + 
  theme_bw() +
  labs(x = "Global deviance score",
       y = paste0("PANSS total \n (",
                  round(sum(is.na(df$PANSS_total))/
                        (sum(is.na(df$PANSS_total))+
                           sum(!is.na(df$PANSS_total)))*100,2),
                  "% NA values)"),
       title = paste0("Timepoint 2, patients r=",r,", p=",p))

# TIMEPOINT 3
df <- subset(df_tps, timepoint==3)
r <- round(as.numeric(cor.test(df$gZ, df$PANSS_total)$estimate),2)
p <- round(cor.test(df$gZ, df$PANSS_total)$p.value,2)
p3 <- ggplot(df, aes(x=gZ, y=PANSS_total)) +
  geom_point(col="green4") + 
  geom_smooth(method="lm", col="black") + 
  theme_bw() +
  labs(x = "Global deviance score",
       y = paste0("PANSS total \n (",
                  round(sum(is.na(df$PANSS_total))/
                        (sum(is.na(df$PANSS_total))+
                           sum(!is.na(df$PANSS_total)))*100,2),
                  "% NA values)"),
       title = paste0("Timepoint 3, patients r=",r,", p=",p))

ggarrange(p1, p2, p3, ncol = 1, nrow = 3)
rm(df, p1, p2, p3, p, r)
```

\newpage
## Correlating the global Z-score with clinical variables (by timepoint)
## Total P

```{r echo=FALSE, message=FALSE, warning=FALSE, comment=NA, fig.width  = 10, fig.height = 10}
# Global deviance - Total_P
# TIMEPOINT 1
df <- subset(df_tps, timepoint==1)
r <- round(as.numeric(cor.test(df$gZ, df$Total_P)$estimate),2)
p <- round(cor.test(df$gZ, df$Total_P)$p.value,2)
p1 <- ggplot(df, aes(x=gZ, y=Total_P)) +
  geom_point(col="green4") + 
  geom_smooth(method="lm", col="black") + 
  theme_bw() +
  labs(x = "Global deviance score",
       y = paste0("Total P \n (",
                  round(sum(is.na(df$Total_P))/
                        (sum(is.na(df$Total_P))+
                           sum(!is.na(df$Total_P)))*100,2),
                  "% NA values)"),
       title = paste0("Timepoint 1, patients r=",r,", p=",p))

# TIMEPOINT 2
df <- subset(df_tps, timepoint==2)
r <- round(as.numeric(cor.test(df$gZ, df$Total_P)$estimate),2)
p <- round(cor.test(df$gZ, df$Total_P)$p.value,2)
p2 <- ggplot(df, aes(x=gZ, y=Total_P)) +
  geom_point(col="green4") + 
  geom_smooth(method="lm", col="black") + 
  theme_bw() +
  labs(x = "Global deviance score",
       y = paste0("Total P \n (",
                  round(sum(is.na(df$Total_P))/
                        (sum(is.na(df$Total_P))+
                           sum(!is.na(df$Total_P)))*100,2),
                  "% NA values)"),
       title = paste0("Timepoint 2, patients r=",r,", p=",p))

# TIMEPOINT 3
df <- subset(df_tps, timepoint==3)
r <- round(as.numeric(cor.test(df$gZ, df$Total_P)$estimate),2)
p <- round(cor.test(df$gZ, df$Total_P)$p.value,2)
p3 <- ggplot(df, aes(x=gZ, y=Total_P)) +
  geom_point(col="green4") + 
  geom_smooth(method="lm", col="black") + 
  theme_bw() +
  labs(x = "Global deviance score",
       y = paste0("Total P \n (",
                  round(sum(is.na(df$Total_P))/
                        (sum(is.na(df$Total_P))+
                           sum(!is.na(df$Total_P)))*100,2),
                  "% NA values)"),
       title = paste0("Timepoint 3, patients r=",r,", p=",p))

ggarrange(p1, p2, p3, ncol = 1, nrow = 3)
rm(df, p1, p2, p3, p, r)
```

\newpage
## Correlating the global Z-score with clinical variables (by timepoint)
## Total N

```{r echo=FALSE, message=FALSE, warning=FALSE, comment=NA, fig.width  = 10, fig.height = 10}
# Global deviance - Total_N
# TIMEPOINT 1
df <- subset(df_tps, timepoint==1)
r <- round(as.numeric(cor.test(df$gZ, df$Total_N)$estimate),2)
p <- round(cor.test(df$gZ, df$Total_N)$p.value,2)
p1 <- ggplot(df, aes(x=gZ, y=Total_N)) +
  geom_point(col="green4") + 
  geom_smooth(method="lm", col="black") + 
  theme_bw() +
  labs(x = "Global deviance score",
       y = paste0("Total N \n (",
                  round(sum(is.na(df$Total_N))/
                        (sum(is.na(df$Total_N))+
                           sum(!is.na(df$Total_N)))*100,2),
                  "% NA values)"),
       title = paste0("Timepoint 1, patients r=",r,", p=",p))

# TIMEPOINT 2
df <- subset(df_tps, timepoint==2)
r <- round(as.numeric(cor.test(df$gZ, df$Total_N)$estimate),2)
p <- round(cor.test(df$gZ, df$Total_N)$p.value,2)
p2 <- ggplot(df, aes(x=gZ, y=Total_N)) +
  geom_point(col="green4") + 
  geom_smooth(method="lm", col="black") + 
  theme_bw() +
  labs(x = "Global deviance score",
       y = paste0("Total N \n (",
                  round(sum(is.na(df$Total_N))/
                        (sum(is.na(df$Total_N))+
                           sum(!is.na(df$Total_N)))*100,2),
                  "% NA values)"),
       title = paste0("Timepoint 2, patients r=",r,", p=",p))

# TIMEPOINT 3
df <- subset(df_tps, timepoint==3)
r <- round(as.numeric(cor.test(df$gZ, df$Total_N)$estimate),2)
p <- round(cor.test(df$gZ, df$Total_N)$p.value,2)
p3 <- ggplot(df, aes(x=gZ, y=Total_N)) +
  geom_point(col="green4") + 
  geom_smooth(method="lm", col="black") + 
  theme_bw() +
  labs(x = "Global deviance score",
       y = paste0("Total N \n (",
                  round(sum(is.na(df$Total_N))/
                        (sum(is.na(df$Total_N))+
                           sum(!is.na(df$Total_N)))*100,2),
                  "% NA values)"),
       title = paste0("Timepoint 3, patients r=",r,", p=",p))

ggarrange(p1, p2, p3, ncol = 1, nrow = 3)
rm(df, p1, p2, p3, p, r)
```




\newpage
## Correlating the global Z-score with clinical variables (by timepoint)
## Total G

```{r echo=FALSE, message=FALSE, warning=FALSE, comment=NA, fig.width  = 10, fig.height = 10}
# Global deviance - Total_G
# TIMEPOINT 1
df <- subset(df_tps, timepoint==1)
r <- round(as.numeric(cor.test(df$gZ, df$Total_G)$estimate),2)
p <- round(cor.test(df$gZ, df$Total_G)$p.value,2)
p1 <- ggplot(df, aes(x=gZ, y=Total_G)) +
  geom_point(col="green4") + 
  geom_smooth(method="lm", col="black") + 
  theme_bw() +
  labs(x = "Global deviance score",
       y = paste0("Total G \n (",
                  round(sum(is.na(df$Total_G))/
                        (sum(is.na(df$Total_G))+
                           sum(!is.na(df$Total_G)))*100,2),
                  "% NA values)"),
       title = paste0("Timepoint 1, patients r=",r,", p=",p))

# TIMEPOINT 2
df <- subset(df_tps, timepoint==2)
r <- round(as.numeric(cor.test(df$gZ, df$Total_G)$estimate),2)
p <- round(cor.test(df$gZ, df$Total_G)$p.value,2)
p2 <- ggplot(df, aes(x=gZ, y=Total_G)) +
  geom_point(col="green4") + 
  geom_smooth(method="lm", col="black") + 
  theme_bw() +
  labs(x = "Global deviance score",
       y = paste0("Total G \n (",
                  round(sum(is.na(df$Total_G))/
                        (sum(is.na(df$Total_G))+
                           sum(!is.na(df$Total_G)))*100,2),
                  "% NA values)"),
       title = paste0("Timepoint 2, patients r=",r,", p=",p))

# TIMEPOINT 3
df <- subset(df_tps, timepoint==3)
r <- round(as.numeric(cor.test(df$gZ, df$Total_G)$estimate),2)
p <- round(cor.test(df$gZ, df$Total_G)$p.value,2)
p3 <- ggplot(df, aes(x=gZ, y=Total_G)) +
  geom_point(col="green4") + 
  geom_smooth(method="lm", col="black") + 
  theme_bw() +
  labs(x = "Global deviance score",
       y = paste0("Total G \n (",
                  round(sum(is.na(df$Total_G))/
                        (sum(is.na(df$Total_G))+
                           sum(!is.na(df$Total_G)))*100,2),
                  "% NA values)"),
       title = paste0("Timepoint 3, patients r=",r,", p=",p))

ggarrange(p1, p2, p3, ncol = 1, nrow = 3)
rm(df, p1, p2, p3, p, r)
```


\newpage
## Correlating the global Z-score with clinical variables (by timepoint)
## Total N.1

```{r echo=FALSE, message=FALSE, warning=FALSE, comment=NA, fig.width  = 10, fig.height = 10}
# Global deviance - Total_N.1
# TIMEPOINT 1
df <- subset(df_tps, timepoint==1)
r <- round(as.numeric(cor.test(df$gZ, df$Total_N.1)$estimate),2)
p <- round(cor.test(df$gZ, df$Total_N.1)$p.value,2)
p1 <- ggplot(df, aes(x=gZ, y=Total_N.1)) +
  geom_point(col="green4") + 
  geom_smooth(method="lm", col="black") + 
  theme_bw() +
  labs(x = "Global deviance score",
       y = paste0("Total N.1 \n (",
                  round(sum(is.na(df$Total_N.1))/
                        (sum(is.na(df$Total_N.1))+
                           sum(!is.na(df$Total_N.1)))*100,2),
                  "% NA values)"),
       title = paste0("Timepoint 1, patients r=",r,", p=",p))

# TIMEPOINT 2
df <- subset(df_tps, timepoint==2)
r <- round(as.numeric(cor.test(df$gZ, df$Total_N.1)$estimate),2)
p <- round(cor.test(df$gZ, df$Total_N.1)$p.value,2)
p2 <- ggplot(df, aes(x=gZ, y=Total_N.1)) +
  geom_point(col="green4") + 
  geom_smooth(method="lm", col="black") + 
  theme_bw() +
  labs(x = "Global deviance score",
       y = paste0("Total N.1 \n (",
                  round(sum(is.na(df$Total_N.1))/
                        (sum(is.na(df$Total_N.1))+
                           sum(!is.na(df$Total_N.1)))*100,2),
                  "% NA values)"),
       title = paste0("Timepoint 2, patients r=",r,", p=",p))

# TIMEPOINT 3
df <- subset(df_tps, timepoint==3)
r <- round(as.numeric(cor.test(df$gZ, df$Total_N.1)$estimate),2)
p <- round(cor.test(df$gZ, df$Total_N.1)$p.value,2)
p3 <- ggplot(df, aes(x=gZ, y=Total_N.1)) +
  geom_point(col="green4") + 
  geom_smooth(method="lm", col="black") + 
  theme_bw() +
  labs(x = "Global deviance score",
       y = paste0("Total N.1 \n (",
                  round(sum(is.na(df$Total_N.1))/
                        (sum(is.na(df$Total_N.1))+
                           sum(!is.na(df$Total_N.1)))*100,2),
                  "% NA values)"),
       title = paste0("Timepoint 3, patients r=",r,", p=",p))

ggarrange(p1, p2, p3, ncol = 1, nrow = 3)
rm(df, p1, p2, p3, p, r)
```


\newpage
## Correlating the global Z-score with clinical variables (by timepoint)
## Total G.1

```{r echo=FALSE, message=FALSE, warning=FALSE, comment=NA, fig.width  = 10, fig.height = 10}
# Global deviance - Total_G.1
# TIMEPOINT 1
df <- subset(df_tps, timepoint==1)
r <- round(as.numeric(cor.test(df$gZ, df$Total_G.1)$estimate),2)
p <- round(cor.test(df$gZ, df$Total_G.1)$p.value,2)
p1 <- ggplot(df, aes(x=gZ, y=Total_G.1)) +
  geom_point(col="green4") + 
  geom_smooth(method="lm", col="black") + 
  theme_bw() +
  labs(x = "Global deviance score",
       y = paste0("Total G.1 \n (",
                  round(sum(is.na(df$Total_G.1))/
                        (sum(is.na(df$Total_G.1))+
                           sum(!is.na(df$Total_G.1)))*100,2),
                  "% NA values)"),
       title = paste0("Timepoint 1, patients r=",r,", p=",p))

# TIMEPOINT 2
df <- subset(df_tps, timepoint==2)
r <- round(as.numeric(cor.test(df$gZ, df$Total_G.1)$estimate),2)
p <- round(cor.test(df$gZ, df$Total_G.1)$p.value,2)
p2 <- ggplot(df, aes(x=gZ, y=Total_G.1)) +
  geom_point(col="green4") + 
  geom_smooth(method="lm", col="black") + 
  theme_bw() +
  labs(x = "Global deviance score",
       y = paste0("Total G.1 \n (",
                  round(sum(is.na(df$Total_G.1))/
                        (sum(is.na(df$Total_G.1))+
                           sum(!is.na(df$Total_G.1)))*100,2),
                  "% NA values)"),
       title = paste0("Timepoint 2, patients r=",r,", p=",p))

# TIMEPOINT 3
df <- subset(df_tps, timepoint==3)
r <- round(as.numeric(cor.test(df$gZ, df$Total_G.1)$estimate),2)
p <- round(cor.test(df$gZ, df$Total_G.1)$p.value,2)
p3 <- ggplot(df, aes(x=gZ, y=Total_G.1)) +
  geom_point(col="green4") + 
  geom_smooth(method="lm", col="black") + 
  theme_bw() +
  labs(x = "Global deviance score",
       y = paste0("Total G.1 \n (",
                  round(sum(is.na(df$Total_G.1))/
                        (sum(is.na(df$Total_G.1))+
                           sum(!is.na(df$Total_G.1)))*100,2),
                  "% NA values)"),
       title = paste0("Timepoint 3, patients r=",r,", p=",p))

ggarrange(p1, p2, p3, ncol = 1, nrow = 3)
rm(df, p1, p2, p3, p, r)
```


\newpage
## Correlating the global Z-score with clinical variables (by timepoint)
## P1delusions

```{r echo=FALSE, message=FALSE, warning=FALSE, comment=NA, fig.width  = 10, fig.height = 10}
# Global deviance - P1delusions
# TIMEPOINT 1
df <- subset(df_tps, timepoint==1)
r <- round(as.numeric(cor.test(df$gZ, df$P1delusions)$estimate),2)
p <- round(cor.test(df$gZ, df$P1delusions)$p.value,2)
p1 <- ggplot(df, aes(x=gZ, y=P1delusions)) +
  geom_point(col="green4") + 
  geom_smooth(method="lm", col="black") + 
  theme_bw() +
  labs(x = "Global deviance score",
       y = paste0("P1 delusions \n (",
                  round(sum(is.na(df$P1delusions))/
                        (sum(is.na(df$P1delusions))+
                           sum(!is.na(df$P1delusions)))*100,2),
                  "% NA values)"),
       title = paste0("Timepoint 1, patients r=",r,", p=",p))

# TIMEPOINT 2
df <- subset(df_tps, timepoint==2)
r <- round(as.numeric(cor.test(df$gZ, df$P1delusions)$estimate),2)
p <- round(cor.test(df$gZ, df$P1delusions)$p.value,2)
p2 <- ggplot(df, aes(x=gZ, y=P1delusions)) +
  geom_point(col="green4") + 
  geom_smooth(method="lm", col="black") + 
  theme_bw() +
  labs(x = "Global deviance score",
       y = paste0("P1 delusions \n (",
                  round(sum(is.na(df$P1delusions))/
                        (sum(is.na(df$P1delusions))+
                           sum(!is.na(df$P1delusions)))*100,2),
                  "% NA values)"),
       title = paste0("Timepoint 2, patients r=",r,", p=",p))

# TIMEPOINT 3
df <- subset(df_tps, timepoint==3)
r <- round(as.numeric(cor.test(df$gZ, df$P1delusions)$estimate),2)
p <- round(cor.test(df$gZ, df$P1delusions)$p.value,2)
p3 <- ggplot(df, aes(x=gZ, y=P1delusions)) +
  geom_point(col="green4") + 
  geom_smooth(method="lm", col="black") + 
  theme_bw() +
  labs(x = "Global deviance score",
       y = paste0("P1 delusions \n (",
                  round(sum(is.na(df$P1delusions))/
                        (sum(is.na(df$P1delusions))+
                           sum(!is.na(df$P1delusions)))*100,2),
                  "% NA values)"),
       title = paste0("Timepoint 3, patients r=",r,", p=",p))

ggarrange(p1, p2, p3, ncol = 1, nrow = 3)
rm(df, p1, p2, p3, p, r)
```


\newpage
## Correlating the global Z-score with clinical variables (by timepoint)
## P2 conceptual disorganization

```{r echo=FALSE, message=FALSE, warning=FALSE, comment=NA, fig.width  = 10, fig.height = 10}
# Global deviance - P2conceptual_disorganization
# TIMEPOINT 1
df <- subset(df_tps, timepoint==1)
r <- round(as.numeric(cor.test(df$gZ, df$P2conceptual_disorganization)$estimate),2)
p <- round(cor.test(df$gZ, df$P2conceptual_disorganization)$p.value,2)
p1 <- ggplot(df, aes(x=gZ, y=P2conceptual_disorganization)) +
  geom_point(col="green4") + 
  geom_smooth(method="lm", col="black") + 
  theme_bw() +
  labs(x = "Global deviance score",
       y = paste0("P2 conceptual disorganization \n (",
                  round(sum(is.na(df$P2conceptual_disorganization))/
                        (sum(is.na(df$P2conceptual_disorganization))+
                           sum(!is.na(df$P2conceptual_disorganization)))*100,2),
                  "% NA values)"),
       title = paste0("Timepoint 1, patients r=",r,", p=",p))

# TIMEPOINT 2
df <- subset(df_tps, timepoint==2)
r <- round(as.numeric(cor.test(df$gZ, df$P2conceptual_disorganization)$estimate),2)
p <- round(cor.test(df$gZ, df$P2conceptual_disorganization)$p.value,2)
p2 <- ggplot(df, aes(x=gZ, y=P2conceptual_disorganization)) +
  geom_point(col="green4") + 
  geom_smooth(method="lm", col="black") + 
  theme_bw() +
  labs(x = "Global deviance score",
       y = paste0("P2 conceptual disorganization \n (",
                  round(sum(is.na(df$P2conceptual_disorganization))/
                        (sum(is.na(df$P2conceptual_disorganization))+
                           sum(!is.na(df$P2conceptual_disorganization)))*100,2),
                  "% NA values)"),
       title = paste0("Timepoint 2, patients r=",r,", p=",p))

# TIMEPOINT 3
df <- subset(df_tps, timepoint==3)
r <- round(as.numeric(cor.test(df$gZ, df$P2conceptual_disorganization)$estimate),2)
p <- round(cor.test(df$gZ, df$P2conceptual_disorganization)$p.value,2)
p3 <- ggplot(df, aes(x=gZ, y=P2conceptual_disorganization)) +
  geom_point(col="green4") + 
  geom_smooth(method="lm", col="black") + 
  theme_bw() +
  labs(x = "Global deviance score",
       y = paste0("P2 conceptual disorganization \n (",
                  round(sum(is.na(df$P2conceptual_disorganization))/
                        (sum(is.na(df$P2conceptual_disorganization))+
                           sum(!is.na(df$P2conceptual_disorganization)))*100,2),
                  "% NA values)"),
       title = paste0("Timepoint 3, patients r=",r,", p=",p))

ggarrange(p1, p2, p3, ncol = 1, nrow = 3)
rm(df, p1, p2, p3, p, r)
```


\newpage
## Correlating the global Z-score with clinical variables (by timepoint)
## P3 hallucinatory behavior

```{r echo=FALSE, message=FALSE, warning=FALSE, comment=NA, fig.width  = 10, fig.height = 10}
# Global deviance - P3hallucinatory_behavior
# TIMEPOINT 1
df <- subset(df_tps, timepoint==1)
r <- round(as.numeric(cor.test(df$gZ, df$P3hallucinatory_behavior)$estimate),2)
p <- round(cor.test(df$gZ, df$P3hallucinatory_behavior)$p.value,2)
p1 <- ggplot(df, aes(x=gZ, y=P3hallucinatory_behavior)) +
  geom_point(col="green4") + 
  geom_smooth(method="lm", col="black") + 
  theme_bw() +
  labs(x = "Global deviance score",
       y = paste0("P3 hallucinatory behavior \n (",
                  round(sum(is.na(df$P3hallucinatory_behavior))/
                        (sum(is.na(df$P3hallucinatory_behavior))+
                           sum(!is.na(df$P3hallucinatory_behavior)))*100,2),
                  "% NA values)"),
       title = paste0("Timepoint 1, patients r=",r,", p=",p))

# TIMEPOINT 2
df <- subset(df_tps, timepoint==2)
r <- round(as.numeric(cor.test(df$gZ, df$P3hallucinatory_behavior)$estimate),2)
p <- round(cor.test(df$gZ, df$P3hallucinatory_behavior)$p.value,2)
p2 <- ggplot(df, aes(x=gZ, y=P3hallucinatory_behavior)) +
  geom_point(col="green4") + 
  geom_smooth(method="lm", col="black") + 
  theme_bw() +
  labs(x = "Global deviance score",
       y = paste0("P3 hallucinatory behavior \n (",
                  round(sum(is.na(df$P3hallucinatory_behavior))/
                        (sum(is.na(df$P3hallucinatory_behavior))+
                           sum(!is.na(df$P3hallucinatory_behavior)))*100,2),
                  "% NA values)"),
       title = paste0("Timepoint 2, patients r=",r,", p=",p))

# TIMEPOINT 3
df <- subset(df_tps, timepoint==3)
r <- round(as.numeric(cor.test(df$gZ, df$P3hallucinatory_behavior)$estimate),2)
p <- round(cor.test(df$gZ, df$P3hallucinatory_behavior)$p.value,2)
p3 <- ggplot(df, aes(x=gZ, y=P3hallucinatory_behavior)) +
  geom_point(col="green4") + 
  geom_smooth(method="lm", col="black") + 
  theme_bw() +
  labs(x = "Global deviance score",
       y = paste0("P3 hallucinatory behavior \n (",
                  round(sum(is.na(df$P3hallucinatory_behavior))/
                        (sum(is.na(df$P3hallucinatory_behavior))+
                           sum(!is.na(df$P3hallucinatory_behavior)))*100,2),
                  "% NA values)"),
       title = paste0("Timepoint 3, patients r=",r,", p=",p))

ggarrange(p1, p2, p3, ncol = 1, nrow = 3)
rm(df, p1, p2, p3, p, r)
```


\newpage
## Correlating the global Z-score with clinical variables (by timepoint)
## P4 excitement

```{r echo=FALSE, message=FALSE, warning=FALSE, comment=NA, fig.width  = 10, fig.height = 10}
# Global deviance - P4excitement
# TIMEPOINT 1
df <- subset(df_tps, timepoint==1)
r <- round(as.numeric(cor.test(df$gZ, df$P4excitement)$estimate),2)
p <- round(cor.test(df$gZ, df$P4excitement)$p.value,2)
p1 <- ggplot(df, aes(x=gZ, y=P4excitement)) +
  geom_point(col="green4") + 
  geom_smooth(method="lm", col="black") + 
  theme_bw() +
  labs(x = "Global deviance score",
       y = paste0("P4 excitement \n (",
                  round(sum(is.na(df$P4excitement))/
                        (sum(is.na(df$P4excitement))+
                           sum(!is.na(df$P4excitement)))*100,2),
                  "% NA values)"),
       title = paste0("Timepoint 1, patients r=",r,", p=",p))

# TIMEPOINT 2
df <- subset(df_tps, timepoint==2)
r <- round(as.numeric(cor.test(df$gZ, df$P4excitement)$estimate),2)
p <- round(cor.test(df$gZ, df$P4excitement)$p.value,2)
p2 <- ggplot(df, aes(x=gZ, y=P4excitement)) +
  geom_point(col="green4") + 
  geom_smooth(method="lm", col="black") + 
  theme_bw() +
  labs(x = "Global deviance score",
       y = paste0("P4 excitement \n (",
                  round(sum(is.na(df$P4excitement))/
                        (sum(is.na(df$P4excitement))+
                           sum(!is.na(df$P4excitement)))*100,2),
                  "% NA values)"),
       title = paste0("Timepoint 2, patients r=",r,", p=",p))

# TIMEPOINT 3
df <- subset(df_tps, timepoint==3)
r <- round(as.numeric(cor.test(df$gZ, df$P4excitement)$estimate),2)
p <- round(cor.test(df$gZ, df$P4excitement)$p.value,2)
p3 <- ggplot(df, aes(x=gZ, y=P4excitement)) +
  geom_point(col="green4") + 
  geom_smooth(method="lm", col="black") + 
  theme_bw() +
  labs(x = "Global deviance score",
       y = paste0("P4 excitement \n (",
                  round(sum(is.na(df$P4excitement))/
                        (sum(is.na(df$P4excitement))+
                           sum(!is.na(df$P4excitement)))*100,2),
                  "% NA values)"),
       title = paste0("Timepoint 3, patients r=",r,", p=",p))

ggarrange(p1, p2, p3, ncol = 1, nrow = 3)
rm(df, p1, p2, p3, p, r)
```


\newpage
## Correlating the global Z-score with clinical variables (by timepoint)
## P5 grandiosity

```{r echo=FALSE, message=FALSE, warning=FALSE, comment=NA, fig.width  = 10, fig.height = 10}
# Global deviance - P5grandiosity
# TIMEPOINT 1
df <- subset(df_tps, timepoint==1)
r <- round(as.numeric(cor.test(df$gZ, df$P5grandiosity)$estimate),2)
p <- round(cor.test(df$gZ, df$P5grandiosity)$p.value,2)
p1 <- ggplot(df, aes(x=gZ, y=P5grandiosity)) +
  geom_point(col="green4") + 
  geom_smooth(method="lm", col="black") + 
  theme_bw() +
  labs(x = "Global deviance score",
       y = paste0("P5 grandiosity \n (",
                  round(sum(is.na(df$P5grandiosity))/
                        (sum(is.na(df$P5grandiosity))+
                           sum(!is.na(df$P5grandiosity)))*100,2),
                  "% NA values)"),
       title = paste0("Timepoint 1, patients r=",r,", p=",p))

# TIMEPOINT 2
df <- subset(df_tps, timepoint==2)
r <- round(as.numeric(cor.test(df$gZ, df$P5grandiosity)$estimate),2)
p <- round(cor.test(df$gZ, df$P5grandiosity)$p.value,2)
p2 <- ggplot(df, aes(x=gZ, y=P5grandiosity)) +
  geom_point(col="green4") + 
  geom_smooth(method="lm", col="black") + 
  theme_bw() +
  labs(x = "Global deviance score",
       y = paste0("P5 grandiosity \n (",
                  round(sum(is.na(df$P5grandiosity))/
                        (sum(is.na(df$P5grandiosity))+
                           sum(!is.na(df$P5grandiosity)))*100,2),
                  "% NA values)"),
       title = paste0("Timepoint 2, patients r=",r,", p=",p))

# TIMEPOINT 3
df <- subset(df_tps, timepoint==3)
r <- round(as.numeric(cor.test(df$gZ, df$P5grandiosity)$estimate),2)
p <- round(cor.test(df$gZ, df$P5grandiosity)$p.value,2)
p3 <- ggplot(df, aes(x=gZ, y=P5grandiosity)) +
  geom_point(col="green4") + 
  geom_smooth(method="lm", col="black") + 
  theme_bw() +
  labs(x = "Global deviance score",
       y = paste0("P5 grandiosity \n (",
                  round(sum(is.na(df$P5grandiosity))/
                        (sum(is.na(df$P5grandiosity))+
                           sum(!is.na(df$P5grandiosity)))*100,2),
                  "% NA values)"),
       title = paste0("Timepoint 3, patients r=",r,", p=",p))

ggarrange(p1, p2, p3, ncol = 1, nrow = 3)
rm(df, p1, p2, p3, p, r)
```


\newpage
## Correlating the global Z-score with clinical variables (by timepoint)
## P6 suspiciousness persecution

```{r echo=FALSE, message=FALSE, warning=FALSE, comment=NA, fig.width  = 10, fig.height = 10}
# Global deviance - P6suspiciousness_persecution
# TIMEPOINT 1
df <- subset(df_tps, timepoint==1)
r <- round(as.numeric(cor.test(df$gZ, df$P6suspiciousness_persecution)$estimate),2)
p <- round(cor.test(df$gZ, df$P6suspiciousness_persecution)$p.value,2)
p1 <- ggplot(df, aes(x=gZ, y=P6suspiciousness_persecution)) +
  geom_point(col="green4") + 
  geom_smooth(method="lm", col="black") + 
  theme_bw() +
  labs(x = "Global deviance score",
       y = paste0("P6 suspiciousness persecution \n (",
                  round(sum(is.na(df$P6suspiciousness_persecution))/
                        (sum(is.na(df$P6suspiciousness_persecution))+
                           sum(!is.na(df$P6suspiciousness_persecution)))*100,2),
                  "% NA values)"),
       title = paste0("Timepoint 1, patients r=",r,", p=",p))

# TIMEPOINT 2
df <- subset(df_tps, timepoint==2)
r <- round(as.numeric(cor.test(df$gZ, df$P6suspiciousness_persecution)$estimate),2)
p <- round(cor.test(df$gZ, df$P6suspiciousness_persecution)$p.value,2)
p2 <- ggplot(df, aes(x=gZ, y=P6suspiciousness_persecution)) +
  geom_point(col="green4") + 
  geom_smooth(method="lm", col="black") + 
  theme_bw() +
  labs(x = "Global deviance score",
       y = paste0("P6 suspiciousness persecution \n (",
                  round(sum(is.na(df$P6suspiciousness_persecution))/
                        (sum(is.na(df$P6suspiciousness_persecution))+
                           sum(!is.na(df$P6suspiciousness_persecution)))*100,2),
                  "% NA values)"),
       title = paste0("Timepoint 2, patients r=",r,", p=",p))

# TIMEPOINT 3
df <- subset(df_tps, timepoint==3)
r <- round(as.numeric(cor.test(df$gZ, df$P6suspiciousness_persecution)$estimate),2)
p <- round(cor.test(df$gZ, df$P6suspiciousness_persecution)$p.value,2)
p3 <- ggplot(df, aes(x=gZ, y=P6suspiciousness_persecution)) +
  geom_point(col="green4") + 
  geom_smooth(method="lm", col="black") + 
  theme_bw() +
  labs(x = "Global deviance score",
       y = paste0("P6 suspiciousness persecution \n (",
                  round(sum(is.na(df$P6suspiciousness_persecution))/
                        (sum(is.na(df$P6suspiciousness_persecution))+
                           sum(!is.na(df$P6suspiciousness_persecution)))*100,2),
                  "% NA values)"),
       title = paste0("Timepoint 3, patients r=",r,", p=",p))

ggarrange(p1, p2, p3, ncol = 1, nrow = 3)
rm(df, p1, p2, p3, p, r)
```


\newpage
## Correlating the global Z-score with clinical variables (by timepoint)
## P7 hostility

```{r echo=FALSE, message=FALSE, warning=FALSE, comment=NA, fig.width  = 10, fig.height = 10}
# Global deviance - P7hostility
# TIMEPOINT 1
df <- subset(df_tps, timepoint==1)
r <- round(as.numeric(cor.test(df$gZ, df$P7hostility)$estimate),2)
p <- round(cor.test(df$gZ, df$P7hostility)$p.value,2)
p1 <- ggplot(df, aes(x=gZ, y=P7hostility)) +
  geom_point(col="green4") + 
  geom_smooth(method="lm", col="black") + 
  theme_bw() +
  labs(x = "Global deviance score",
       y = paste0("P7 hostility \n (",
                  round(sum(is.na(df$P7hostility))/
                        (sum(is.na(df$P7hostility))+
                           sum(!is.na(df$P7hostility)))*100,2),
                  "% NA values)"),
       title = paste0("Timepoint 1, patients r=",r,", p=",p))

# TIMEPOINT 2
df <- subset(df_tps, timepoint==2)
r <- round(as.numeric(cor.test(df$gZ, df$P7hostility)$estimate),2)
p <- round(cor.test(df$gZ, df$P7hostility)$p.value,2)
p2 <- ggplot(df, aes(x=gZ, y=P7hostility)) +
  geom_point(col="green4") + 
  geom_smooth(method="lm", col="black") + 
  theme_bw() +
  labs(x = "Global deviance score",
       y = paste0("P7 hostility \n (",
                  round(sum(is.na(df$P7hostility))/
                        (sum(is.na(df$P7hostility))+
                           sum(!is.na(df$P7hostility)))*100,2),
                  "% NA values)"),
       title = paste0("Timepoint 2, patients r=",r,", p=",p))

# TIMEPOINT 3
df <- subset(df_tps, timepoint==3)
r <- round(as.numeric(cor.test(df$gZ, df$P7hostility)$estimate),2)
p <- round(cor.test(df$gZ, df$P7hostility)$p.value,2)
p3 <- ggplot(df, aes(x=gZ, y=P7hostility)) +
  geom_point(col="green4") + 
  geom_smooth(method="lm", col="black") + 
  theme_bw() +
  labs(x = "Global deviance score",
       y = paste0("P7 hostility \n (",
                  round(sum(is.na(df$P7hostility))/
                        (sum(is.na(df$P7hostility))+
                           sum(!is.na(df$P7hostility)))*100,2),
                  "% NA values)"),
       title = paste0("Timepoint 3, patients r=",r,", p=",p))

ggarrange(p1, p2, p3, ncol = 1, nrow = 3)
rm(df, p1, p2, p3, p, r)
```


\newpage
## Correlating the global Z-score with clinical variables (by timepoint)
## N1 blunted affect

```{r echo=FALSE, message=FALSE, warning=FALSE, comment=NA, fig.width  = 10, fig.height = 10}
# Global deviance - N1blunted_affect
# TIMEPOINT 1
df <- subset(df_tps, timepoint==1)
r <- round(as.numeric(cor.test(df$gZ, df$N1blunted_affect)$estimate),2)
p <- round(cor.test(df$gZ, df$N1blunted_affect)$p.value,2)
p1 <- ggplot(df, aes(x=gZ, y=N1blunted_affect)) +
  geom_point(col="green4") + 
  geom_smooth(method="lm", col="black") + 
  theme_bw() +
  labs(x = "Global deviance score",
       y = paste0("N1 blunted affect \n (",
                  round(sum(is.na(df$N1blunted_affect))/
                        (sum(is.na(df$N1blunted_affect))+
                           sum(!is.na(df$N1blunted_affect)))*100,2),
                  "% NA values)"),
       title = paste0("Timepoint 1, patients r=",r,", p=",p))

# TIMEPOINT 2
df <- subset(df_tps, timepoint==2)
r <- round(as.numeric(cor.test(df$gZ, df$N1blunted_affect)$estimate),2)
p <- round(cor.test(df$gZ, df$N1blunted_affect)$p.value,2)
p2 <- ggplot(df, aes(x=gZ, y=N1blunted_affect)) +
  geom_point(col="green4") + 
  geom_smooth(method="lm", col="black") + 
  theme_bw() +
  labs(x = "Global deviance score",
       y = paste0("N1 blunted affect \n (",
                  round(sum(is.na(df$N1blunted_affect))/
                        (sum(is.na(df$N1blunted_affect))+
                           sum(!is.na(df$N1blunted_affect)))*100,2),
                  "% NA values)"),
       title = paste0("Timepoint 2, patients r=",r,", p=",p))

# TIMEPOINT 3
df <- subset(df_tps, timepoint==3)
r <- round(as.numeric(cor.test(df$gZ, df$N1blunted_affect)$estimate),2)
p <- round(cor.test(df$gZ, df$N1blunted_affect)$p.value,2)
p3 <- ggplot(df, aes(x=gZ, y=N1blunted_affect)) +
  geom_point(col="green4") + 
  geom_smooth(method="lm", col="black") + 
  theme_bw() +
  labs(x = "Global deviance score",
       y = paste0("N1 blunted affect \n (",
                  round(sum(is.na(df$N1blunted_affect))/
                        (sum(is.na(df$N1blunted_affect))+
                           sum(!is.na(df$N1blunted_affect)))*100,2),
                  "% NA values)"),
       title = paste0("Timepoint 3, patients r=",r,", p=",p))

ggarrange(p1, p2, p3, ncol = 1, nrow = 3)
rm(df, p1, p2, p3, p, r)
```


\newpage
## Correlating the global Z-score with clinical variables (by timepoint)
## N2 emotional withdrawal

```{r echo=FALSE, message=FALSE, warning=FALSE, comment=NA, fig.width  = 10, fig.height = 10}
# Global deviance - N2emotional_withdrawal
# TIMEPOINT 1
df <- subset(df_tps, timepoint==1)
r <- round(as.numeric(cor.test(df$gZ, df$N2emotional_withdrawal)$estimate),2)
p <- round(cor.test(df$gZ, df$N2emotional_withdrawal)$p.value,2)
p1 <- ggplot(df, aes(x=gZ, y=N2emotional_withdrawal)) +
  geom_point(col="green4") + 
  geom_smooth(method="lm", col="black") + 
  theme_bw() +
  labs(x = "Global deviance score",
       y = paste0("N2 emotional withdrawal \n (",
                  round(sum(is.na(df$N2emotional_withdrawal))/
                        (sum(is.na(df$N2emotional_withdrawal))+
                           sum(!is.na(df$N2emotional_withdrawal)))*100,2),
                  "% NA values)"),
       title = paste0("Timepoint 1, patients r=",r,", p=",p))

# TIMEPOINT 2
df <- subset(df_tps, timepoint==2)
r <- round(as.numeric(cor.test(df$gZ, df$N2emotional_withdrawal)$estimate),2)
p <- round(cor.test(df$gZ, df$N2emotional_withdrawal)$p.value,2)
p2 <- ggplot(df, aes(x=gZ, y=N2emotional_withdrawal)) +
  geom_point(col="green4") + 
  geom_smooth(method="lm", col="black") + 
  theme_bw() +
  labs(x = "Global deviance score",
       y = paste0("N2 emotional withdrawal \n (",
                  round(sum(is.na(df$N2emotional_withdrawal))/
                        (sum(is.na(df$N2emotional_withdrawal))+
                           sum(!is.na(df$N2emotional_withdrawal)))*100,2),
                  "% NA values)"),
       title = paste0("Timepoint 2, patients r=",r,", p=",p))

# TIMEPOINT 3
df <- subset(df_tps, timepoint==3)
r <- round(as.numeric(cor.test(df$gZ, df$N2emotional_withdrawal)$estimate),2)
p <- round(cor.test(df$gZ, df$N2emotional_withdrawal)$p.value,2)
p3 <- ggplot(df, aes(x=gZ, y=N2emotional_withdrawal)) +
  geom_point(col="green4") + 
  geom_smooth(method="lm", col="black") + 
  theme_bw() +
  labs(x = "Global deviance score",
       y = paste0("N2 emotional withdrawal \n (",
                  round(sum(is.na(df$N2emotional_withdrawal))/
                        (sum(is.na(df$N2emotional_withdrawal))+
                           sum(!is.na(df$N2emotional_withdrawal)))*100,2),
                  "% NA values)"),
       title = paste0("Timepoint 3, patients r=",r,", p=",p))

ggarrange(p1, p2, p3, ncol = 1, nrow = 3)
rm(df, p1, p2, p3, p, r)
```


\newpage
## Correlating the global Z-score with clinical variables (by timepoint)
## N3poor_rapport

```{r echo=FALSE, message=FALSE, warning=FALSE, comment=NA, fig.width  = 10, fig.height = 10}
# Global deviance - N3poor_rapport
# TIMEPOINT 1
df <- subset(df_tps, timepoint==1)
r <- round(as.numeric(cor.test(df$gZ, df$N3poor_rapport)$estimate),2)
p <- round(cor.test(df$gZ, df$N3poor_rapport)$p.value,2)
p1 <- ggplot(df, aes(x=gZ, y=N3poor_rapport)) +
  geom_point(col="green4") + 
  geom_smooth(method="lm", col="black") + 
  theme_bw() +
  labs(x = "Global deviance score",
       y = paste0("N3poor_rapport \n (",
                  round(sum(is.na(df$N3poor_rapport))/
                        (sum(is.na(df$N3poor_rapport))+
                           sum(!is.na(df$N3poor_rapport)))*100,2),
                  "% NA values)"),
       title = paste0("Timepoint 1, patients r=",r,", p=",p))

# TIMEPOINT 2
df <- subset(df_tps, timepoint==2)
r <- round(as.numeric(cor.test(df$gZ, df$N3poor_rapport)$estimate),2)
p <- round(cor.test(df$gZ, df$N3poor_rapport)$p.value,2)
p2 <- ggplot(df, aes(x=gZ, y=N3poor_rapport)) +
  geom_point(col="green4") + 
  geom_smooth(method="lm", col="black") + 
  theme_bw() +
  labs(x = "Global deviance score",
       y = paste0("N3poor_rapport \n (",
                  round(sum(is.na(df$N3poor_rapport))/
                        (sum(is.na(df$N3poor_rapport))+
                           sum(!is.na(df$N3poor_rapport)))*100,2),
                  "% NA values)"),
       title = paste0("Timepoint 2, patients r=",r,", p=",p))

# TIMEPOINT 3
df <- subset(df_tps, timepoint==3)
r <- round(as.numeric(cor.test(df$gZ, df$N3poor_rapport)$estimate),2)
p <- round(cor.test(df$gZ, df$N3poor_rapport)$p.value,2)
p3 <- ggplot(df, aes(x=gZ, y=N3poor_rapport)) +
  geom_point(col="green4") + 
  geom_smooth(method="lm", col="black") + 
  theme_bw() +
  labs(x = "Global deviance score",
       y = paste0("N3poor_rapport \n (",
                  round(sum(is.na(df$N3poor_rapport))/
                        (sum(is.na(df$N3poor_rapport))+
                           sum(!is.na(df$N3poor_rapport)))*100,2),
                  "% NA values)"),
       title = paste0("Timepoint 3, patients r=",r,", p=",p))

ggarrange(p1, p2, p3, ncol = 1, nrow = 3)
rm(df, p1, p2, p3, p, r)
```


\newpage
## Correlating the global Z-score with clinical variables (by timepoint)
## N4passive_apathetic_social

```{r echo=FALSE, message=FALSE, warning=FALSE, comment=NA, fig.width  = 10, fig.height = 10}
# Global deviance - N4passive_apathetic_social
# TIMEPOINT 1
df <- subset(df_tps, timepoint==1)
r <- round(as.numeric(cor.test(df$gZ, df$N4passive_apathetic_social)$estimate),2)
p <- round(cor.test(df$gZ, df$N4passive_apathetic_social)$p.value,2)
p1 <- ggplot(df, aes(x=gZ, y=N4passive_apathetic_social)) +
  geom_point(col="green4") + 
  geom_smooth(method="lm", col="black") + 
  theme_bw() +
  labs(x = "Global deviance score",
       y = paste0("N4passive_apathetic_social \n (",
                  round(sum(is.na(df$N4passive_apathetic_social))/
                        (sum(is.na(df$N4passive_apathetic_social))+
                           sum(!is.na(df$N4passive_apathetic_social)))*100,2),
                  "% NA values)"),
       title = paste0("Timepoint 1, patients r=",r,", p=",p))

# TIMEPOINT 2
df <- subset(df_tps, timepoint==2)
r <- round(as.numeric(cor.test(df$gZ, df$N4passive_apathetic_social)$estimate),2)
p <- round(cor.test(df$gZ, df$N4passive_apathetic_social)$p.value,2)
p2 <- ggplot(df, aes(x=gZ, y=N4passive_apathetic_social)) +
  geom_point(col="green4") + 
  geom_smooth(method="lm", col="black") + 
  theme_bw() +
  labs(x = "Global deviance score",
       y = paste0("N4passive_apathetic_social \n (",
                  round(sum(is.na(df$N4passive_apathetic_social))/
                        (sum(is.na(df$N4passive_apathetic_social))+
                           sum(!is.na(df$N4passive_apathetic_social)))*100,2),
                  "% NA values)"),
       title = paste0("Timepoint 2, patients r=",r,", p=",p))

# TIMEPOINT 3
df <- subset(df_tps, timepoint==3)
r <- round(as.numeric(cor.test(df$gZ, df$N4passive_apathetic_social)$estimate),2)
p <- round(cor.test(df$gZ, df$N4passive_apathetic_social)$p.value,2)
p3 <- ggplot(df, aes(x=gZ, y=N4passive_apathetic_social)) +
  geom_point(col="green4") + 
  geom_smooth(method="lm", col="black") + 
  theme_bw() +
  labs(x = "Global deviance score",
       y = paste0("N4passive_apathetic_social \n (",
                  round(sum(is.na(df$N4passive_apathetic_social))/
                        (sum(is.na(df$N4passive_apathetic_social))+
                           sum(!is.na(df$N4passive_apathetic_social)))*100,2),
                  "% NA values)"),
       title = paste0("Timepoint 3, patients r=",r,", p=",p))

ggarrange(p1, p2, p3, ncol = 1, nrow = 3)
rm(df, p1, p2, p3, p, r)
```

\newpage
## Correlating the global Z-score with clinical variables (by timepoint)
## N5difficulty_abstract_thinking

```{r echo=FALSE, message=FALSE, warning=FALSE, comment=NA, fig.width  = 10, fig.height = 10}
# Global deviance - N5difficulty_abstract_thinking
# TIMEPOINT 1
df <- subset(df_tps, timepoint==1)
r <- round(as.numeric(cor.test(df$gZ, df$N5difficulty_abstract_thinking)$estimate),2)
p <- round(cor.test(df$gZ, df$N5difficulty_abstract_thinking)$p.value,2)
p1 <- ggplot(df, aes(x=gZ, y=N5difficulty_abstract_thinking)) +
  geom_point(col="green4") + 
  geom_smooth(method="lm", col="black") + 
  theme_bw() +
  labs(x = "Global deviance score",
       y = paste0("N5difficulty_abstract_thinking \n (",
                  round(sum(is.na(df$N5difficulty_abstract_thinking))/
                        (sum(is.na(df$N5difficulty_abstract_thinking))+
                           sum(!is.na(df$N5difficulty_abstract_thinking)))*100,2),
                  "% NA values)"),
       title = paste0("Timepoint 1, patients r=",r,", p=",p))

# TIMEPOINT 2
df <- subset(df_tps, timepoint==2)
r <- round(as.numeric(cor.test(df$gZ, df$N5difficulty_abstract_thinking)$estimate),2)
p <- round(cor.test(df$gZ, df$N5difficulty_abstract_thinking)$p.value,2)
p2 <- ggplot(df, aes(x=gZ, y=N5difficulty_abstract_thinking)) +
  geom_point(col="green4") + 
  geom_smooth(method="lm", col="black") + 
  theme_bw() +
  labs(x = "Global deviance score",
       y = paste0("N5difficulty_abstract_thinking \n (",
                  round(sum(is.na(df$N5difficulty_abstract_thinking))/
                        (sum(is.na(df$N5difficulty_abstract_thinking))+
                           sum(!is.na(df$N5difficulty_abstract_thinking)))*100,2),
                  "% NA values)"),
       title = paste0("Timepoint 2, patients r=",r,", p=",p))

# TIMEPOINT 3
df <- subset(df_tps, timepoint==3)
r <- round(as.numeric(cor.test(df$gZ, df$N5difficulty_abstract_thinking)$estimate),2)
p <- round(cor.test(df$gZ, df$N5difficulty_abstract_thinking)$p.value,2)
p3 <- ggplot(df, aes(x=gZ, y=N5difficulty_abstract_thinking)) +
  geom_point(col="green4") + 
  geom_smooth(method="lm", col="black") + 
  theme_bw() +
  labs(x = "Global deviance score",
       y = paste0("N5difficulty_abstract_thinking \n (",
                  round(sum(is.na(df$N5difficulty_abstract_thinking))/
                        (sum(is.na(df$N5difficulty_abstract_thinking))+
                           sum(!is.na(df$N5difficulty_abstract_thinking)))*100,2),
                  "% NA values)"),
       title = paste0("Timepoint 3, patients r=",r,", p=",p))

ggarrange(p1, p2, p3, ncol = 1, nrow = 3)
rm(df, p1, p2, p3, p, r)
```

\newpage
## Correlating the global Z-score with clinical variables (by timepoint)
## N6lack_of_spontaneity

```{r echo=FALSE, message=FALSE, warning=FALSE, comment=NA, fig.width  = 10, fig.height = 10}
# Global deviance - N6lack_of_spontaneity
# TIMEPOINT 1
df <- subset(df_tps, timepoint==1)
r <- round(as.numeric(cor.test(df$gZ, df$N6lack_of_spontaneity)$estimate),2)
p <- round(cor.test(df$gZ, df$N6lack_of_spontaneity)$p.value,2)
p1 <- ggplot(df, aes(x=gZ, y=N6lack_of_spontaneity)) +
  geom_point(col="green4") + 
  geom_smooth(method="lm", col="black") + 
  theme_bw() +
  labs(x = "Global deviance score",
       y = paste0("N6lack_of_spontaneity \n (",
                  round(sum(is.na(df$N6lack_of_spontaneity))/
                        (sum(is.na(df$N6lack_of_spontaneity))+
                           sum(!is.na(df$N6lack_of_spontaneity)))*100,2),
                  "% NA values)"),
       title = paste0("Timepoint 1, patients r=",r,", p=",p))

# TIMEPOINT 2
df <- subset(df_tps, timepoint==2)
r <- round(as.numeric(cor.test(df$gZ, df$N6lack_of_spontaneity)$estimate),2)
p <- round(cor.test(df$gZ, df$N6lack_of_spontaneity)$p.value,2)
p2 <- ggplot(df, aes(x=gZ, y=N6lack_of_spontaneity)) +
  geom_point(col="green4") + 
  geom_smooth(method="lm", col="black") + 
  theme_bw() +
  labs(x = "Global deviance score",
       y = paste0("N6lack_of_spontaneity \n (",
                  round(sum(is.na(df$N6lack_of_spontaneity))/
                        (sum(is.na(df$N6lack_of_spontaneity))+
                           sum(!is.na(df$N6lack_of_spontaneity)))*100,2),
                  "% NA values)"),
       title = paste0("Timepoint 2, patients r=",r,", p=",p))

# TIMEPOINT 3
df <- subset(df_tps, timepoint==3)
r <- round(as.numeric(cor.test(df$gZ, df$N6lack_of_spontaneity)$estimate),2)
p <- round(cor.test(df$gZ, df$N6lack_of_spontaneity)$p.value,2)
p3 <- ggplot(df, aes(x=gZ, y=N6lack_of_spontaneity)) +
  geom_point(col="green4") + 
  geom_smooth(method="lm", col="black") + 
  theme_bw() +
  labs(x = "Global deviance score",
       y = paste0("N6lack_of_spontaneity \n (",
                  round(sum(is.na(df$N6lack_of_spontaneity))/
                        (sum(is.na(df$N6lack_of_spontaneity))+
                           sum(!is.na(df$N6lack_of_spontaneity)))*100,2),
                  "% NA values)"),
       title = paste0("Timepoint 3, patients r=",r,", p=",p))

ggarrange(p1, p2, p3, ncol = 1, nrow = 3)
rm(df, p1, p2, p3, p, r)
```

\newpage
## Correlating the global Z-score with clinical variables (by timepoint)
## N7stereotyping_thinking

```{r echo=FALSE, message=FALSE, warning=FALSE, comment=NA, fig.width  = 10, fig.height = 10}
# Global deviance - N7stereotyping_thinking
# TIMEPOINT 1
df <- subset(df_tps, timepoint==1)
r <- round(as.numeric(cor.test(df$gZ, df$N7stereotyping_thinking)$estimate),2)
p <- round(cor.test(df$gZ, df$N7stereotyping_thinking)$p.value,2)
p1 <- ggplot(df, aes(x=gZ, y=N7stereotyping_thinking)) +
  geom_point(col="green4") + 
  geom_smooth(method="lm", col="black") + 
  theme_bw() +
  labs(x = "Global deviance score",
       y = paste0("N7stereotyping_thinking \n (",
                  round(sum(is.na(df$N7stereotyping_thinking))/
                        (sum(is.na(df$N7stereotyping_thinking))+
                           sum(!is.na(df$N7stereotyping_thinking)))*100,2),
                  "% NA values)"),
       title = paste0("Timepoint 1, patients r=",r,", p=",p))

# TIMEPOINT 2
df <- subset(df_tps, timepoint==2)
r <- round(as.numeric(cor.test(df$gZ, df$N7stereotyping_thinking)$estimate),2)
p <- round(cor.test(df$gZ, df$N7stereotyping_thinking)$p.value,2)
p2 <- ggplot(df, aes(x=gZ, y=N7stereotyping_thinking)) +
  geom_point(col="green4") + 
  geom_smooth(method="lm", col="black") + 
  theme_bw() +
  labs(x = "Global deviance score",
       y = paste0("N7stereotyping_thinking \n (",
                  round(sum(is.na(df$N7stereotyping_thinking))/
                        (sum(is.na(df$N7stereotyping_thinking))+
                           sum(!is.na(df$N7stereotyping_thinking)))*100,2),
                  "% NA values)"),
       title = paste0("Timepoint 2, patients r=",r,", p=",p))

# TIMEPOINT 3
df <- subset(df_tps, timepoint==3)
r <- round(as.numeric(cor.test(df$gZ, df$N7stereotyping_thinking)$estimate),2)
p <- round(cor.test(df$gZ, df$N7stereotyping_thinking)$p.value,2)
p3 <- ggplot(df, aes(x=gZ, y=N7stereotyping_thinking)) +
  geom_point(col="green4") + 
  geom_smooth(method="lm", col="black") + 
  theme_bw() +
  labs(x = "Global deviance score",
       y = paste0("N7stereotyping_thinking \n (",
                  round(sum(is.na(df$N7stereotyping_thinking))/
                        (sum(is.na(df$N7stereotyping_thinking))+
                           sum(!is.na(df$N7stereotyping_thinking)))*100,2),
                  "% NA values)"),
       title = paste0("Timepoint 3, patients r=",r,", p=",p))

ggarrange(p1, p2, p3, ncol = 1, nrow = 3)
rm(df, p1, p2, p3, p, r)
```

\newpage
## Correlating the global Z-score with clinical variables (by timepoint)
## G1somatic_concern

```{r echo=FALSE, message=FALSE, warning=FALSE, comment=NA, fig.width  = 10, fig.height = 10}
# Global deviance - G1somatic_concern
# TIMEPOINT 1
df <- subset(df_tps, timepoint==1)
r <- round(as.numeric(cor.test(df$gZ, df$G1somatic_concern)$estimate),2)
p <- round(cor.test(df$gZ, df$G1somatic_concern)$p.value,2)
p1 <- ggplot(df, aes(x=gZ, y=G1somatic_concern)) +
  geom_point(col="green4") + 
  geom_smooth(method="lm", col="black") + 
  theme_bw() +
  labs(x = "Global deviance score",
       y = paste0("G1somatic_concern \n (",
                  round(sum(is.na(df$G1somatic_concern))/
                        (sum(is.na(df$G1somatic_concern))+
                           sum(!is.na(df$G1somatic_concern)))*100,2),
                  "% NA values)"),
       title = paste0("Timepoint 1, patients r=",r,", p=",p))

# TIMEPOINT 2
df <- subset(df_tps, timepoint==2)
r <- round(as.numeric(cor.test(df$gZ, df$G1somatic_concern)$estimate),2)
p <- round(cor.test(df$gZ, df$G1somatic_concern)$p.value,2)
p2 <- ggplot(df, aes(x=gZ, y=G1somatic_concern)) +
  geom_point(col="green4") + 
  geom_smooth(method="lm", col="black") + 
  theme_bw() +
  labs(x = "Global deviance score",
       y = paste0("G1somatic_concern \n (",
                  round(sum(is.na(df$G1somatic_concern))/
                        (sum(is.na(df$G1somatic_concern))+
                           sum(!is.na(df$G1somatic_concern)))*100,2),
                  "% NA values)"),
       title = paste0("Timepoint 2, patients r=",r,", p=",p))

# TIMEPOINT 3
df <- subset(df_tps, timepoint==3)
r <- round(as.numeric(cor.test(df$gZ, df$G1somatic_concern)$estimate),2)
p <- round(cor.test(df$gZ, df$G1somatic_concern)$p.value,2)
p3 <- ggplot(df, aes(x=gZ, y=G1somatic_concern)) +
  geom_point(col="green4") + 
  geom_smooth(method="lm", col="black") + 
  theme_bw() +
  labs(x = "Global deviance score",
       y = paste0("G1somatic_concern \n (",
                  round(sum(is.na(df$G1somatic_concern))/
                        (sum(is.na(df$G1somatic_concern))+
                           sum(!is.na(df$G1somatic_concern)))*100,2),
                  "% NA values)"),
       title = paste0("Timepoint 3, patients r=",r,", p=",p))

ggarrange(p1, p2, p3, ncol = 1, nrow = 3)
rm(df, p1, p2, p3, p, r)
```

\newpage
## Correlating the global Z-score with clinical variables (by timepoint)
## G2anxiety

```{r echo=FALSE, message=FALSE, warning=FALSE, comment=NA, fig.width  = 10, fig.height = 10}
# Global deviance - G2anxiety
# TIMEPOINT 1
df <- subset(df_tps, timepoint==1)
r <- round(as.numeric(cor.test(df$gZ, df$G2anxiety)$estimate),2)
p <- round(cor.test(df$gZ, df$G2anxiety)$p.value,2)
p1 <- ggplot(df, aes(x=gZ, y=G2anxiety)) +
  geom_point(col="green4") + 
  geom_smooth(method="lm", col="black") + 
  theme_bw() +
  labs(x = "Global deviance score",
       y = paste0("G2anxiety \n (",
                  round(sum(is.na(df$G2anxiety))/
                        (sum(is.na(df$G2anxiety))+
                           sum(!is.na(df$G2anxiety)))*100,2),
                  "% NA values)"),
       title = paste0("Timepoint 1, patients r=",r,", p=",p))

# TIMEPOINT 2
df <- subset(df_tps, timepoint==2)
r <- round(as.numeric(cor.test(df$gZ, df$G2anxiety)$estimate),2)
p <- round(cor.test(df$gZ, df$G2anxiety)$p.value,2)
p2 <- ggplot(df, aes(x=gZ, y=G2anxiety)) +
  geom_point(col="green4") + 
  geom_smooth(method="lm", col="black") + 
  theme_bw() +
  labs(x = "Global deviance score",
       y = paste0("G2anxiety \n (",
                  round(sum(is.na(df$G2anxiety))/
                        (sum(is.na(df$G2anxiety))+
                           sum(!is.na(df$G2anxiety)))*100,2),
                  "% NA values)"),
       title = paste0("Timepoint 2, patients r=",r,", p=",p))

# TIMEPOINT 3
df <- subset(df_tps, timepoint==3)
r <- round(as.numeric(cor.test(df$gZ, df$G2anxiety)$estimate),2)
p <- round(cor.test(df$gZ, df$G2anxiety)$p.value,2)
p3 <- ggplot(df, aes(x=gZ, y=G2anxiety)) +
  geom_point(col="green4") + 
  geom_smooth(method="lm", col="black") + 
  theme_bw() +
  labs(x = "Global deviance score",
       y = paste0("G2anxiety \n (",
                  round(sum(is.na(df$G2anxiety))/
                        (sum(is.na(df$G2anxiety))+
                           sum(!is.na(df$G2anxiety)))*100,2),
                  "% NA values)"),
       title = paste0("Timepoint 3, patients r=",r,", p=",p))

ggarrange(p1, p2, p3, ncol = 1, nrow = 3)
rm(df, p1, p2, p3, p, r)
```

\newpage
## Correlating the global Z-score with clinical variables (by timepoint)
## G3guilt_feelings

```{r echo=FALSE, message=FALSE, warning=FALSE, comment=NA, fig.width  = 10, fig.height = 10}
# Global deviance - G3guilt_feelings
# TIMEPOINT 1
df <- subset(df_tps, timepoint==1)
r <- round(as.numeric(cor.test(df$gZ, df$G3guilt_feelings)$estimate),2)
p <- round(cor.test(df$gZ, df$G3guilt_feelings)$p.value,2)
p1 <- ggplot(df, aes(x=gZ, y=G3guilt_feelings)) +
  geom_point(col="green4") + 
  geom_smooth(method="lm", col="black") + 
  theme_bw() +
  labs(x = "Global deviance score",
       y = paste0("G3guilt_feelings \n (",
                  round(sum(is.na(df$G3guilt_feelings))/
                        (sum(is.na(df$G3guilt_feelings))+
                           sum(!is.na(df$G3guilt_feelings)))*100,2),
                  "% NA values)"),
       title = paste0("Timepoint 1, patients r=",r,", p=",p))

# TIMEPOINT 2
df <- subset(df_tps, timepoint==2)
r <- round(as.numeric(cor.test(df$gZ, df$G3guilt_feelings)$estimate),2)
p <- round(cor.test(df$gZ, df$G3guilt_feelings)$p.value,2)
p2 <- ggplot(df, aes(x=gZ, y=G3guilt_feelings)) +
  geom_point(col="green4") + 
  geom_smooth(method="lm", col="black") + 
  theme_bw() +
  labs(x = "Global deviance score",
       y = paste0("G3guilt_feelings \n (",
                  round(sum(is.na(df$G3guilt_feelings))/
                        (sum(is.na(df$G3guilt_feelings))+
                           sum(!is.na(df$G3guilt_feelings)))*100,2),
                  "% NA values)"),
       title = paste0("Timepoint 2, patients r=",r,", p=",p))

# TIMEPOINT 3
df <- subset(df_tps, timepoint==3)
r <- round(as.numeric(cor.test(df$gZ, df$G3guilt_feelings)$estimate),2)
p <- round(cor.test(df$gZ, df$G3guilt_feelings)$p.value,2)
p3 <- ggplot(df, aes(x=gZ, y=G3guilt_feelings)) +
  geom_point(col="green4") + 
  geom_smooth(method="lm", col="black") + 
  theme_bw() +
  labs(x = "Global deviance score",
       y = paste0("G3guilt_feelings \n (",
                  round(sum(is.na(df$G3guilt_feelings))/
                        (sum(is.na(df$G3guilt_feelings))+
                           sum(!is.na(df$G3guilt_feelings)))*100,2),
                  "% NA values)"),
       title = paste0("Timepoint 3, patients r=",r,", p=",p))

ggarrange(p1, p2, p3, ncol = 1, nrow = 3)
rm(df, p1, p2, p3, p, r)
```

\newpage
## Correlating the global Z-score with clinical variables (by timepoint)
## G4tension

```{r echo=FALSE, message=FALSE, warning=FALSE, comment=NA, fig.width  = 10, fig.height = 10}
# Global deviance - G4tension
# TIMEPOINT 1
df <- subset(df_tps, timepoint==1)
r <- round(as.numeric(cor.test(df$gZ, df$G4tension)$estimate),2)
p <- round(cor.test(df$gZ, df$G4tension)$p.value,2)
p1 <- ggplot(df, aes(x=gZ, y=G4tension)) +
  geom_point(col="green4") + 
  geom_smooth(method="lm", col="black") + 
  theme_bw() +
  labs(x = "Global deviance score",
       y = paste0("G4tension \n (",
                  round(sum(is.na(df$G4tension))/
                        (sum(is.na(df$G4tension))+
                           sum(!is.na(df$G4tension)))*100,2),
                  "% NA values)"),
       title = paste0("Timepoint 1, patients r=",r,", p=",p))

# TIMEPOINT 2
df <- subset(df_tps, timepoint==2)
r <- round(as.numeric(cor.test(df$gZ, df$G4tension)$estimate),2)
p <- round(cor.test(df$gZ, df$G4tension)$p.value,2)
p2 <- ggplot(df, aes(x=gZ, y=G4tension)) +
  geom_point(col="green4") + 
  geom_smooth(method="lm", col="black") + 
  theme_bw() +
  labs(x = "Global deviance score",
       y = paste0("G4tension \n (",
                  round(sum(is.na(df$G4tension))/
                        (sum(is.na(df$G4tension))+
                           sum(!is.na(df$G4tension)))*100,2),
                  "% NA values)"),
       title = paste0("Timepoint 2, patients r=",r,", p=",p))

# TIMEPOINT 3
df <- subset(df_tps, timepoint==3)
r <- round(as.numeric(cor.test(df$gZ, df$G4tension)$estimate),2)
p <- round(cor.test(df$gZ, df$G4tension)$p.value,2)
p3 <- ggplot(df, aes(x=gZ, y=G4tension)) +
  geom_point(col="green4") + 
  geom_smooth(method="lm", col="black") + 
  theme_bw() +
  labs(x = "Global deviance score",
       y = paste0("G4tension \n (",
                  round(sum(is.na(df$G4tension))/
                        (sum(is.na(df$G4tension))+
                           sum(!is.na(df$G4tension)))*100,2),
                  "% NA values)"),
       title = paste0("Timepoint 3, patients r=",r,", p=",p))

ggarrange(p1, p2, p3, ncol = 1, nrow = 3)
rm(df, p1, p2, p3, p, r)
```

\newpage
## Correlating the global Z-score with clinical variables (by timepoint)
## G5mannerism_and_posturing

```{r echo=FALSE, message=FALSE, warning=FALSE, comment=NA, fig.width  = 10, fig.height = 10}
# Global deviance - G5mannerism_and_posturing
# TIMEPOINT 1
df <- subset(df_tps, timepoint==1)
r <- round(as.numeric(cor.test(df$gZ, df$G5mannerism_and_posturing)$estimate),2)
p <- round(cor.test(df$gZ, df$G5mannerism_and_posturing)$p.value,2)
p1 <- ggplot(df, aes(x=gZ, y=G5mannerism_and_posturing)) +
  geom_point(col="green4") + 
  geom_smooth(method="lm", col="black") + 
  theme_bw() +
  labs(x = "Global deviance score",
       y = paste0("G5mannerism_and_posturing \n (",
                  round(sum(is.na(df$G5mannerism_and_posturing))/
                        (sum(is.na(df$G5mannerism_and_posturing))+
                           sum(!is.na(df$G5mannerism_and_posturing)))*100,2),
                  "% NA values)"),
       title = paste0("Timepoint 1, patients r=",r,", p=",p))

# TIMEPOINT 2
df <- subset(df_tps, timepoint==2)
r <- round(as.numeric(cor.test(df$gZ, df$G5mannerism_and_posturing)$estimate),2)
p <- round(cor.test(df$gZ, df$G5mannerism_and_posturing)$p.value,2)
p2 <- ggplot(df, aes(x=gZ, y=G5mannerism_and_posturing)) +
  geom_point(col="green4") + 
  geom_smooth(method="lm", col="black") + 
  theme_bw() +
  labs(x = "Global deviance score",
       y = paste0("G5mannerism_and_posturing \n (",
                  round(sum(is.na(df$G5mannerism_and_posturing))/
                        (sum(is.na(df$G5mannerism_and_posturing))+
                           sum(!is.na(df$G5mannerism_and_posturing)))*100,2),
                  "% NA values)"),
       title = paste0("Timepoint 2, patients r=",r,", p=",p))

# TIMEPOINT 3
df <- subset(df_tps, timepoint==3)
r <- round(as.numeric(cor.test(df$gZ, df$G5mannerism_and_posturing)$estimate),2)
p <- round(cor.test(df$gZ, df$G5mannerism_and_posturing)$p.value,2)
p3 <- ggplot(df, aes(x=gZ, y=G5mannerism_and_posturing)) +
  geom_point(col="green4") + 
  geom_smooth(method="lm", col="black") + 
  theme_bw() +
  labs(x = "Global deviance score",
       y = paste0("G5mannerism_and_posturing \n (",
                  round(sum(is.na(df$G5mannerism_and_posturing))/
                        (sum(is.na(df$G5mannerism_and_posturing))+
                           sum(!is.na(df$G5mannerism_and_posturing)))*100,2),
                  "% NA values)"),
       title = paste0("Timepoint 3, patients r=",r,", p=",p))

ggarrange(p1, p2, p3, ncol = 1, nrow = 3)
rm(df, p1, p2, p3, p, r)
```

\newpage
## Correlating the global Z-score with clinical variables (by timepoint)
## G6depression

```{r echo=FALSE, message=FALSE, warning=FALSE, comment=NA, fig.width  = 10, fig.height = 10}
# Global deviance - G6depression
# TIMEPOINT 1
df <- subset(df_tps, timepoint==1)
r <- round(as.numeric(cor.test(df$gZ, df$G6depression)$estimate),2)
p <- round(cor.test(df$gZ, df$G6depression)$p.value,2)
p1 <- ggplot(df, aes(x=gZ, y=G6depression)) +
  geom_point(col="green4") + 
  geom_smooth(method="lm", col="black") + 
  theme_bw() +
  labs(x = "Global deviance score",
       y = paste0("G6depression \n (",
                  round(sum(is.na(df$G6depression))/
                        (sum(is.na(df$G6depression))+
                           sum(!is.na(df$G6depression)))*100,2),
                  "% NA values)"),
       title = paste0("Timepoint 1, patients r=",r,", p=",p))

# TIMEPOINT 2
df <- subset(df_tps, timepoint==2)
r <- round(as.numeric(cor.test(df$gZ, df$G6depression)$estimate),2)
p <- round(cor.test(df$gZ, df$G6depression)$p.value,2)
p2 <- ggplot(df, aes(x=gZ, y=G6depression)) +
  geom_point(col="green4") + 
  geom_smooth(method="lm", col="black") + 
  theme_bw() +
  labs(x = "Global deviance score",
       y = paste0("G6depression \n (",
                  round(sum(is.na(df$G6depression))/
                        (sum(is.na(df$G6depression))+
                           sum(!is.na(df$G6depression)))*100,2),
                  "% NA values)"),
       title = paste0("Timepoint 2, patients r=",r,", p=",p))

# TIMEPOINT 3
df <- subset(df_tps, timepoint==3)
r <- round(as.numeric(cor.test(df$gZ, df$G6depression)$estimate),2)
p <- round(cor.test(df$gZ, df$G6depression)$p.value,2)
p3 <- ggplot(df, aes(x=gZ, y=G6depression)) +
  geom_point(col="green4") + 
  geom_smooth(method="lm", col="black") + 
  theme_bw() +
  labs(x = "Global deviance score",
       y = paste0("G6depression \n (",
                  round(sum(is.na(df$G6depression))/
                        (sum(is.na(df$G6depression))+
                           sum(!is.na(df$G6depression)))*100,2),
                  "% NA values)"),
       title = paste0("Timepoint 3, patients r=",r,", p=",p))

ggarrange(p1, p2, p3, ncol = 1, nrow = 3)
rm(df, p1, p2, p3, p, r)
```

\newpage
## Correlating the global Z-score with clinical variables (by timepoint)
## G7motor_retardation

```{r echo=FALSE, message=FALSE, warning=FALSE, comment=NA, fig.width  = 10, fig.height = 10}
# Global deviance - G7motor_retardation
# TIMEPOINT 1
df <- subset(df_tps, timepoint==1)
r <- round(as.numeric(cor.test(df$gZ, df$G7motor_retardation)$estimate),2)
p <- round(cor.test(df$gZ, df$G7motor_retardation)$p.value,2)
p1 <- ggplot(df, aes(x=gZ, y=G7motor_retardation)) +
  geom_point(col="green4") + 
  geom_smooth(method="lm", col="black") + 
  theme_bw() +
  labs(x = "Global deviance score",
       y = paste0("G7motor_retardation \n (",
                  round(sum(is.na(df$G7motor_retardation))/
                        (sum(is.na(df$G7motor_retardation))+
                           sum(!is.na(df$G7motor_retardation)))*100,2),
                  "% NA values)"),
       title = paste0("Timepoint 1, patients r=",r,", p=",p))

# TIMEPOINT 2
df <- subset(df_tps, timepoint==2)
r <- round(as.numeric(cor.test(df$gZ, df$G7motor_retardation)$estimate),2)
p <- round(cor.test(df$gZ, df$G7motor_retardation)$p.value,2)
p2 <- ggplot(df, aes(x=gZ, y=G7motor_retardation)) +
  geom_point(col="green4") + 
  geom_smooth(method="lm", col="black") + 
  theme_bw() +
  labs(x = "Global deviance score",
       y = paste0("G7motor_retardation \n (",
                  round(sum(is.na(df$G7motor_retardation))/
                        (sum(is.na(df$G7motor_retardation))+
                           sum(!is.na(df$G7motor_retardation)))*100,2),
                  "% NA values)"),
       title = paste0("Timepoint 2, patients r=",r,", p=",p))

# TIMEPOINT 3
df <- subset(df_tps, timepoint==3)
r <- round(as.numeric(cor.test(df$gZ, df$G7motor_retardation)$estimate),2)
p <- round(cor.test(df$gZ, df$G7motor_retardation)$p.value,2)
p3 <- ggplot(df, aes(x=gZ, y=G7motor_retardation)) +
  geom_point(col="green4") + 
  geom_smooth(method="lm", col="black") + 
  theme_bw() +
  labs(x = "Global deviance score",
       y = paste0("G7motor_retardation \n (",
                  round(sum(is.na(df$G7motor_retardation))/
                        (sum(is.na(df$G7motor_retardation))+
                           sum(!is.na(df$G7motor_retardation)))*100,2),
                  "% NA values)"),
       title = paste0("Timepoint 3, patients r=",r,", p=",p))

ggarrange(p1, p2, p3, ncol = 1, nrow = 3)
rm(df, p1, p2, p3, p, r)
```

\newpage
## Correlating the global Z-score with clinical variables (by timepoint)
## G8uncooperativeness

```{r echo=FALSE, message=FALSE, warning=FALSE, comment=NA, fig.width  = 10, fig.height = 10}
# Global deviance - G8uncooperativeness
# TIMEPOINT 1
df <- subset(df_tps, timepoint==1)
r <- round(as.numeric(cor.test(df$gZ, df$G8uncooperativeness)$estimate),2)
p <- round(cor.test(df$gZ, df$G8uncooperativeness)$p.value,2)
p1 <- ggplot(df, aes(x=gZ, y=G8uncooperativeness)) +
  geom_point(col="green4") + 
  geom_smooth(method="lm", col="black") + 
  theme_bw() +
  labs(x = "Global deviance score",
       y = paste0("G8uncooperativeness \n (",
                  round(sum(is.na(df$G8uncooperativeness))/
                        (sum(is.na(df$G8uncooperativeness))+
                           sum(!is.na(df$G8uncooperativeness)))*100,2),
                  "% NA values)"),
       title = paste0("Timepoint 1, patients r=",r,", p=",p))

# TIMEPOINT 2
df <- subset(df_tps, timepoint==2)
r <- round(as.numeric(cor.test(df$gZ, df$G8uncooperativeness)$estimate),2)
p <- round(cor.test(df$gZ, df$G8uncooperativeness)$p.value,2)
p2 <- ggplot(df, aes(x=gZ, y=G8uncooperativeness)) +
  geom_point(col="green4") + 
  geom_smooth(method="lm", col="black") + 
  theme_bw() +
  labs(x = "Global deviance score",
       y = paste0("G8uncooperativeness \n (",
                  round(sum(is.na(df$G8uncooperativeness))/
                        (sum(is.na(df$G8uncooperativeness))+
                           sum(!is.na(df$G8uncooperativeness)))*100,2),
                  "% NA values)"),
       title = paste0("Timepoint 2, patients r=",r,", p=",p))

# TIMEPOINT 3
df <- subset(df_tps, timepoint==3)
r <- round(as.numeric(cor.test(df$gZ, df$G8uncooperativeness)$estimate),2)
p <- round(cor.test(df$gZ, df$G8uncooperativeness)$p.value,2)
p3 <- ggplot(df, aes(x=gZ, y=G8uncooperativeness)) +
  geom_point(col="green4") + 
  geom_smooth(method="lm", col="black") + 
  theme_bw() +
  labs(x = "Global deviance score",
       y = paste0("G8uncooperativeness \n (",
                  round(sum(is.na(df$G8uncooperativeness))/
                        (sum(is.na(df$G8uncooperativeness))+
                           sum(!is.na(df$G8uncooperativeness)))*100,2),
                  "% NA values)"),
       title = paste0("Timepoint 3, patients r=",r,", p=",p))

ggarrange(p1, p2, p3, ncol = 1, nrow = 3)
rm(df, p1, p2, p3, p, r)
```

\newpage
## Correlating the global Z-score with clinical variables (by timepoint)
## G9unusualthought_content

```{r echo=FALSE, message=FALSE, warning=FALSE, comment=NA, fig.width  = 10, fig.height = 10}
# Global deviance - G9unusualthought_content
# TIMEPOINT 1
df <- subset(df_tps, timepoint==1)
r <- round(as.numeric(cor.test(df$gZ, df$G9unusualthought_content)$estimate),2)
p <- round(cor.test(df$gZ, df$G9unusualthought_content)$p.value,2)
p1 <- ggplot(df, aes(x=gZ, y=G9unusualthought_content)) +
  geom_point(col="green4") + 
  geom_smooth(method="lm", col="black") + 
  theme_bw() +
  labs(x = "Global deviance score",
       y = paste0("G9unusualthought_content \n (",
                  round(sum(is.na(df$G9unusualthought_content))/
                        (sum(is.na(df$G9unusualthought_content))+
                           sum(!is.na(df$G9unusualthought_content)))*100,2),
                  "% NA values)"),
       title = paste0("Timepoint 1, patients r=",r,", p=",p))

# TIMEPOINT 2
df <- subset(df_tps, timepoint==2)
r <- round(as.numeric(cor.test(df$gZ, df$G9unusualthought_content)$estimate),2)
p <- round(cor.test(df$gZ, df$G9unusualthought_content)$p.value,2)
p2 <- ggplot(df, aes(x=gZ, y=G9unusualthought_content)) +
  geom_point(col="green4") + 
  geom_smooth(method="lm", col="black") + 
  theme_bw() +
  labs(x = "Global deviance score",
       y = paste0("G9unusualthought_content \n (",
                  round(sum(is.na(df$G9unusualthought_content))/
                        (sum(is.na(df$G9unusualthought_content))+
                           sum(!is.na(df$G9unusualthought_content)))*100,2),
                  "% NA values)"),
       title = paste0("Timepoint 2, patients r=",r,", p=",p))

# TIMEPOINT 3
df <- subset(df_tps, timepoint==3)
r <- round(as.numeric(cor.test(df$gZ, df$G9unusualthought_content)$estimate),2)
p <- round(cor.test(df$gZ, df$G9unusualthought_content)$p.value,2)
p3 <- ggplot(df, aes(x=gZ, y=G9unusualthought_content)) +
  geom_point(col="green4") + 
  geom_smooth(method="lm", col="black") + 
  theme_bw() +
  labs(x = "Global deviance score",
       y = paste0("G9unusualthought_content \n (",
                  round(sum(is.na(df$G9unusualthought_content))/
                        (sum(is.na(df$G9unusualthought_content))+
                           sum(!is.na(df$G9unusualthought_content)))*100,2),
                  "% NA values)"),
       title = paste0("Timepoint 3, patients r=",r,", p=",p))

ggarrange(p1, p2, p3, ncol = 1, nrow = 3)
rm(df, p1, p2, p3, p, r)
```

\newpage
## Correlating the global Z-score with clinical variables (by timepoint)
## G10disorientation

```{r echo=FALSE, message=FALSE, warning=FALSE, comment=NA, fig.width  = 10, fig.height = 10}
# Global deviance - G10disorientation
# TIMEPOINT 1
df <- subset(df_tps, timepoint==1)
r <- round(as.numeric(cor.test(df$gZ, df$G10disorientation)$estimate),2)
p <- round(cor.test(df$gZ, df$G10disorientation)$p.value,2)
p1 <- ggplot(df, aes(x=gZ, y=G10disorientation)) +
  geom_point(col="green4") + 
  geom_smooth(method="lm", col="black") + 
  theme_bw() +
  labs(x = "Global deviance score",
       y = paste0("G10disorientation \n (",
                  round(sum(is.na(df$G10disorientation))/
                        (sum(is.na(df$G10disorientation))+
                           sum(!is.na(df$G10disorientation)))*100,2),
                  "% NA values)"),
       title = paste0("Timepoint 1, patients r=",r,", p=",p))

# TIMEPOINT 2
df <- subset(df_tps, timepoint==2)
r <- round(as.numeric(cor.test(df$gZ, df$G10disorientation)$estimate),2)
p <- round(cor.test(df$gZ, df$G10disorientation)$p.value,2)
p2 <- ggplot(df, aes(x=gZ, y=G10disorientation)) +
  geom_point(col="green4") + 
  geom_smooth(method="lm", col="black") + 
  theme_bw() +
  labs(x = "Global deviance score",
       y = paste0("G10disorientation \n (",
                  round(sum(is.na(df$G10disorientation))/
                        (sum(is.na(df$G10disorientation))+
                           sum(!is.na(df$G10disorientation)))*100,2),
                  "% NA values)"),
       title = paste0("Timepoint 2, patients r=",r,", p=",p))

# TIMEPOINT 3
df <- subset(df_tps, timepoint==3)
r <- round(as.numeric(cor.test(df$gZ, df$G10disorientation)$estimate),2)
p <- round(cor.test(df$gZ, df$G10disorientation)$p.value,2)
p3 <- ggplot(df, aes(x=gZ, y=G10disorientation)) +
  geom_point(col="green4") + 
  geom_smooth(method="lm", col="black") + 
  theme_bw() +
  labs(x = "Global deviance score",
       y = paste0("G10disorientation \n (",
                  round(sum(is.na(df$G10disorientation))/
                        (sum(is.na(df$G10disorientation))+
                           sum(!is.na(df$G10disorientation)))*100,2),
                  "% NA values)"),
       title = paste0("Timepoint 3, patients r=",r,", p=",p))

ggarrange(p1, p2, p3, ncol = 1, nrow = 3)
rm(df, p1, p2, p3, p, r)
```

\newpage
## Correlating the global Z-score with clinical variables (by timepoint)
## G11poor_attention

```{r echo=FALSE, message=FALSE, warning=FALSE, comment=NA, fig.width  = 10, fig.height = 10}
# Global deviance - G11poor_attention
# TIMEPOINT 1
df <- subset(df_tps, timepoint==1)
r <- round(as.numeric(cor.test(df$gZ, df$G11poor_attention)$estimate),2)
p <- round(cor.test(df$gZ, df$G11poor_attention)$p.value,2)
p1 <- ggplot(df, aes(x=gZ, y=G11poor_attention)) +
  geom_point(col="green4") + 
  geom_smooth(method="lm", col="black") + 
  theme_bw() +
  labs(x = "Global deviance score",
       y = paste0("G11poor_attention \n (",
                  round(sum(is.na(df$G11poor_attention))/
                        (sum(is.na(df$G11poor_attention))+
                           sum(!is.na(df$G11poor_attention)))*100,2),
                  "% NA values)"),
       title = paste0("Timepoint 1, patients r=",r,", p=",p))

# TIMEPOINT 2
df <- subset(df_tps, timepoint==2)
r <- round(as.numeric(cor.test(df$gZ, df$G11poor_attention)$estimate),2)
p <- round(cor.test(df$gZ, df$G11poor_attention)$p.value,2)
p2 <- ggplot(df, aes(x=gZ, y=G11poor_attention)) +
  geom_point(col="green4") + 
  geom_smooth(method="lm", col="black") + 
  theme_bw() +
  labs(x = "Global deviance score",
       y = paste0("G11poor_attention \n (",
                  round(sum(is.na(df$G11poor_attention))/
                        (sum(is.na(df$G11poor_attention))+
                           sum(!is.na(df$G11poor_attention)))*100,2),
                  "% NA values)"),
       title = paste0("Timepoint 2, patients r=",r,", p=",p))

# TIMEPOINT 3
df <- subset(df_tps, timepoint==3)
r <- round(as.numeric(cor.test(df$gZ, df$G11poor_attention)$estimate),2)
p <- round(cor.test(df$gZ, df$G11poor_attention)$p.value,2)
p3 <- ggplot(df, aes(x=gZ, y=G11poor_attention)) +
  geom_point(col="green4") + 
  geom_smooth(method="lm", col="black") + 
  theme_bw() +
  labs(x = "Global deviance score",
       y = paste0("G11poor_attention \n (",
                  round(sum(is.na(df$G11poor_attention))/
                        (sum(is.na(df$G11poor_attention))+
                           sum(!is.na(df$G11poor_attention)))*100,2),
                  "% NA values)"),
       title = paste0("Timepoint 3, patients r=",r,", p=",p))

ggarrange(p1, p2, p3, ncol = 1, nrow = 3)
rm(df, p1, p2, p3, p, r)
```

\newpage
## Correlating the global Z-score with clinical variables (by timepoint)
## G12lack_of_judgement_and_insight

```{r echo=FALSE, message=FALSE, warning=FALSE, comment=NA, fig.width  = 10, fig.height = 10}
# Global deviance - G12lack_of_judgement_and_insight
# TIMEPOINT 1
df <- subset(df_tps, timepoint==1)
r <- round(as.numeric(cor.test(df$gZ, df$G12lack_of_judgement_and_insight)$estimate),2)
p <- round(cor.test(df$gZ, df$G12lack_of_judgement_and_insight)$p.value,2)
p1 <- ggplot(df, aes(x=gZ, y=G12lack_of_judgement_and_insight)) +
  geom_point(col="green4") + 
  geom_smooth(method="lm", col="black") + 
  theme_bw() +
  labs(x = "Global deviance score",
       y = paste0("G12lack_of_judgement_and_insight \n (",
                  round(sum(is.na(df$G12lack_of_judgement_and_insight))/
                        (sum(is.na(df$G12lack_of_judgement_and_insight))+
                           sum(!is.na(df$G12lack_of_judgement_and_insight)))*100,2),
                  "% NA values)"),
       title = paste0("Timepoint 1, patients r=",r,", p=",p))

# TIMEPOINT 2
df <- subset(df_tps, timepoint==2)
r <- round(as.numeric(cor.test(df$gZ, df$G12lack_of_judgement_and_insight)$estimate),2)
p <- round(cor.test(df$gZ, df$G12lack_of_judgement_and_insight)$p.value,2)
p2 <- ggplot(df, aes(x=gZ, y=G12lack_of_judgement_and_insight)) +
  geom_point(col="green4") + 
  geom_smooth(method="lm", col="black") + 
  theme_bw() +
  labs(x = "Global deviance score",
       y = paste0("G12lack_of_judgement_and_insight \n (",
                  round(sum(is.na(df$G12lack_of_judgement_and_insight))/
                        (sum(is.na(df$G12lack_of_judgement_and_insight))+
                           sum(!is.na(df$G12lack_of_judgement_and_insight)))*100,2),
                  "% NA values)"),
       title = paste0("Timepoint 2, patients r=",r,", p=",p))

# TIMEPOINT 3
df <- subset(df_tps, timepoint==3)
r <- round(as.numeric(cor.test(df$gZ, df$G12lack_of_judgement_and_insight)$estimate),2)
p <- round(cor.test(df$gZ, df$G12lack_of_judgement_and_insight)$p.value,2)
p3 <- ggplot(df, aes(x=gZ, y=G12lack_of_judgement_and_insight)) +
  geom_point(col="green4") + 
  geom_smooth(method="lm", col="black") + 
  theme_bw() +
  labs(x = "Global deviance score",
       y = paste0("G12lack_of_judgement_and_insight \n (",
                  round(sum(is.na(df$G12lack_of_judgement_and_insight))/
                        (sum(is.na(df$G12lack_of_judgement_and_insight))+
                           sum(!is.na(df$G12lack_of_judgement_and_insight)))*100,2),
                  "% NA values)"),
       title = paste0("Timepoint 3, patients r=",r,", p=",p))

ggarrange(p1, p2, p3, ncol = 1, nrow = 3)
rm(df, p1, p2, p3, p, r)
```

\newpage
## Correlating the global Z-score with clinical variables (by timepoint)
## G13disturbance_of_volition

```{r echo=FALSE, message=FALSE, warning=FALSE, comment=NA, fig.width  = 10, fig.height = 10}
# Global deviance - G13disturbance_of_volition
# TIMEPOINT 1
df <- subset(df_tps, timepoint==1)
r <- round(as.numeric(cor.test(df$gZ, df$G13disturbance_of_volition)$estimate),2)
p <- round(cor.test(df$gZ, df$G13disturbance_of_volition)$p.value,2)
p1 <- ggplot(df, aes(x=gZ, y=G13disturbance_of_volition)) +
  geom_point(col="green4") + 
  geom_smooth(method="lm", col="black") + 
  theme_bw() +
  labs(x = "Global deviance score",
       y = paste0("G13disturbance_of_volition \n (",
                  round(sum(is.na(df$G13disturbance_of_volition))/
                        (sum(is.na(df$G13disturbance_of_volition))+
                           sum(!is.na(df$G13disturbance_of_volition)))*100,2),
                  "% NA values)"),
       title = paste0("Timepoint 1, patients r=",r,", p=",p))

# TIMEPOINT 2
df <- subset(df_tps, timepoint==2)
r <- round(as.numeric(cor.test(df$gZ, df$G13disturbance_of_volition)$estimate),2)
p <- round(cor.test(df$gZ, df$G13disturbance_of_volition)$p.value,2)
p2 <- ggplot(df, aes(x=gZ, y=G13disturbance_of_volition)) +
  geom_point(col="green4") + 
  geom_smooth(method="lm", col="black") + 
  theme_bw() +
  labs(x = "Global deviance score",
       y = paste0("G13disturbance_of_volition \n (",
                  round(sum(is.na(df$G13disturbance_of_volition))/
                        (sum(is.na(df$G13disturbance_of_volition))+
                           sum(!is.na(df$G13disturbance_of_volition)))*100,2),
                  "% NA values)"),
       title = paste0("Timepoint 2, patients r=",r,", p=",p))

# TIMEPOINT 3
df <- subset(df_tps, timepoint==3)
r <- round(as.numeric(cor.test(df$gZ, df$G13disturbance_of_volition)$estimate),2)
p <- round(cor.test(df$gZ, df$G13disturbance_of_volition)$p.value,2)
p3 <- ggplot(df, aes(x=gZ, y=G13disturbance_of_volition)) +
  geom_point(col="green4") + 
  geom_smooth(method="lm", col="black") + 
  theme_bw() +
  labs(x = "Global deviance score",
       y = paste0("G13disturbance_of_volition \n (",
                  round(sum(is.na(df$G13disturbance_of_volition))/
                        (sum(is.na(df$G13disturbance_of_volition))+
                           sum(!is.na(df$G13disturbance_of_volition)))*100,2),
                  "% NA values)"),
       title = paste0("Timepoint 3, patients r=",r,", p=",p))

ggarrange(p1, p2, p3, ncol = 1, nrow = 3)
rm(df, p1, p2, p3, p, r)
```

\newpage
## Correlating the global Z-score with clinical variables (by timepoint)
## G14poor_impulse_control

```{r echo=FALSE, message=FALSE, warning=FALSE, comment=NA, fig.width  = 10, fig.height = 10}
# Global deviance - G14poor_impulse_control
# TIMEPOINT 1
df <- subset(df_tps, timepoint==1)
r <- round(as.numeric(cor.test(df$gZ, df$G14poor_impulse_control)$estimate),2)
p <- round(cor.test(df$gZ, df$G14poor_impulse_control)$p.value,2)
p1 <- ggplot(df, aes(x=gZ, y=G14poor_impulse_control)) +
  geom_point(col="green4") + 
  geom_smooth(method="lm", col="black") + 
  theme_bw() +
  labs(x = "Global deviance score",
       y = paste0("G14poor_impulse_control \n (",
                  round(sum(is.na(df$G14poor_impulse_control))/
                        (sum(is.na(df$G14poor_impulse_control))+
                           sum(!is.na(df$G14poor_impulse_control)))*100,2),
                  "% NA values)"),
       title = paste0("Timepoint 1, patients r=",r,", p=",p))

# TIMEPOINT 2
df <- subset(df_tps, timepoint==2)
r <- round(as.numeric(cor.test(df$gZ, df$G14poor_impulse_control)$estimate),2)
p <- round(cor.test(df$gZ, df$G14poor_impulse_control)$p.value,2)
p2 <- ggplot(df, aes(x=gZ, y=G14poor_impulse_control)) +
  geom_point(col="green4") + 
  geom_smooth(method="lm", col="black") + 
  theme_bw() +
  labs(x = "Global deviance score",
       y = paste0("G14poor_impulse_control \n (",
                  round(sum(is.na(df$G14poor_impulse_control))/
                        (sum(is.na(df$G14poor_impulse_control))+
                           sum(!is.na(df$G14poor_impulse_control)))*100,2),
                  "% NA values)"),
       title = paste0("Timepoint 2, patients r=",r,", p=",p))

# TIMEPOINT 3
df <- subset(df_tps, timepoint==3)
r <- round(as.numeric(cor.test(df$gZ, df$G14poor_impulse_control)$estimate),2)
p <- round(cor.test(df$gZ, df$G14poor_impulse_control)$p.value,2)
p3 <- ggplot(df, aes(x=gZ, y=G14poor_impulse_control)) +
  geom_point(col="green4") + 
  geom_smooth(method="lm", col="black") + 
  theme_bw() +
  labs(x = "Global deviance score",
       y = paste0("G14poor_impulse_control \n (",
                  round(sum(is.na(df$G14poor_impulse_control))/
                        (sum(is.na(df$G14poor_impulse_control))+
                           sum(!is.na(df$G14poor_impulse_control)))*100,2),
                  "% NA values)"),
       title = paste0("Timepoint 3, patients r=",r,", p=",p))

ggarrange(p1, p2, p3, ncol = 1, nrow = 3)
rm(df, p1, p2, p3, p, r)
```

