---
title: "Harmonization"
author: "Noemi González Lois"
date: "`r Sys.Date()`"
output:
  pdf_document: default
  html_document: default
---

```{r, warning=F, message = F, echo = FALSE}
#install.packages("easypackages")
library("easypackages")

list.of.packages <- c("tidyverse", "MatchIt", 
                      "nlme", "JMbayes", "plyr",
                      "BiocManager", "dplyr",
                      "devtools", "longCombat", 
                      "tinytex", "knitr", "Rmisc", 
                      "effectsize", "tidyr",
                      "Hmisc", "kableExtra")

new.packages <- list.of.packages[!(list.of.packages %in%
                                     installed.packages()[,"Package"])]
  if(length(new.packages)>0) { install.packages(new.packages)}

libraries(list.of.packages)
rm(list.of.packages, new.packages)
```

```{r setup I, echo=F}
knitr::opts_chunk$set(
  include = TRUE,  
  echo=TRUE, 
  eval=TRUE, 
  warning=TRUE, 
  message = TRUE,
  cache = TRUE,
  fig.width = 12,
  fig.height = 8
  )
```

```{r, warning=F, message = F, echo = FALSE}
setwd("/data_J/Scripts")
source("1_DataPreparation.R")
```


```{r include=FALSE, results=}
df_68 <- getData("68")
df_308 <- getData("308")
# #measure <- "CT"
measure <- "Vol"
```

# Experimento: harmonización de BV sólo sujetos masculinos:

```{r include=FALSE}
# ### 68 REG PARC, NO MATCH IT
df_68_males <- subset(df_68, scode==1)
df_308_males <- subset(df_308, scode==1)

df_68_Combat <- DataPreprocessing_males(df = df_68_males,
                parc = "68",
                measure = measure,
                harmonization = T,
                match = F)
### 308 REG PARC, NO MATCH IT
df_308_Combat <- DataPreprocessing_males(df = df_308_males,
                 parc = "308",
                 measure = measure,
                 harmonization = T,
                 match = F)

### 68 REG PARC, MATCH IT
df_68_Combat_Match <- DataPreprocessing_males(df = df_68_males,
                      parc = "68",
                      measure = measure,
                      harmonization = T,
                      match = T)

### 308 REG PARC, MATCH IT
df_308_Combat_Match <- DataPreprocessing_males(df = df_308_males,
                       parc = "308",
                       measure = measure,
                       harmonization = T,
                       match = T)
```


```{r include=FALSE, results=}
### 68 REG PARC, NO MATCH IT
df_68_Combat <- DataPreprocessing(df = df_68,
                parc = "68",
                measure = measure,
                harmonization = T,
                match = F)

### 308 REG PARC, NO MATCH IT
df_308_Combat <- DataPreprocessing(df = df_308,
                 parc = "308",
                 measure = measure,
                 harmonization = T,
                 match = F)

### 68 REG PARC, MATCH IT
df_68_Combat_Match <- DataPreprocessing(df = df_68,
                      parc = "68",
                      measure = measure,
                      harmonization = T,
                      match = T)

### 308 REG PARC, MATCH IT
df_308_Combat_Match <- DataPreprocessing(df = df_308,
                       parc = "308",
                       measure = measure,
                       harmonization = T,
                       match = T)
```


\newpage


```{r include=FALSE}
signif_df <- function(x, digits) {
    numeric_columns <- sapply(x, mode) == 'numeric'
    x[numeric_columns] <-  round(x[numeric_columns], digits)
    return(x)}
```

# Additive batch effects BEFORE longitudinal ComBat (CT)
## 68 regions

```{r message=FALSE, warning=FALSE, include=FALSE}
df <- df_68
measure <- measure
formula = 'age + scode + dcode*timepoint'
ranef = '(1|subID)'
features  <- colnames(df%>%dplyr::select(ends_with(measure)))

a_68 <- addTest("ID", "acode", features, formula, ranef, df, verbose = F)
a_68[2] <- as.numeric(unlist(a_68[colnames(a_68)[2]]))
a_68[3] <- as.numeric(unlist(a_68[colnames(a_68)[3]]))
a_68[4] <- as.numeric(unlist(a_68[colnames(a_68)[4]]))
```

\tiny

```{r echo=FALSE}
a_68 <- signif_df(a_68, 3)
kable(a_68)
```

\normalsize

```{r echo=FALSE}
a_68_sig <- a_68 %>%
  dplyr::mutate(significant = ifelse(`KR p-value` < 0.05, 1, 0)) %>%
  dplyr::summarise(sig= sum(significant==1),
                   nonsig = sum(significant==0))
cat("\n Significant:",a_68_sig$sig, "\n Non-significant:", a_68_sig$nonsig)
```

\newpage


# Additive batch effects BEFORE longitudinal ComBat (CT)
## 308 regions

```{r message=FALSE, warning=FALSE, include=FALSE}
df <- df_308
features  <- colnames(df%>%dplyr::select(ends_with(measure)))
a_308 <- addTest("ID", "acode", features, formula, ranef, df, verbose = F)
a_308[2] <- as.numeric(unlist(a_308[colnames(a_308)[2]]))
a_308[3] <- as.numeric(unlist(a_308[colnames(a_308)[3]]))
a_308[4] <- as.numeric(unlist(a_308[colnames(a_308)[4]]))
```

\tiny

```{r echo=FALSE}
a_308 <- signif_df(a_308, 3)
kable(a_308)
```

\normalsize

```{r echo=FALSE}
a_308_sig <- a_308 %>%
  dplyr::mutate(significant = ifelse(`KR p-value` < 0.05, 1, 0)) %>%
  dplyr::summarise(sig= sum(significant==1),
                   nonsig = sum(significant==0))
cat("\n Significant:",a_308_sig$sig, "\n Non-significant:", a_308_sig$nonsig)
```

\newpage

# Additive batch effects BEFORE longitudinal ComBat (boxplot) (CT)
## 68 regions

```{r echo=FALSE, message=FALSE, warning=FALSE}
df <- df_68
features  <- colnames(df%>%dplyr::select(ends_with(measure)))
feature <- which(features==a_68[1,"Feature"], arr.ind = FALSE, useNames = TRUE)

batchBoxplot("ID", "acode", feature, formula, ranef, df,
  adjustBatch = FALSE, orderby = "mean", plotMeans = TRUE,
  colors = "grey", xlabel = "batch", ylabel = "residuals",
  title = "", verbose = F)
```

# Additive batch effects BEFORE longitudinal ComBat (boxplot) (CT)
## 308 regions

```{r echo=FALSE, message=FALSE, warning=FALSE}
df <- df_308
features  <- colnames(df%>%dplyr::select(ends_with(measure)))
feature <- which(features==a_308[1,"Feature"], arr.ind = FALSE, useNames = TRUE)

batchBoxplot("ID", "acode", feature, formula, ranef, df,
  adjustBatch = FALSE, orderby = "mean", plotMeans = TRUE,
  colors = "grey", xlabel = "batch", ylabel = "residuals",
  title = "", verbose = F)
```

\newpage

# Multiplicative batch effects BEFORE longitudinal ComBat (CT)
## 68 regions

```{r message=FALSE, warning=FALSE, include=FALSE}
df <- df_68
features  <- colnames(df%>%dplyr::select(ends_with(measure)))
m_68 <- multTest("ID", "acode", features, formula, ranef, df, verbose = F)
m_68[2] <- as.numeric(unlist(m_68[colnames(m_68)[2]]))
m_68[4] <- as.numeric(unlist(m_68[colnames(m_68)[4]]))
m_68[3] <- NULL
colnames(m_68) <- c("Feature", "$\\chi ^2$", "p-value")
```

\tiny

```{r echo=FALSE}
m_68 <- signif_df(m_68, 3)
kable(m_68)
```

\normalsize

```{r echo=FALSE}
m_68_sig <- m_68 %>%
  dplyr::mutate(significant = ifelse(`p-value` < 0.05, 1, 0)) %>%
  dplyr::summarise(sig= sum(significant==1),
                   nonsig = sum(significant==0))
cat("\n Significant:",m_68_sig$sig, "\n Non-significant:", m_68_sig$nonsig)
```

\newpage


# Multiplicative batch effects BEFORE longitudinal ComBat (CT)
## 308 regions

```{r message=FALSE, warning=FALSE, include=FALSE}
df <- df_308
features  <- colnames(df%>%dplyr::select(ends_with(measure)))
m_308 <- multTest("ID", "acode", features, formula, ranef, df, verbose = F)
m_308[2] <- as.numeric(unlist(m_308[colnames(m_308)[2]]))
m_308[4] <- as.numeric(unlist(m_308[colnames(m_308)[4]]))
m_308[3] <- NULL
colnames(m_308) <- c("Feature", "$\\chi ^2$", "p-value")
```

\tiny

```{r echo=FALSE}
m_308 <- signif_df(m_308, 3)
kable(m_308)
```

\normalsize

```{r echo=FALSE}
m_308_sig <- m_308 %>%
  dplyr::mutate(significant = ifelse(`p-value` < 0.05, 1, 0)) %>%
  dplyr::summarise(sig= sum(significant==1),
                   nonsig = sum(significant==0))
cat("\n Significant:",m_308_sig$sig, "\n Non-significant:", m_308_sig$nonsig)
```
\newpage


# Multiplicative batch effects BEFORE longitudinal ComBat (boxplot) (CT)
## 68 regions

```{r echo=FALSE, message=FALSE, warning=FALSE}
df <- df_68
features  <- colnames(df%>%dplyr::select(ends_with(measure)))
feature <- which(features==m_68[1,"Feature"], arr.ind = FALSE, useNames = TRUE)

batchBoxplot("ID", "acode", feature, formula, ranef, df,
  adjustBatch = T, orderby = "var", plotMeans = TRUE,
  colors = "grey", xlabel = "batch", ylabel = "residuals",
  title = "", verbose = F)
```

# Multiplicative batch effects BEFORE longitudinal ComBat (boxplot) (CT)
## 308 regions

```{r echo=FALSE, message=FALSE, warning=FALSE}
df <- df_308
features  <- colnames(df%>%dplyr::select(ends_with(measure)))
feature <- which(features==m_308[1,"Feature"], arr.ind = FALSE, useNames = TRUE)

batchBoxplot("ID", "acode", feature, formula, ranef, df,
  adjustBatch = T, orderby = "var", plotMeans = TRUE,
  colors = "grey", xlabel = "batch", ylabel = "residuals",
  title = "", verbose = F)
```

\newpage


# Additive batch effects AFTER longitudinal ComBat (CT)
## 68 regions

```{r message=FALSE, warning=FALSE, include=FALSE}
df <- df_68_Combat
features  <- colnames(df%>%dplyr::select(ends_with(measure)))

a_68_after <- addTest("ID", "acode", features, formula, ranef, df, verbose = F)
a_68_after[2] <- as.numeric(unlist(a_68_after[colnames(a_68_after)[2]]))
a_68_after[3] <- as.numeric(unlist(a_68_after[colnames(a_68_after)[3]]))
a_68_after[4] <- as.numeric(unlist(a_68_after[colnames(a_68_after)[4]]))
```

\tiny

```{r echo=FALSE}
a_68_after <- signif_df(a_68_after, 3)
kable(a_68_after)
```

\normalsize

```{r echo=FALSE}
a_68_after_sig <- a_68_after %>%
  dplyr::mutate(significant = ifelse(`KR p-value` < 0.05, 1, 0)) %>%
  dplyr::summarise(sig= sum(significant==1),
                   nonsig = sum(significant==0))
cat("\n Significant:",a_68_after_sig$sig, "\n Non-significant:", a_68_after_sig$nonsig)
```

\newpage


# Additive batch effects AFTER longitudinal ComBat (CT)
## 308 regions

```{r message=FALSE, warning=FALSE, include=FALSE}
df <- df_308_Combat
features  <- colnames(df%>%dplyr::select(ends_with(measure)))
a_308_after <- addTest("ID", "acode", features, formula, ranef, df, verbose = F)
a_308_after[2] <- as.numeric(unlist(a_308_after[colnames(a_308_after)[2]]))
a_308_after[3] <- as.numeric(unlist(a_308_after[colnames(a_308_after)[3]]))
a_308_after[4] <- as.numeric(unlist(a_308_after[colnames(a_308_after)[4]]))
```

\tiny

```{r echo=FALSE}
a_308_after <- signif_df(a_308_after, 3)
kable(a_308_after)
```

\normalsize

```{r echo=FALSE}
a_308_after_sig <- a_308_after %>%
  dplyr::mutate(significant = ifelse(`KR p-value` < 0.05, 1, 0)) %>%
  dplyr::summarise(sig= sum(significant==1),
                   nonsig = sum(significant==0))
cat("\n Significant:",a_308_after_sig$sig, "\n Non-significant:", a_308_after_sig$nonsig)
```

\newpage

# Additive batch effects AFTER longitudinal ComBat (boxplot) (CT)
## 68 regions

```{r echo=FALSE, message=FALSE, warning=FALSE}
df <- df_68_Combat
features  <- colnames(df%>%dplyr::select(ends_with(measure)))
feature <- which(features==a_68[1,"Feature"], arr.ind = FALSE, useNames = TRUE)

batchBoxplot("ID", "acode", feature, formula, ranef, df,
  adjustBatch = FALSE, orderby = "mean", plotMeans = TRUE,
  colors = "grey", xlabel = "batch", ylabel = "residuals",
  title = "", verbose = F)
```

# Additive batch effects AFTER longitudinal ComBat (boxplot) (CT)
## 308 regions

```{r echo=FALSE, message=FALSE, warning=FALSE}
df <- df_308_Combat
features  <- colnames(df%>%dplyr::select(ends_with(measure)))
feature <- which(features==a_308[1,"Feature"], arr.ind = FALSE, useNames = TRUE)

batchBoxplot("ID", "acode", feature, formula, ranef, df,
  adjustBatch = FALSE, orderby = "mean", plotMeans = TRUE,
  colors = "grey", xlabel = "batch", ylabel = "residuals",
  title = "", verbose = F)
```

\newpage

# Multiplicative batch effects AFTER longitudinal ComBat (CT)
## 68 regions

```{r message=FALSE, warning=FALSE, include=FALSE}
df <- df_68_Combat
features  <- colnames(df%>%dplyr::select(ends_with(measure)))
m_68_after <- multTest("ID", "acode", features, formula, ranef, df, verbose = F)
m_68_after[2] <- as.numeric(unlist(m_68_after[colnames(m_68_after)[2]]))
m_68_after[4] <- as.numeric(unlist(m_68_after[colnames(m_68_after)[4]]))
m_68_after[3] <- NULL
colnames(m_68_after) <- c("Feature", "$\\chi ^2$", "p-value")
```

\tiny

```{r echo=FALSE}
m_68_after <- signif_df(m_68_after, 3)
kable(m_68_after)
```

\normalsize

```{r echo=FALSE}
m_68_after_sig <- m_68_after %>%
  dplyr::mutate(significant = ifelse(`p-value` < 0.05, 1, 0)) %>%
  dplyr::summarise(sig= sum(significant==1),
                   nonsig = sum(significant==0))
cat("\n Significant:",m_68_after_sig$sig, "\n Non-significant:", m_68_after_sig$nonsig)
```

\newpage


# Multiplicative batch effects AFTER longitudinal ComBat (CT)
## 308 regions

```{r message=FALSE, warning=FALSE, include=FALSE}
df <- df_308_Combat
features  <- colnames(df%>%dplyr::select(ends_with(measure)))
m_308_after <- multTest("ID", "acode", features, formula, ranef, df, verbose = F)
m_308_after[2] <- as.numeric(unlist(m_308_after[colnames(m_308_after)[2]]))
m_308_after[4] <- as.numeric(unlist(m_308_after[colnames(m_308_after)[4]]))
m_308_after[3] <- NULL
colnames(m_308_after) <- c("Feature", "$\\chi ^2$", "p-value")
```

\tiny

```{r echo=FALSE}
m_308_after <- signif_df(m_308_after, 3)
kable(m_308_after)
```

\normalsize

```{r echo=FALSE}
m_308_after_sig <- m_308_after %>%
  dplyr::mutate(significant = ifelse(`p-value` < 0.05, 1, 0)) %>%
  dplyr::summarise(sig= sum(significant==1),
                   nonsig = sum(significant==0))
cat("\n Significant:",m_308_after_sig$sig, "\n Non-significant:", m_308_after_sig$nonsig)
```
\newpage


# Multiplicative batch effects AFTER longitudinal ComBat (boxplot) (CT)
## 68 regions

```{r echo=FALSE, message=FALSE, warning=FALSE}
df <- df_68_Combat
features  <- colnames(df%>%dplyr::select(ends_with(measure)))
feature <- which(features==m_68[1,"Feature"], arr.ind = FALSE, useNames = TRUE)

batchBoxplot("ID", "acode", feature, formula, ranef, df,
  adjustBatch = T, orderby = "var", plotMeans = TRUE,
  colors = "grey", xlabel = "batch", ylabel = "residuals",
  title = "", verbose = F)
```

# Multiplicative batch effects AFTER longitudinal ComBat (boxplot) (CT)
## 308 regions

```{r echo=FALSE, message=FALSE, warning=FALSE}
df <- df_308_Combat
features  <- colnames(df%>%dplyr::select(ends_with(measure)))
feature <- which(features==m_308[1,"Feature"], arr.ind = FALSE, useNames = TRUE)

batchBoxplot("ID", "acode", feature, formula, ranef, df,
  adjustBatch = T, orderby = "var", plotMeans = TRUE,
  colors = "grey", xlabel = "batch", ylabel = "residuals",
  title = "", verbose = F)
```

\newpage


# VOLUME


\newpage

```{r include=FALSE, results=}
df_68 <- getData("68")
df_308 <- getData("308")
measure <- "Vol"
```

```{r include=FALSE, results=}
### 68 REG PARC, NO MATCH IT
df_68_Combat <- DataPreprocessing(df = df_68,
                parc = "68",
                measure = measure,
                harmonization = T,
                match = F)

### 308 REG PARC, NO MATCH IT
df_308_Combat <- DataPreprocessing(df = df_308,
                 parc = "308",
                 measure = measure,
                 harmonization = T,
                 match = F)

### 68 REG PARC, MATCH IT
df_68_Combat_Match <- DataPreprocessing(df = df_68,
                      parc = "68",
                      measure = measure,
                      harmonization = T,
                      match = T)

### 308 REG PARC, MATCH IT
df_308_Combat_Match <- DataPreprocessing(df = df_308,
                       parc = "308",
                       measure = measure,
                       harmonization = T,
                       match = T)
```


\newpage

# Additive batch effects BEFORE longitudinal ComBat (BV)
## 68 regions

```{r message=FALSE, warning=FALSE, include=FALSE}
df <- df_68
measure <- measure
formula = 'age + scode + dcode*timepoint'
ranef = '(1|subID)'
features  <- colnames(df%>%dplyr::select(ends_with(measure)))

a_68 <- addTest("ID", "acode", features, formula, ranef, df, verbose = F)
a_68[2] <- as.numeric(unlist(a_68[colnames(a_68)[2]]))
a_68[3] <- as.numeric(unlist(a_68[colnames(a_68)[3]]))
a_68[4] <- as.numeric(unlist(a_68[colnames(a_68)[4]]))
```

\tiny

```{r echo=FALSE}
a_68 <- signif_df(a_68, 3)
kable(a_68)
```

\normalsize

```{r echo=FALSE}
a_68_sig <- a_68 %>%
  dplyr::mutate(significant = ifelse(`KR p-value` < 0.05, 1, 0)) %>%
  dplyr::summarise(sig= sum(significant==1),
                   nonsig = sum(significant==0))
cat("\n Significant:",a_68_sig$sig, "\n Non-significant:", a_68_sig$nonsig)
```

\newpage


# Additive batch effects BEFORE longitudinal ComBat (BV)
## 308 regions

```{r message=FALSE, warning=FALSE, include=FALSE}
df <- df_308
features  <- colnames(df%>%dplyr::select(ends_with(measure)))
a_308 <- addTest("ID", "acode", features, formula, ranef, df, verbose = F)
a_308[2] <- as.numeric(unlist(a_308[colnames(a_308)[2]]))
a_308[3] <- as.numeric(unlist(a_308[colnames(a_308)[3]]))
a_308[4] <- as.numeric(unlist(a_308[colnames(a_308)[4]]))
```

\tiny

```{r echo=FALSE}
a_308 <- signif_df(a_308, 3)
kable(a_308)
```

\normalsize

```{r echo=FALSE}
a_308_sig <- a_308 %>%
  dplyr::mutate(significant = ifelse(`KR p-value` < 0.05, 1, 0)) %>%
  dplyr::summarise(sig= sum(significant==1),
                   nonsig = sum(significant==0))
cat("\n Significant:",a_308_sig$sig, "\n Non-significant:", a_308_sig$nonsig)
```

\newpage

# Additive batch effects BEFORE longitudinal ComBat (boxplot) (BV)
## 68 regions

```{r echo=FALSE, message=FALSE, warning=FALSE}
df <- df_68
features  <- colnames(df%>%dplyr::select(ends_with(measure)))
feature <- which(features==a_68[1,"Feature"], arr.ind = FALSE, useNames = TRUE)

batchBoxplot("ID", "acode", feature, formula, ranef, df,
  adjustBatch = FALSE, orderby = "mean", plotMeans = TRUE,
  colors = "grey", xlabel = "batch", ylabel = "residuals",
  title = "", verbose = F)
```

# Additive batch effects BEFORE longitudinal ComBat (boxplot) (BV)
## 308 regions

```{r echo=FALSE, message=FALSE, warning=FALSE}
df <- df_308
features  <- colnames(df%>%dplyr::select(ends_with(measure)))
feature <- which(features==a_308[1,"Feature"], arr.ind = FALSE, useNames = TRUE)

batchBoxplot("ID", "acode", feature, formula, ranef, df,
  adjustBatch = FALSE, orderby = "mean", plotMeans = TRUE,
  colors = "grey", xlabel = "batch", ylabel = "residuals",
  title = "", verbose = F)
```

\newpage

# Multiplicative batch effects BEFORE longitudinal ComBat (BV)
## 68 regions

```{r message=FALSE, warning=FALSE, include=FALSE}
df <- df_68
features  <- colnames(df%>%dplyr::select(ends_with(measure)))
m_68 <- multTest("ID", "acode", features, formula, ranef, df, verbose = F)
m_68[2] <- as.numeric(unlist(m_68[colnames(m_68)[2]]))
m_68[4] <- as.numeric(unlist(m_68[colnames(m_68)[4]]))
m_68[3] <- NULL
colnames(m_68) <- c("Feature", "$\\chi ^2$", "p-value")
```

\tiny

```{r echo=FALSE}
m_68 <- signif_df(m_68, 3)
kable(m_68)
```

\normalsize

```{r echo=FALSE}
m_68_sig <- m_68 %>%
  dplyr::mutate(significant = ifelse(`p-value` < 0.05, 1, 0)) %>%
  dplyr::summarise(sig= sum(significant==1),
                   nonsig = sum(significant==0))
cat("\n Significant:",m_68_sig$sig, "\n Non-significant:", m_68_sig$nonsig)
```

\newpage


# Multiplicative batch effects BEFORE longitudinal ComBat (BV)
## 308 regions

```{r message=FALSE, warning=FALSE, include=FALSE}
df <- df_308
features  <- colnames(df%>%dplyr::select(ends_with(measure)))
m_308 <- multTest("ID", "acode", features, formula, ranef, df, verbose = F)
m_308[2] <- as.numeric(unlist(m_308[colnames(m_308)[2]]))
m_308[4] <- as.numeric(unlist(m_308[colnames(m_308)[4]]))
m_308[3] <- NULL
colnames(m_308) <- c("Feature", "$\\chi ^2$", "p-value")
```

\tiny

```{r echo=FALSE}
m_308 <- signif_df(m_308, 3)
kable(m_308)
```

\normalsize

```{r echo=FALSE}
m_308_sig <- m_308 %>%
  dplyr::mutate(significant = ifelse(`p-value` < 0.05, 1, 0)) %>%
  dplyr::summarise(sig= sum(significant==1),
                   nonsig = sum(significant==0))
cat("\n Significant:",m_308_sig$sig, "\n Non-significant:", m_308_sig$nonsig)
```
\newpage


# Multiplicative batch effects BEFORE longitudinal ComBat (boxplot) (BV)
## 68 regions

```{r echo=FALSE, message=FALSE, warning=FALSE}
df <- df_68
features  <- colnames(df%>%dplyr::select(ends_with(measure)))
feature <- which(features==m_68[1,"Feature"], arr.ind = FALSE, useNames = TRUE)

batchBoxplot("ID", "acode", feature, formula, ranef, df,
  adjustBatch = T, orderby = "var", plotMeans = TRUE,
  colors = "grey", xlabel = "batch", ylabel = "residuals",
  title = "", verbose = F)
```

# Multiplicative batch effects BEFORE longitudinal ComBat (boxplot) (BV)
## 308 regions

```{r echo=FALSE, message=FALSE, warning=FALSE}
df <- df_308
features  <- colnames(df%>%dplyr::select(ends_with(measure)))
feature <- which(features==m_308[1,"Feature"], arr.ind = FALSE, useNames = TRUE)

batchBoxplot("ID", "acode", feature, formula, ranef, df,
  adjustBatch = T, orderby = "var", plotMeans = TRUE,
  colors = "grey", xlabel = "batch", ylabel = "residuals",
  title = "", verbose = F)
```

\newpage


# Additive batch effects AFTER longitudinal ComBat (BV)
## 68 regions

```{r message=FALSE, warning=FALSE, include=FALSE}
df <- df_68_Combat
features  <- colnames(df%>%dplyr::select(ends_with(measure)))

a_68_after <- addTest("ID", "acode", features, formula, ranef, df, verbose = F)
a_68_after[2] <- as.numeric(unlist(a_68_after[colnames(a_68_after)[2]]))
a_68_after[3] <- as.numeric(unlist(a_68_after[colnames(a_68_after)[3]]))
a_68_after[4] <- as.numeric(unlist(a_68_after[colnames(a_68_after)[4]]))
```

\tiny

```{r echo=FALSE}
a_68_after <- signif_df(a_68_after, 3)
kable(a_68_after)
```

\normalsize

```{r echo=FALSE}
a_68_after_sig <- a_68_after %>%
  dplyr::mutate(significant = ifelse(`KR p-value` < 0.05, 1, 0)) %>%
  dplyr::summarise(sig= sum(significant==1),
                   nonsig = sum(significant==0))
cat("\n Significant:",a_68_after_sig$sig, "\n Non-significant:", a_68_after_sig$nonsig)
```

\newpage


# Additive batch effects AFTER longitudinal ComBat (BV)
## 308 regions

```{r message=FALSE, warning=FALSE, include=FALSE}
df <- df_308_Combat
features  <- colnames(df%>%dplyr::select(ends_with(measure)))
a_308_after <- addTest("ID", "acode", features, formula, ranef, df, verbose = F)
a_308_after[2] <- as.numeric(unlist(a_308_after[colnames(a_308_after)[2]]))
a_308_after[3] <- as.numeric(unlist(a_308_after[colnames(a_308_after)[3]]))
a_308_after[4] <- as.numeric(unlist(a_308_after[colnames(a_308_after)[4]]))
```

\tiny

```{r echo=FALSE}
a_308_after <- signif_df(a_308_after, 3)
kable(a_308_after)
```

\normalsize

```{r echo=FALSE}
a_308_after_sig <- a_308_after %>%
  dplyr::mutate(significant = ifelse(`KR p-value` < 0.05, 1, 0)) %>%
  dplyr::summarise(sig= sum(significant==1),
                   nonsig = sum(significant==0))
cat("\n Significant:",a_308_after_sig$sig, "\n Non-significant:", a_308_after_sig$nonsig)
```

\newpage

# Additive batch effects AFTER longitudinal ComBat (boxplot) (BV)
## 68 regions

```{r echo=FALSE, message=FALSE, warning=FALSE}
df <- df_68_Combat
features  <- colnames(df%>%dplyr::select(ends_with(measure)))
feature <- which(features==a_68[1,"Feature"], arr.ind = FALSE, useNames = TRUE)

batchBoxplot("ID", "acode", feature, formula, ranef, df,
  adjustBatch = FALSE, orderby = "mean", plotMeans = TRUE,
  colors = "grey", xlabel = "batch", ylabel = "residuals",
  title = "", verbose = F)
```

# Additive batch effects AFTER longitudinal ComBat (boxplot) (BV)
## 308 regions

```{r echo=FALSE, message=FALSE, warning=FALSE}
df <- df_308_Combat
features  <- colnames(df%>%dplyr::select(ends_with(measure)))
feature <- which(features==a_308[1,"Feature"], arr.ind = FALSE, useNames = TRUE)

batchBoxplot("ID", "acode", feature, formula, ranef, df,
  adjustBatch = FALSE, orderby = "mean", plotMeans = TRUE,
  colors = "grey", xlabel = "batch", ylabel = "residuals",
  title = "", verbose = F)
```

\newpage

# Multiplicative batch effects AFTER longitudinal ComBat (BV)
## 68 regions

```{r message=FALSE, warning=FALSE, include=FALSE}
df <- df_68_Combat
features  <- colnames(df%>%dplyr::select(ends_with(measure)))
m_68_after <- multTest("ID", "acode", features, formula, ranef, df, verbose = F)
m_68_after[2] <- as.numeric(unlist(m_68_after[colnames(m_68_after)[2]]))
m_68_after[4] <- as.numeric(unlist(m_68_after[colnames(m_68_after)[4]]))
m_68_after[3] <- NULL
colnames(m_68_after) <- c("Feature", "$\\chi ^2$", "p-value")
```

\tiny

```{r echo=FALSE}
m_68_after <- signif_df(m_68_after, 3)
kable(m_68_after)
```

\normalsize

```{r echo=FALSE}
m_68_after_sig <- m_68_after %>%
  dplyr::mutate(significant = ifelse(`p-value` < 0.05, 1, 0)) %>%
  dplyr::summarise(sig= sum(significant==1),
                   nonsig = sum(significant==0))
cat("\n Significant:",m_68_after_sig$sig, "\n Non-significant:", m_68_after_sig$nonsig)
```

\newpage


# Multiplicative batch effects AFTER longitudinal ComBat (BV)
## 308 regions

```{r message=FALSE, warning=FALSE, include=FALSE}
df <- df_308_Combat
features  <- colnames(df%>%dplyr::select(ends_with(measure)))
m_308_after <- multTest("ID", "acode", features, formula, ranef, df, verbose = F)
m_308_after[2] <- as.numeric(unlist(m_308_after[colnames(m_308_after)[2]]))
m_308_after[4] <- as.numeric(unlist(m_308_after[colnames(m_308_after)[4]]))
m_308_after[3] <- NULL
colnames(m_308_after) <- c("Feature", "$\\chi ^2$", "p-value")
```

\tiny

```{r echo=FALSE}
m_308_after <- signif_df(m_308_after, 3)
kable(m_308_after)
```

\normalsize

```{r echo=FALSE}
m_308_after_sig <- m_308_after %>%
  dplyr::mutate(significant = ifelse(`p-value` < 0.05, 1, 0)) %>%
  dplyr::summarise(sig= sum(significant==1),
                   nonsig = sum(significant==0))
cat("\n Significant:",m_308_after_sig$sig, "\n Non-significant:", m_308_after_sig$nonsig)
```
\newpage


# Multiplicative batch effects AFTER longitudinal ComBat (boxplot) (BV)
## 68 regions

```{r echo=FALSE, message=FALSE, warning=FALSE}
df <- df_68_Combat
features  <- colnames(df%>%dplyr::select(ends_with(measure)))
feature <- which(features==m_68[1,"Feature"], arr.ind = FALSE, useNames = TRUE)

batchBoxplot("ID", "acode", feature, formula, ranef, df,
  adjustBatch = T, orderby = "var", plotMeans = TRUE,
  colors = "grey", xlabel = "batch", ylabel = "residuals",
  title = "", verbose = F)
```

# Multiplicative batch effects AFTER longitudinal ComBat (boxplot) (BV)
## 308 regions

```{r echo=FALSE, message=FALSE, warning=FALSE}
df <- df_308_Combat
features  <- colnames(df%>%dplyr::select(ends_with(measure)))
feature <- which(features==m_308[1,"Feature"], arr.ind = FALSE, useNames = TRUE)

batchBoxplot("ID", "acode", feature, formula, ranef, df,
  adjustBatch = T, orderby = "var", plotMeans = TRUE,
  colors = "grey", xlabel = "batch", ylabel = "residuals",
  title = "", verbose = F)
```

\newpage
