---
title: "Normative modeling in Schizophrenia - Mod 1 Hugo meeting"
author: "Noemi González Lois"
date: "`r Sys.Date()`"
output:
  pdf_document: default
  html_document: default
---


```{r, warning=F, message = F, echo = FALSE}
#install.packages("easypackages")
library("easypackages")

list.of.packages <- c("viridis", "tidyverse", "MatchIt", "grid", "png", 
                      "gridExtra", "parallel", "nlme", "JMbayes", "plyr",
                      "BiocManager", "Biostrings", "lme4", "ggplot2", "dplyr",
                      "Hmisc", "devtools", "longCombat", "neuroCombat", 
                      "tinytex", "knitr", "ggExtra", "variancePartition",
                      "Rmisc", "doParallel", "hrbrthemes", "cowplot", 
                      "BiocParallel", "effectsize", "ggpubr", "caret", "scorer",
                      "tidyr")

new.packages <- list.of.packages[!(list.of.packages %in%
                                     installed.packages()[,"Package"])]
  if(length(new.packages)>0) { install.packages(new.packages)}

libraries(list.of.packages)
ncores <- detectCores()
rm(list.of.packages, new.packages)
```


```{r, eval = F, include = FALSE}
tinytex::install_tinytex()
install_github("jcbeer/longCombat")
install_github("jfortin1/neuroCombatData")
install_github("jfortin1/neuroCombat_Rpackage")
BiocManager::install("BiocParallel")
BiocManager::install("Biostrings")
BiocManager::install("variancePartition")
install_version("dplyr", version = "1.0.5", repos = "http://cran.us.r-project.org")
tinytex::install_tinytex()
devtools::install_github("paulhendricks/scorer")
```

```{r setup I, echo=F}
knitr::opts_chunk$set(
  include = TRUE,  
  echo=TRUE, 
  eval=TRUE, 
  warning=TRUE, 
  message = TRUE,
  cache = TRUE,
  fig.width = 12,
  fig.height = 8,
  error = TRUE)
```


```{r, warning=F, message = F, echo = FALSE}
setwd("/data_J/Scripts")
source("1_DataPreparation.R")
```

# Linear Mixed Effects Model Regresion

```{r}
model_train_cv <- function(i, df, measure){
  
  # We select current region "i" and the relevant covariates:
  var_names  <- c("age", "scode", "dcode", "euler", "subID", "timepoint")
  reg_names  <- colnames(df%>%dplyr::select(ends_with(measure)))
  df <- df[ , c(reg_names[i], var_names) ]
  
  # We rename the current region "i" as "reg":
  colnames(df)[colnames(df)==reg_names[i]] <- "reg"

  # We separate data from healthy controls and patients:
  df_hc  <- df[df[,"dcode"]==0, ] 
  df_pat <- df[df[,"dcode"]==1, ] 

  # We get the unique identifiers from the healthy controls as well as from the patients:
  ids_hc  <- unique(df_hc$subID)
  ids_pat <- unique(df_pat$subID)

  # we create 10 folds with the healthy controls IDs:
  num_folds <- 10
  set.seed(123) # seed for replicability
  folds_hc <- createFolds(ids_hc, k=num_folds, list=TRUE, returnTrain=TRUE)

  # and we create as well 10 folds with the patients IDs:
  set.seed(123) # seed for replicability
  folds_pat <- createFolds(ids_pat, k=num_folds, list=TRUE, returnTrain=TRUE)
  
  # Empty structure to store the predictions:
  predictions <- NULL

  # For each fold we do:
  for(f in 1:num_folds){
    
    # We get the train and test IDs corresponding to this fold
    train_ids <- ids_hc[folds_hc[[f]]]
    test_ids  <- ids_hc[-folds_hc[[f]]]
    
    # With those, we generate the fold partitions with the brain measurement and covariates
    train <- subset(df_hc, subID%in%train_ids) # Train set for this fold
    test  <- subset(df_hc, subID%in%test_ids)  # Validation set for this fold
    
    # Fit of the longitudinal Linear Mixed Effects model
    CT_lme <- lme(as.formula("reg ~ scode + age + euler"),
               random = ~ 1 + age|subID,
               data   = train,
               control= lmeControl(opt = 'optim', 
                                   msMaxIter = 4000,
                                   method = 'REML',
                                   maxIter = 500))

  # Predictions for each control in the validation set of this fold:
  for(participant in test_ids){
    prediction_subset <- subset(test, subID==participant)
    # Dynamic predictions at the subject level:
    y_preds <- IndvPred_lme(CT_lme, newdata = prediction_subset,
                            all_times = T, timeVar = "age", M = 500,
                            return_data = T)
    # True value for current region i of this control
    y_trues <- prediction_subset[['reg']]
    
    # Save the prediction for each timepoint:
    n_tp <- nrow(prediction_subset)
    for (tp in 1:n_tp){
      y_true <- as.numeric(y_trues[tp])
      age_tp <- prediction_subset[,"age"][tp]
      y_pred <- y_preds[y_preds[,"age"]==age_tp, "pred"]
      predictions <- rbind(predictions, data.frame("fold" = f,
                                                 "region" = reg_names[i],
                                                 "sigma"  = CT_lme$sigma,
                                                 "subID"  = participant,
                                                 "diagnose"  = "control",
                                                 "timepoint" = tp,
                                                 "y_true" = y_true,
                                                 "y_pred" = y_pred))
    }
   }
  
  ##### PATIENTS #####
  
  # We get the 10% patients IDs corresponding to this fold (test with 10% patients)
  fold_ids  <- ids_pat[-folds_pat[[f]]]

  # With those, we generate a test subset with a 10% patients
  pats <- subset(df_pat, subID%in%fold_ids)

  # We make predictions for each patient with the LME model of this fold:
  for(participant in fold_ids){
    prediction_subset <- subset(pats, subID==participant)
    
    # Dynamic predictions at the subject level:
    y_preds <- IndvPred_lme(CT_lme, newdata = prediction_subset,
                            all_times = T, timeVar = "age", M = 500,
                            return_data = T)

    # True value for current region i of this patient
    y_trues <- prediction_subset[['reg']]
    
    # Save the prediction for each timepoint:
    n_tp <- nrow(prediction_subset)
    for (tp in 1:n_tp){
      y_true <- as.numeric(y_trues[tp])
      age_tp <- prediction_subset[,"age"][tp]
      y_pred <- y_preds[y_preds[,"age"]==age_tp, "pred"]
      predictions <- rbind(predictions, data.frame("fold" = f,
                                                 "region" = reg_names[i],
                                                 "sigma"  = CT_lme$sigma,
                                                 "subID"  = participant,
                                                 "diagnose"  = "patient",
                                                 "timepoint" = tp,
                                                 "y_true" = y_true,
                                                 "y_pred" = y_pred))
     }
    }
  }
return(predictions)
}
```

```{r include=FALSE}
df_68  <- getData("68")
df_308 <- getData("308")
```


```{r eval = F, include=FALSE}
################# NO MATCH IT ###################################
df <- DataPreparation(df = df_68,
                      parc = "68",
                      measure = "CT",
                      harmonization = T,
                      match = F)
measure <- "CT"
n <- length(colnames(df%>%dplyr::select(ends_with(measure))))
predictions_68NoM <- do.call(rbind, mclapply(1:n, model_train_cv,
                                 df, measure,
                                 mc.cores = ncores-1))
write.csv(predictions_68NoM,"/data_J/Results/Files/predictions_HM1_68NoM.csv", row.names = FALSE)
```

```{r eval = F, include=FALSE}
################# NO MATCH IT ###################################
df <- DataPreparation(df = df_308,
                      parc = "308",
                      harmonization = T,
                      match = F)
measure <- "_thickness"
n <- length(colnames(df%>%dplyr::select(ends_with(measure))))
predictions_308NoM <- do.call(rbind, mclapply(1:n, model_train_cv,
                                 df, measure,
                                 mc.cores = ncores-1))
write.csv(predictions_308NoM,"/data_J/Results/Files/predictions_HM1_308NoM.csv", row.names = FALSE)
```

```{r eval = F, include=FALSE}
#################### MATCH IT ###################################
df <- DataPreparation(df = df_68,
                      parc = "68",
                      harmonization = T,
                      match = T)
measure <- "CT_freesurfer"
n <- length(colnames(df%>%dplyr::select(ends_with(measure))))
predictions_68M <- do.call(rbind, mclapply(1:n, model_train_cv,
                                           df, measure,
                                           mc.cores = ncores-1))
write.csv(predictions_68M,   "/data_J/Results/Files/predictions_HM1_68M.csv",    row.names = FALSE)
```

```{r eval = F, include=FALSE}
#################### MATCH IT ###################################
df <- DataPreparation(df = df_308,
                      parc = "308",
                      harmonization = T,
                      match = T)
measure <- "_thickness"
n <- length(colnames(df%>%dplyr::select(ends_with(measure))))
predictions_308M <- do.call(rbind, mclapply(1:n, model_train_cv,
                                 df, measure,
                                 mc.cores = ncores-1))
write.csv(predictions_308M,  "/data_J/Results/Files/predictions_HM1_308M.csv",   row.names = FALSE)
```

```{r echo = FALSE}
predictions_68NoM  <- read.csv("/data_J/Results/Files/predictions_HM1_68NoM.csv" )
predictions_308NoM <- read.csv("/data_J/Results/Files/predictions_HM1_308NoM.csv")
predictions_68M    <- read.csv("/data_J/Results/Files/predictions_HM1_68M.csv"   )
predictions_308M   <- read.csv("/data_J/Results/Files/predictions_HM1_308M.csv"  )
```

```{r include=FALSE}
rm(df_308, df_68, ncores, model_train_cv)
```


# PERFORMANCE METRICS ANALYSIS

## WITHOUT TAKING INTO ACCOUNT THE FOLDS:


```{r include=FALSE}
extract_metrics <- function(df) {
  
  regs  <- unique(df$region)
  
  # We create an empty column to store the z-scores
  df["Z-score"] <- 0
  
  # and an empty structure to store the metrics
  metrics_df <- NULL
  
  for (reg in regs){
    # aux is the auxiliar variable that contains
    # the data corresponding to region "reg"
    aux <- df
    aux <- aux[aux[ ,"region"]==reg, ]
    
    # Z-SCORE
    # (true - pred)/sigma
    Z <- (aux$y_true - aux$y_pred)/aux$sigma
    df[df[,"region"]==reg,"Z-score"] <- Z
    
    # aux is the auxiliar variable that contains
    # the data corresponding to region "reg"
    aux <- df
    aux <- aux[aux[ ,"region"]==reg, ]
    
    # T-TEST
    # We get the previously calculated z-scores corresponding to controls and patients
    z_hc  <- aux[aux[, "diagnose"]== "control", "Z-score"]
    z_pat <- aux[aux[, "diagnose"]== "patient", "Z-score"]
    
    # So we have one t-test value for each region 
    # (actually there are 10 t-test values because 
    # there are 10 folds so 10 times each region)
    pval.ttest <- t.test(x = z_pat, y = z_hc, alternative = "two.sided",
                         mu = 0, var.equal = TRUE, conf.level  = 0.95)$p.value

    ### CONTROLS
    # We get the model predictions and the true values from the control data
    pred_hc  <- aux[aux[, "diagnose"]== "control","y_pred"]
    true_hc  <- aux[aux[, "diagnose"]== "control","y_true"]
  
    # CORRELATION COEFFICIENT
    # "pearson" (default), "kendall", or "spearman"
    corr.coef <- cor(pred_hc, true_hc)
    
    # Mean Absolute Error (MAE)
    MAE <- mean_absolute_error(pred_hc, true_hc)
    
    # Mean Squared Error (MSE)
    MSE <- mean_squared_error(pred_hc, true_hc)
  
    # Standardized Mean Absolute Error (SMAE)
    # It is the MAE divided by the deviation of the target values
    # The less is the better.
    SMAE <- MAE/sd(true_hc) # sd() gives the same result as --> sqrt(var(true_hc))
    
    # Standardized Mean Squared Error (SMSE)
    # It is the MSE divided by the variance of the target values
    # The less is the better. SMSE < 1 show that we learn something meaningful
    SMSE <- MSE/var(true_hc)
    
    # Coefficient of determination (R2) (same as EV)
    rss <- sum((pred_hc - true_hc) ^ 2)       # Residual Sum of Squares
    tss <- sum((true_hc - mean(true_hc)) ^ 2) # Total Sum of Squares
    r2  <- 1 - rss/tss
  
    metrics_df <- rbind(metrics_df, data.frame("region" = reg,
                                         "diagnose"  = "control",
                                         "corr" = round(corr.coef,5),
                                         "MAE"  = round(MAE,5),
                                         "MSE"  = round(MSE,5),
                                         "SMAE" = round(SMAE,5),
                                         "SMSE" = round(SMSE,5),
                                         "R2"   = round(r2,5),
                                         "pval t-test" = round(pval.ttest,5)))
    
      ### PATIENTS
      # We get the model predictions and the true values from the patients data
      pred_pat  <- aux[aux[, "diagnose"]== "patient","y_pred"]
      true_pat  <- aux[aux[, "diagnose"]== "patient","y_true"]
    
      # CORRELATION COEFFICIENT
      # "pearson" (default), "kendall", or "spearman"
      corr.coef <- cor(pred_pat, true_pat)
      
      # Mean Absolute Error (MAE)
      MAE <- mean_absolute_error(pred_pat, true_pat)
      # Mean Squared Error (MSE)
      MSE <- mean_squared_error(pred_pat, true_pat)
    
      # Standardized Mean Squared Error (SMSE)
      # It is the MSE divided by the variance of the target values
      # The less is the better. SMSE < 1 show that we learn something meaningful
      SMSE <- MSE/var(true_pat)
      # Standardized Mean Absolute Error (SMAE)
      # It is the MAE divided by the deviation of the target values
      # The less is the better. SMSE < 1 show that we learn something meaningful
      SMAE <- MAE/sd(true_pat) # sd() gives the same result as --> sqrt(var(true_pat))
    
      # Coefficient of determination (R2) (same as EV)
      rss <- sum((pred_pat - true_pat) ^ 2)       # Residual Sum of Squares
      tss <- sum((true_pat - mean(true_pat)) ^ 2) # Total Sum of Squares
      r2  <- 1 - rss/tss
    
      metrics_df <- rbind(metrics_df, data.frame("region" = reg,
                                           "diagnose"  = "patient",
                                           "corr" = round(corr.coef,5),
                                           "MAE"  = round(MAE,5),
                                           "MSE"  = round(MSE,5),
                                           "SMAE" = round(SMAE,5),
                                           "SMSE" = round(SMSE,5),
                                           "R2"   = round(r2,5),
                                           "pval t-test" = round(pval.ttest,5)))
  }

# # FDR correction for the t-test p-values
# even <- metrics_df[ !c(TRUE,FALSE), "pval.t.test"]  # Even rows (par)
# odd  <- metrics_df[ c(TRUE,FALSE), "pval.t.test"]   # Odd rows (impar)
# 
# even.FDR <- p.adjust(even, method = "fdr")  # Even rows (par)
# odd.FDR  <- p.adjust(odd,  method = "fdr")  # Odd rows (impar)
# 
# metrics_df[ !c(TRUE,FALSE), "pval.t.test.FDR"] <- even.FDR
# metrics_df[ c(TRUE,FALSE), "pval.t.test.FDR"]  <- odd.FDR

return(list("df" = df, 
            "performance" = metrics_df))
}
```


```{r eval=F, echo = FALSE}
metrics_68NoM <- extract_metrics(predictions_68NoM)
predictions_68NoM <- metrics_68NoM$df
performance_68NoM <- metrics_68NoM$performance

metrics_308NoM <- extract_metrics(predictions_308NoM)
predictions_308NoM <- metrics_308NoM$df
performance_308NoM <- metrics_308NoM$performance

metrics_68M <- extract_metrics(predictions_68M)
predictions_68M <- metrics_68M$df
performance_68M <- metrics_68M$performance

metrics_308M <- extract_metrics(predictions_308M)
predictions_308M <- metrics_308M$df
performance_308M <- metrics_308M$performance

write.csv(performance_68M, "/data_J/Results/Files/performance_68M.csv", row.names = FALSE)
write.csv(performance_308M, "/data_J/Results/Files/performance_308M.csv", row.names = FALSE)
write.csv(performance_68NoM, "/data_J/Results/Files/performance_68NoM.csv", row.names = FALSE)
write.csv(performance_308NoM, "/data_J/Results/Files/performance_308NoM.csv", row.names = FALSE)

write.csv(predictions_68M, "/data_J/Results/Files/predictions_68M.csv", row.names = FALSE)
write.csv(predictions_308M, "/data_J/Results/Files/predictions_308M.csv", row.names = FALSE)
write.csv(predictions_68NoM, "/data_J/Results/Files/predictions_68NoM.csv", row.names = FALSE)
write.csv(predictions_308NoM, "/data_J/Results/Files/predictions_308NoM.csv", row.names = FALSE)

rm(metrics_68NoM, metrics_68M, metrics_308M, metrics_308NoM, extract_metrics, 
   performance_68M, performance_308M, performance_68NoM, performance_308NoM, 
   predictions_68M, predictions_308M, predictions_68NoM, predictions_308NoM)
```

```{r echo = FALSE}
performance_68NoM  <- read.csv("/data_J/Results/Files/performance_68NoM.csv" )
performance_308NoM <- read.csv("/data_J/Results/Files/performance_308NoM.csv")
performance_68M    <- read.csv("/data_J/Results/Files/performance_68M.csv"   )
performance_308M   <- read.csv("/data_J/Results/Files/performance_308M.csv"  )
```

```{r echo = FALSE}
predictions_68NoM  <- read.csv("/data_J/Results/Files/predictions_68NoM.csv" )
predictions_308NoM <- read.csv("/data_J/Results/Files/predictions_308NoM.csv")
predictions_68M    <- read.csv("/data_J/Results/Files/predictions_68M.csv"   )
predictions_308M   <- read.csv("/data_J/Results/Files/predictions_308M.csv"  )
```

```{r include=FALSE}
# Combine all the performance metrics into one dataset:
performance_68NoM$Group  <-"68NoM"
performance_68M$Group    <-"68M"
performance_308NoM$Group <-"308NoM"
performance_308M$Group   <-"308M"

performance <- rbind(performance_68NoM, performance_68M,
                     performance_308NoM,performance_308M)

hc.performance  <- subset(performance, diagnose=="control")
pat.performance <- subset(performance, diagnose=="patient")
```


```{r include=FALSE}
#### MEAN and SD ####
hc.performance_mean_sd <- hc.performance %>%
    dplyr::group_by(Group) %>%
    dplyr::summarise(
         # SD
         MAE.sd = sd(MAE),
         MSE.sd = sd(MSE),
         SMAE.sd= sd(SMAE),
         SMSE.sd= sd(SMSE),
         corr.sd= sd(corr),
         R2.sd  = sd(R2),
         # MEAN
         MAE = mean(MAE),
         MSE = mean(MSE),
         SMAE= mean(SMAE),
         SMSE= mean(SMSE),
         corr= mean(corr),
         R2  = mean(R2))

pat.performance_mean_sd <- pat.performance %>%
    dplyr::group_by(Group) %>%
    dplyr::summarise(
         # SD
         MAE.sd = sd(MAE),
         MSE.sd = sd(MSE),
         SMAE.sd= sd(SMAE),
         SMSE.sd= sd(SMSE),
         corr.sd= sd(corr),
         R2.sd  = sd(R2),
         # MEAN
         MAE = mean(MAE),
         MSE = mean(MSE),
         SMAE= mean(SMAE),
         SMSE= mean(SMSE),
         corr= mean(corr),
         R2  = mean(R2))
```

# BOXPLOT

```{r include=FALSE}
plot_performance <- function(df, ylim.corr, ylim.mae, ylim.mse, 
                             ylim.smse, ylim.smae, ylim.r2) {
  
  plot1 <- ggplot(df, aes_string(x="Group", y="corr",
                                         group= "Group", color="Group")) +
  geom_boxplot(outlier.alpha = 0.1) +
  ylim(ylim.corr) +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.background = element_blank(),
        axis.line    = element_line(colour = "black"),
        plot.title   = element_text(size=15,face="bold"),
        axis.text.x  = element_blank(),
        axis.title.x = element_blank(),
        axis.title.y =  element_text(size = 15,face="bold"),
        legend.title = element_text(size = 15,face="bold"),
        legend.text = element_text(size  = 15),
        legend.margin=margin(0, 0, 0, -10),
        legend.position="bottom") +
  scale_color_manual(name = "Df",
                     labels = c("308M", "308NoM", "68M", "68NoM"),
                     values = c("red", "blue", "green", "#E7B800"))

  
  plot2 <- ggplot(df, aes_string(x="Group", y="MAE",
                                         group= "Group", color="Group")) +
  geom_boxplot(outlier.alpha = 0.1) +
  ylim(ylim.mae) +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.background = element_blank(),
        axis.line    = element_line(colour = "black"),
        plot.title   = element_text(size=15,face="bold"),
        axis.text.x  = element_blank(),
        axis.title.x = element_blank(),
        axis.title.y =  element_text(size = 15,face="bold"),
        legend.title = element_text(size = 15,face="bold"),
        legend.text = element_text(size  = 15),
        legend.margin=margin(0, 0, 0, -10),
        legend.position="bottom") +
  scale_color_manual(name = "Df",
                     labels = c("308M", "308NoM", "68M", "68NoM"),
                     values = c("red", "blue", "green", "#E7B800"))
  
  plot3 <- ggplot(df, aes_string(x="Group", y="MSE",
                                         group= "Group", color="Group")) +
  geom_boxplot(outlier.alpha = 0.1) +
  ylim(ylim.mse) +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.background = element_blank(),
        axis.line    = element_line(colour = "black"),
        plot.title   = element_text(size=15,face="bold"),
        axis.text.x  = element_blank(),
        axis.title.x = element_blank(),
        axis.title.y =  element_text(size = 15,face="bold"),
        legend.title = element_text(size = 15,face="bold"),
        legend.text = element_text(size  = 15),
        legend.margin=margin(0, 0, 0, -10),
        legend.position="bottom") +
  scale_color_manual(name = "Df",
                     labels = c("308M", "308NoM", "68M", "68NoM"),
                     values = c("red", "blue", "green", "#E7B800"))

  plot4 <- ggplot(df, aes_string(x="Group", y="SMSE",
                                         group= "Group", color="Group")) +
  geom_boxplot(outlier.alpha = 0.1) +
  ylim(ylim.smse) +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.background = element_blank(),
        axis.line    = element_line(colour = "black"),
        plot.title   = element_text(size=15,face="bold"),
        axis.text.x  = element_blank(),
        axis.title.x = element_blank(),
        axis.title.y =  element_text(size = 15,face="bold"),
        legend.title = element_text(size = 15,face="bold"),
        legend.text = element_text(size  = 15),
        legend.margin=margin(0, 0, 0, -10),
        legend.position="bottom") +
  scale_color_manual(name = "Df",
                     labels = c("308M", "308NoM", "68M", "68NoM"),
                     values = c("red", "blue", "green", "#E7B800"))
  
  
  plot5 <- ggplot(df, aes_string(x="Group", y="SMAE",
                                         group= "Group", color="Group")) +
  geom_boxplot(outlier.alpha = 0.1) +
  ylim(ylim.smae) +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.background = element_blank(),
        axis.line    = element_line(colour = "black"),
        plot.title   = element_text(size=15,face="bold"),
        axis.text.x  = element_blank(),
        axis.title.x = element_blank(),
        axis.title.y =  element_text(size = 15,face="bold"),
        legend.title = element_text(size = 15,face="bold"),
        legend.text = element_text(size  = 15),
        legend.margin=margin(0, 0, 0, -10),
        legend.position="bottom") +
  scale_color_manual(name = "Df",
                     labels = c("308M", "308NoM", "68M", "68NoM"),
                     values = c("red", "blue", "green", "#E7B800"))
  
  
  plot6 <- ggplot(df, aes_string(x="Group", y="R2",
                                         group= "Group", color="Group")) +
  geom_boxplot(outlier.alpha = 0.1) +
  ylim(ylim.r2) +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.background = element_blank(),
        axis.line    = element_line(colour = "black"),
        plot.title   = element_text(size=15,face="bold"),
        axis.text.x  = element_blank(),
        axis.title.x = element_blank(),
        axis.title.y =  element_text(size = 15,face="bold"),
        legend.title = element_text(size = 15,face="bold"),
        legend.text = element_text(size  = 15),
        legend.margin=margin(0, 0, 0, -10),
        legend.position="bottom") +
  scale_color_manual(name = "Df",
                     labels = c("308M", "308NoM", "68M", "68NoM"),
                     values = c("red", "blue", "green", "#E7B800"))
  
  prow <- plot_grid(
    plot1 + theme(legend.position="none"),
    plot6 + theme(legend.position="none"),
    plot2 + theme(legend.position="none"),
    plot3 + theme(legend.position="none"),
    plot5 + theme(legend.position="none"),
    plot4 + theme(legend.position="none"),
    align = 'vh',
    labels = c(" ", " ", " ", " ", " ", " "),
    hjust = -1,
    nrow = 3)

# extract a legend that is laid out horizontally
legend_b <- get_legend(
  plot1 +
    guides(color = guide_legend(nrow = 1)) +
    theme(legend.position = "bottom")
)
plot_grid(prow, legend_b, ncol = 1, rel_heights = c(1, .1))

}
```


```{r eval=T, include=FALSE}
########### Limits of the color gradients of the graphics #############
# CORR
ylim.corr <- c(min(performance$corr), max(performance$corr))

# MAE
ylim.mae <- c(min(performance$MAE), max(performance$MAE))

# MSE
ylim.mse <- c(min(performance$MSE), max(performance$MSE))

# SMSE
ylim.smse <- c(min(performance$SMSE), max(performance$SMSE))

# SMAE
ylim.smae <- c(min(performance$SMAE),max(performance$SMAE))

# R2
ylim.r2 <- c(min(performance$R2),max(performance$R2))

rm(performance)
```

## HEALTHY CONTROLS

```{r echo=FALSE, fig.height=5, fig.width=5, message=FALSE, warning=FALSE}
plot_performance(hc.performance, ylim.corr, ylim.mae, ylim.mse, 
                 ylim.smse, ylim.smae, ylim.r2)
```

## PATIENTS


```{r echo=FALSE, fig.height=5, fig.width=5, message=FALSE, warning=FALSE}
plot_performance(pat.performance, ylim.corr, ylim.mae, ylim.mse, 
                 ylim.smse, ylim.smae, ylim.r2)
```

```{r include=FALSE}
rm(ylim.corr, ylim.mae, ylim.mse, ylim.smse, ylim.smae, ylim.r2, 
   plot_performance, hc.performance, pat.performance, performance_308M, 
   performance_308NoM, performance_68M, performance_68NoM, extract_metrics)
```


# SCATTERPLOT + ERROR BAND

```{r include=FALSE}
plot_performance_mean_sd <- function(df, ylim.corr, ylim.mae, ylim.mse, 
                             ylim.smse, ylim.smae, ylim.r2) {
  
  plot1 <- ggplot(df, aes_string(x="Group", y="corr",
                                         group= "Group", color="Group")) +
  geom_point(aes(shape=Group, color=Group), size=4) +
  ylim(ylim.corr) +
  geom_errorbar(aes(ymin=corr-corr.sd, ymax=corr+corr.sd),
                position = position_dodge(width=0.9), width=.2, color="black") +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.background = element_blank(),
        axis.line    = element_line(colour = "black"),
        plot.title   = element_text(size=15,face="bold"),
        axis.text.x  = element_blank(),
        axis.title.x = element_blank(),
        axis.title.y =  element_text(size = 15,face="bold"),
        legend.title = element_text(size = 15,face="bold"),
        legend.text = element_text(size  = 15),
        legend.margin=margin(0, 0, 0, -10),
        legend.position="bottom") +
  scale_shape_manual(name = "Df",
                     labels = c("308M", "308NoM", "68M", "68NoM"),
                     values = c(15, 16, 17, 18)) +
  scale_color_manual(name = "Df",
                     labels = c("308M", "308NoM", "68M", "68NoM"),
                     values = c("red", "blue", "green", "#E7B800"))
  
  plot2 <- ggplot(df, aes_string(x="Group", y="MAE",
                                         group= "Group", color="Group")) +
  geom_point(aes(shape=Group, color=Group), size=4) +
  geom_errorbar(aes(ymin=MAE-MAE.sd, ymax=MAE+MAE.sd),
                position = position_dodge(width=0.9), width=.2, color="black") +
  ylim(ylim.mae) +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.background = element_blank(),
        axis.line    = element_line(colour = "black"),
        plot.title   = element_text(size=15,face="bold"),
        axis.text.x  = element_blank(),
        axis.title.x = element_blank(),
        axis.title.y =  element_text(size = 15,face="bold"),
        legend.title = element_text(size = 15,face="bold"),
        legend.text = element_text(size  = 15),
        legend.margin=margin(0, 0, 0, -10),
        legend.position="bottom") +
  scale_shape_manual(name = "Df",
                     labels = c("308M", "308NoM", "68M", "68NoM"),
                     values = c(15, 16, 17, 18)) +
  scale_color_manual(name = "Df",
                     labels = c("308M", "308NoM", "68M", "68NoM"),
                     values = c("red", "blue", "green", "#E7B800"))
  
  plot3 <- ggplot(df, aes_string(x="Group", y="MSE",
                                         group= "Group", color="Group")) +
  geom_point(aes(shape=Group, color=Group), size=4) +
  geom_errorbar(aes(ymin=MSE-MSE.sd, ymax=MSE+MSE.sd),
                position = position_dodge(width=0.9), width=.2, color="black") +
  ylim(ylim.mse) +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.background = element_blank(),
        axis.line    = element_line(colour = "black"),
        plot.title   = element_text(size=15,face="bold"),
        axis.text.x  = element_blank(),
        axis.title.x = element_blank(),
        axis.title.y =  element_text(size = 15,face="bold"),
        legend.title = element_text(size = 15,face="bold"),
        legend.text = element_text(size  = 15),
        legend.margin=margin(0, 0, 0, -10),
        legend.position="bottom") +
  scale_shape_manual(name = "Df",
                     labels = c("308M", "308NoM", "68M", "68NoM"),
                     values = c(15, 16, 17, 18)) +
  scale_color_manual(name = "Df",
                     labels = c("308M", "308NoM", "68M", "68NoM"),
                     values = c("red", "blue", "green", "#E7B800"))

  plot4 <- ggplot(df, aes_string(x="Group", y="SMSE",
                                         group= "Group", color="Group")) +
  geom_point(aes(shape=Group, color=Group), size=4) +
  geom_errorbar(aes(ymin=SMSE-SMSE.sd, ymax=SMSE+SMSE.sd),
                position = position_dodge(width=0.9), width=.2, color="black") +
  ylim(ylim.smse) +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.background = element_blank(),
        axis.line    = element_line(colour = "black"),
        plot.title   = element_text(size=15,face="bold"),
        axis.text.x  = element_blank(),
        axis.title.x = element_blank(),
        axis.title.y =  element_text(size = 15,face="bold"),
        legend.title = element_text(size = 15,face="bold"),
        legend.text = element_text(size  = 15),
        legend.margin=margin(0, 0, 0, -10),
        legend.position="bottom") +
  scale_shape_manual(name = "Df",
                     labels = c("308M", "308NoM", "68M", "68NoM"),
                     values = c(15, 16, 17, 18)) +
  scale_color_manual(name = "Df",
                     labels = c("308M", "308NoM", "68M", "68NoM"),
                     values = c("red", "blue", "green", "#E7B800"))
  
  
  plot5 <- ggplot(df, aes_string(x="Group", y="SMAE",
                                         group= "Group", color="Group")) +
  geom_point(aes(shape=Group, color=Group), size=4) +
  geom_errorbar(aes(ymin=SMAE-SMAE.sd, ymax=SMAE+SMAE.sd),
                position = position_dodge(width=0.9), width=.2, color="black") +
  ylim(ylim.smae) +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.background = element_blank(),
        axis.line    = element_line(colour = "black"),
        plot.title   = element_text(size=15,face="bold"),
        axis.text.x  = element_blank(),
        axis.title.x = element_blank(),
        axis.title.y =  element_text(size = 15,face="bold"),
        legend.title = element_text(size = 15,face="bold"),
        legend.text = element_text(size  = 15),
        legend.margin=margin(0, 0, 0, -10),
        legend.position="bottom") +
  scale_shape_manual(name = "Df",
                     labels = c("308M", "308NoM", "68M", "68NoM"),
                     values = c(15, 16, 17, 18)) +
  scale_color_manual(name = "Df",
                     labels = c("308M", "308NoM", "68M", "68NoM"),
                     values = c("red", "blue", "green", "#E7B800"))
  
  
  plot6 <- ggplot(df, aes_string(x="Group", y="R2",
                                         group= "Group", color="Group")) +
  geom_point(aes(shape=Group, color=Group), size=4) +
  geom_errorbar(aes(ymin=R2-R2.sd, ymax=R2+R2.sd),
                position = position_dodge(width=0.9), width=.2, color="black") +
  ylim(ylim.r2) +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.background = element_blank(),
        axis.line    = element_line(colour = "black"),
        plot.title   = element_text(size=15,face="bold"),
        axis.text.x  = element_blank(),
        axis.title.x = element_blank(),
        axis.title.y =  element_text(size = 15,face="bold"),
        legend.title = element_text(size = 15,face="bold"),
        legend.text = element_text(size  = 15),
        legend.margin=margin(0, 0, 0, -10),
        legend.position="bottom") +
  scale_shape_manual(name = "Df",
                     labels = c("308M", "308NoM", "68M", "68NoM"),
                     values = c(15, 16, 17, 18)) +
  scale_color_manual(name = "Df",
                     labels = c("308M", "308NoM", "68M", "68NoM"),
                     values = c("red", "blue", "green", "#E7B800"))
  
  # PLOT ARRANGING
  figure <- ggarrange(plot1, plot6, plot3, plot2, plot4, plot5, ncol = 2, nrow = 3, 
                      common.legend = TRUE, legend="bottom")
  figure

}

```

```{r eval=T, include=FALSE}
########### Limits of the graphics #############
# CORR
ylim.corr <- c(min(hc.performance_mean_sd$corr - hc.performance_mean_sd$corr.sd, 
                   pat.performance_mean_sd$corr- pat.performance_mean_sd$corr.sd),
               max(hc.performance_mean_sd$corr + hc.performance_mean_sd$corr.sd, 
                   pat.performance_mean_sd$corr+ pat.performance_mean_sd$corr.sd))
# MAE
ylim.mae <- c(min(hc.performance_mean_sd$MAE - hc.performance_mean_sd$MAE.sd, 
                   pat.performance_mean_sd$MAE- pat.performance_mean_sd$MAE.sd),
               max(hc.performance_mean_sd$MAE + hc.performance_mean_sd$MAE.sd, 
                   pat.performance_mean_sd$MAE+ pat.performance_mean_sd$MAE.sd))

# MSE
ylim.mse <- c(min(hc.performance_mean_sd$MSE - hc.performance_mean_sd$MSE.sd, 
                   pat.performance_mean_sd$MSE- pat.performance_mean_sd$MSE.sd),
               max(hc.performance_mean_sd$MSE + hc.performance_mean_sd$MSE.sd, 
                   pat.performance_mean_sd$MSE+ pat.performance_mean_sd$MSE.sd))
# SMSE
ylim.smse <- c(min(hc.performance_mean_sd$SMSE - hc.performance_mean_sd$SMSE.sd, 
                   pat.performance_mean_sd$SMSE- pat.performance_mean_sd$SMSE.sd),
               max(hc.performance_mean_sd$SMSE + hc.performance_mean_sd$SMSE.sd, 
                   pat.performance_mean_sd$SMSE+ pat.performance_mean_sd$SMSE.sd))
# SMAE
ylim.smae <- c(min(hc.performance_mean_sd$SMAE - hc.performance_mean_sd$SMAE.sd, 
                   pat.performance_mean_sd$SMAE- pat.performance_mean_sd$SMAE.sd),
               max(hc.performance_mean_sd$SMAE + hc.performance_mean_sd$SMAE.sd, 
                   pat.performance_mean_sd$SMAE+ pat.performance_mean_sd$SMAE.sd))

# R2
ylim.r2 <- c(min(hc.performance_mean_sd$R2 - hc.performance_mean_sd$R2.sd, 
                   pat.performance_mean_sd$R2- pat.performance_mean_sd$R2.sd),
               max(hc.performance_mean_sd$R2 + hc.performance_mean_sd$R2.sd, 
                   pat.performance_mean_sd$R2+ pat.performance_mean_sd$R2.sd))


```

## HEALTHY CONTROLS


```{r echo=FALSE, fig.height=5, fig.width=5, message=FALSE, warning=FALSE}
plot_performance_mean_sd(hc.performance_mean_sd, ylim.corr, ylim.mae, ylim.mse,
                             ylim.smse, ylim.smae, ylim.r2)
```




## PATIENTS

```{r echo=FALSE, fig.height=5, fig.width=5, message=FALSE, warning=FALSE}
plot_performance_mean_sd(pat.performance_mean_sd, ylim.corr, ylim.mae, ylim.mse, 
                             ylim.smse, ylim.smae, ylim.r2)
```



## TAKING INTO ACCOUNT THE FOLDS:

```{r include=FALSE}
extract_metrics_f <- function(df) {
  
  regs  <- unique(df$region)
  
  # We create an empty column to store the z-scores
  df["Z-score"] <- 0
  
  # and an empty structure to store the metrics
  metrics_df <- NULL
  
  for (reg in regs){
    for (f in 1:10) {
      # aux is the auxiliar variable that contains
      # the data corresponding to fold "f" region "reg"
      aux <- df
      aux <- aux[aux[ ,"fold"  ]==f,   ]
      aux <- aux[aux[ ,"region"]==reg, ]
      
      # Z-SCORE
      # (true - pred)/sigma
      Z <- (aux$y_true - aux$y_pred)/aux$sigma
      df[df[,"region"]==reg,][df[df[,"region"]==reg,][,"fold"]==f,"Z-score"] <- Z

      # aux is the auxiliar variable that contains
      # the data corresponding to fold "f" region "reg"
      aux <- df
      aux <- aux[aux[ ,"fold"  ]==f,   ]
      aux <- aux[aux[ ,"region"]==reg, ]
      
      # T-TEST
      # We get the previously calculated z-scores corresponding to controls and patients
      z_hc  <- aux[aux[, "diagnose"]== "control", "Z-score"]
      z_pat <- aux[aux[, "diagnose"]== "patient", "Z-score"]
      
      pval.ttest <- t.test(x = z_pat, y = z_hc, alternative = "two.sided",
                           mu = 0, var.equal = TRUE, conf.level  = 0.95)$p.value
      
      ### CONTROLS
      # We get the model predictions and the true values from the control data
      pred_hc  <- aux[aux[, "diagnose"]== "control", "y_pred"]
      true_hc  <- aux[aux[, "diagnose"]== "control", "y_true"]
    
      # CORRELATION COEFFICIENT
      # "pearson" (default), "kendall", or "spearman"
      corr.coef <- cor(pred_hc, true_hc)
      
      # Mean Absolute Error (MAE)
      MAE <- mean_absolute_error(pred_hc, true_hc)
      # Mean Squared Error (MSE)
      MSE <- mean_squared_error(pred_hc, true_hc)
    
      # Standardized Mean Squared Error (SMSE)
      # It is the MSE divided by the variance of the true values
      # The less is the better. SMSE < 1 show that we learn something meaningful
      SMSE <- MSE/var(true_hc)

      # Standardized Mean Absolute Error (SMAE)
      # It is the MAE divided by the deviation of the true values
      # The less is the better. 
      SMAE <- MAE/sd(true_hc)
      
      # Coefficient of determination (R2) (same as EV)
      rss <- sum((pred_hc - true_hc) ^ 2)       # Residual Sum of Squares
      tss <- sum((true_hc - mean(true_hc)) ^ 2) # Total Sum of Squares
      r2  <- 1 - rss/tss
    
      metrics_df <- rbind(metrics_df, data.frame("region" = reg,
                                           "fold"   = f,
                                           "diagnose"  = "control",
                                           "corr" = round(corr.coef,5),
                                           "MAE"  = round(MAE,5),
                                           "MSE"  = round(MSE,5),
                                           "SMSE" = round(SMSE,5),
                                           "SMAE" = round(SMAE,5),
                                           "R2"   = round(r2,5),
                                           "pval t-test" = round(pval.ttest,5)))
      
      ### PATIENTS
      # We get the model predictions and the true values from the patients data
      pred_pat  <- aux[aux[, "diagnose"]== "patient","y_pred"]
      true_pat  <- aux[aux[, "diagnose"]== "patient","y_true"]
    
      # CORRELATION COEFFICIENT
      # "pearson" (default), "kendall", or "spearman"
      corr.coef <- cor(pred_pat, true_pat)
      
      # Mean Absolute Error (MAE)
      MAE <- mean_absolute_error(pred_pat, true_pat)
      # Mean Squared Error (MSE)
      MSE <- mean_squared_error(pred_pat, true_pat)
    
      # Standardized Mean Squared Error (SMSE)
      # It is the MSE divided by the variance of the true values
      # The less is the better. SMSE < 1 show that we learn something meaningful
      SMSE <- MSE/var(true_pat)

      # Standardized Mean Absolute Error (SMAE)
      # It is the MAE divided by the deviation of the true values
      # The less is the better. 
      SMAE <- MAE/sd(true_pat)
        
      # Coefficient of determination (R2)
      rss <- sum((pred_pat - true_pat) ^ 2)       # Residual Sum of Squares
      tss <- sum((true_pat - mean(true_pat)) ^ 2) # Total Sum of Squares
      r2  <- 1 - rss/tss
    
      metrics_df <- rbind(metrics_df, data.frame("region" = reg,
                                           "fold"   = f,
                                           "diagnose"  = "patient",
                                           "corr" = round(corr.coef,5),
                                           "MAE"  = round(MAE,5),
                                           "MSE"  = round(MSE,5),
                                           "SMSE" = round(SMSE,5),
                                           "SMAE" = round(SMAE,5),
                                           "R2"   = round(r2,5),
                                           "pval t-test" = round(pval.ttest,5))) 
    }
  }

# # FDR correction for the t-test p-values, 
# # by fold (fold 1:correct FDR for all regions, fold 2:..., and so on...)
#     metrics_df$pval.t.test.FDR <- 0
#     for (f in 1:10) {
#       metrics_df_f <- subset(metrics_df, fold==f)
#       even <- metrics_df_f[!c(TRUE, FALSE), "pval.t.test"]  # Even rows (par)
#       odd  <- metrics_df_f[ c(TRUE, FALSE), "pval.t.test"]  # Odd rows (impar)
#       even.FDR <- p.adjust(even, method = "fdr")  # Even rows (par)
#       odd.FDR  <- p.adjust(odd,  method = "fdr")  # Odd rows (impar)
#       metrics_df_f[ !c(TRUE,FALSE), "pval.t.test.FDR"] <- even.FDR
#       metrics_df_f[  c(TRUE,FALSE), "pval.t.test.FDR"] <- odd.FDR
#       metrics_df[metrics_df[ , "fold"]==f, "pval.t.test.FDR"] <- metrics_df_f[,"pval.t.test.FDR"]
#       }

return(list("df" = df, 
            "performance" = metrics_df))
}
```


```{r eval = F, include=FALSE}
metrics_68NoM <- extract_metrics_f(predictions_68NoM)
performance_68NoM_f <- metrics_68NoM$performance

metrics_308NoM <- extract_metrics_f(predictions_308NoM)
performance_308NoM_f <- metrics_308NoM$performance

metrics_68M <- extract_metrics_f(predictions_68M)
performance_68M_f <- metrics_68M$performance

metrics_308M <- extract_metrics_f(predictions_308M)
performance_308M_f <- metrics_308M$performance

write.csv(performance_308M_f,"/data_J/Results/Files/performance_308M_f.csv", row.names = FALSE)
write.csv(performance_308NoM_f,"/data_J/Results/Files/performance_308NoM_f.csv", row.names = FALSE)
write.csv(performance_68M_f,"/data_J/Results/Files/performance_68M_f.csv", row.names = FALSE)
write.csv(performance_68NoM_f,"/data_J/Results/Files/performance_68NoM_f.csv", row.names = FALSE)

rm(metrics_68NoM, metrics_308NoM, metrics_68M, metrics_308M)
```


```{r echo = FALSE}
performance_68NoM_f  <- read.csv("/data_J/Results/Files/performance_68NoM_f.csv" )
performance_308NoM_f <- read.csv("/data_J/Results/Files/performance_308NoM_f.csv")
performance_68M_f    <- read.csv("/data_J/Results/Files/performance_68M_f.csv"   )
performance_308M_f   <- read.csv("/data_J/Results/Files/performance_308M_f.csv"  )

rm(extract_metrics_f)
```

```{r echo = FALSE}
##### Combine all the predictions into one dataset ####
performance_68NoM_f$Group  <-"68NoM"
performance_68M_f$Group    <-"68M"
performance_308NoM_f$Group <-"308NoM"
performance_308M_f$Group   <-"308M"

performance_f <- rbind(performance_68NoM_f, performance_68M_f,
                     performance_308NoM_f, performance_308M_f)
```


```{r include=FALSE}
plot_matrix <- function(df, nreg, ylim.corr, ylim.mae, ylim.mse, 
                        ylim.smse, ylim.smae, ylim.r2) {
  df$regionN  <- rep(1:nreg,each=10)
  
  # CORRELATION
  p1 <- ggplot(df, aes(fold, regionN)) +
  scale_x_continuous(breaks = c(1:10)) + 
  geom_raster(aes(fill = corr)) +
  labs(x = " ",
     y = " ",
     title = " ") +
  ggtitle(expression(rho)) +
  theme(panel.grid.major = element_blank(),
      panel.grid.minor = element_blank(),
      panel.background = element_blank(),
      axis.line    = element_line(colour = "black"),
      plot.title   = element_text(size=15),
      axis.text    = element_text(size=10),
      axis.title   = element_text(size=10,face="bold"),
      legend.title = element_blank()) + 
  scale_fill_gradientn(colours = c("blue", "red"),
                       limits=c(ylim.corr))

  # MAE
  p2 <-   ggplot(df, aes(fold, regionN)) +
  scale_x_continuous(breaks = c(1:10)) + 
  geom_raster(aes(fill = MAE)) +
  labs(x = " ",
     y = " ",
     title = "MAE") +
  theme(panel.grid.major = element_blank(),
      panel.grid.minor = element_blank(),
      panel.background = element_blank(),
      axis.line    = element_line(colour = "black"),
      plot.title   = element_text(size=15),
      axis.text    = element_text(size=10),
      axis.title   = element_text(size=10,face="bold"),
      legend.title = element_blank()) + 
  scale_fill_gradientn(colours = c("blue", "red"),
                       limits=c(ylim.mae))

  # MSE
  p3 <- ggplot(df, aes(fold, regionN)) +
  scale_x_continuous(breaks = c(1:10)) + 
  geom_raster(aes(fill = MSE)) +
  labs(x = " ",
     y = " ",
     title = "MSE") +
  theme(panel.grid.major = element_blank(),
      panel.grid.minor = element_blank(),
      panel.background = element_blank(),
      axis.line    = element_line(colour = "black"),
      plot.title   = element_text(size=15),
      axis.text    = element_text(size=10),
      axis.title   = element_text(size=10,face="bold"),
      legend.title = element_blank()) + 
  scale_fill_gradientn(colours = c("blue", "red"),
                       limits=c(ylim.mse))
  
  # SMSE
  p4 <- ggplot(df, aes(fold, regionN)) +
  scale_x_continuous(breaks = c(1:10)) + 
  geom_raster(aes(fill = SMSE)) +
  labs(x = " ",
     y = " ",
     title = "SMSE") +
  theme(panel.grid.major = element_blank(),
      panel.grid.minor = element_blank(),
      panel.background = element_blank(),
      axis.line    = element_line(colour = "black"),
      plot.title   = element_text(size=15),
      axis.text    = element_text(size=10),
      axis.title   = element_text(size=10,face="bold"),
      legend.title = element_blank()) + 
  scale_fill_gradientn(colours = c("blue", "red"),
                       limits=c(ylim.smse))
  
  # SMAE
  p5 <- ggplot(df, aes(fold, regionN)) +
  scale_x_continuous(breaks = c(1:10)) + 
  geom_raster(aes(fill = SMAE)) +
  labs(x = " ",
     y = " ",
     title = "SMAE") +
  theme(panel.grid.major = element_blank(),
      panel.grid.minor = element_blank(),
      panel.background = element_blank(),
      axis.line    = element_line(colour = "black"),
      plot.title   = element_text(size=15),
      axis.text    = element_text(size=10),
      axis.title   = element_text(size=10,face="bold"),
      legend.title = element_blank()) + 
  scale_fill_gradientn(colours = c("blue", "red"),
                       limits=c(ylim.smae))
    
  # Coefficient of determination (R2)
  p6 <- ggplot(df, aes(fold, regionN)) +
  scale_x_continuous(breaks = c(1:10)) + 
  geom_raster(aes(fill = R2)) +
  labs(x = " ",
     y = " ",
     title = " ") +
  ggtitle(bquote(~R^2))+
  theme(panel.grid.major = element_blank(),
      panel.grid.minor = element_blank(),
      panel.background = element_blank(),
      axis.line    = element_line(colour = "black"),
      plot.title   = element_text(size=15),
      axis.text    = element_text(size=10),
      axis.title   = element_text(size=10,face="bold"),
      legend.title = element_blank()) + 
  scale_fill_gradientn(colours = c("blue", "red"),
                       limits=c(ylim.r2))
  
  # PLOT ARRANGING
  figure <- ggarrange(p1, p6, p2, p3, p5, p4, ncol = 2, nrow = 3)
  annotate_figure(figure,
                  left = text_grob("Region", rot = 90, face = "bold", 
                                   size = 15, color = "black"),
                  bottom = text_grob("fold", 
                                     face = "bold", size = 15, color = "black"))
}
```


## 68 regions (NoM)

```{r include=FALSE}
performance_68NoM_f.hc   <- subset(performance_68NoM_f, diagnose=="control")
performance_68NoM_f.pat  <- subset(performance_68NoM_f, diagnose=="patient")
```

```{r echo = FALSE}
#### Limits of the gradients ####
# CORR
ylim.corr <- c(min(c(performance_68NoM_f$corr, performance_68M_f$corr)),
               max(c(performance_68NoM_f$corr, performance_68M_f$corr)))
# MAE
ylim.mae <- c(min(c(performance_68NoM_f$MAE, performance_68M_f$MAE)),
              max(c(performance_68NoM_f$MAE, performance_68M_f$MAE)))
# MSE
ylim.mse <- c(min(c(performance_68NoM_f$MSE, performance_68M_f$MSE)),
              max(c(performance_68NoM_f$MSE, performance_68M_f$MSE)))
# SMSE
ylim.smse <- c(min(c(performance_68NoM_f$SMSE, performance_68M_f$SMSE)),
              max(c(performance_68NoM_f$SMSE, performance_68M_f$SMSE)))
# SMAE
ylim.smae <- c(min(c(performance_68NoM_f$SMAE, performance_68M_f$SMAE)),
              max(c(performance_68NoM_f$SMAE, performance_68M_f$SMAE)))
# R2
ylim.r2 <- c(min(c(performance_68NoM_f$R2, performance_68M_f$R2)),
              max(c(performance_68NoM_f$R2, performance_68M_f$R2)))
rm(performance_f)
```


### HEALTHY CONTROLS

```{r echo=FALSE, fig.width = 10, fig.height = 10}
plot_matrix(performance_68NoM_f.hc, 68, ylim.corr, ylim.mae, ylim.mse, 
                 ylim.smse, ylim.smae, ylim.r2)
```

### PATIENTS

```{r echo=FALSE, fig.width = 10, fig.height = 8}
plot_matrix(performance_68NoM_f.pat, 68, ylim.corr, ylim.mae, ylim.mse, 
                 ylim.smse, ylim.smae, ylim.r2)
```

## 68 regions (M)

```{r include=FALSE}
performance_68M_f.hc  <- subset(performance_68M_f, diagnose=="control")
performance_68M_f.pat <- subset(performance_68M_f, diagnose=="patient")
```

### HEALTHY CONTROLS

```{r echo=FALSE, fig.width = 10, fig.height = 8}
plot_matrix(performance_68M_f.hc, 68, ylim.corr, ylim.mae, ylim.mse, 
                 ylim.smse, ylim.smae, ylim.r2)
```

### PATIENTS

```{r echo=FALSE, fig.width = 10, fig.height = 8}
plot_matrix(performance_68M_f.pat, 68, ylim.corr, ylim.mae, ylim.mse, 
                 ylim.smse, ylim.smae, ylim.r2)
```

## Difference between NoM and M (68 Regions)

```{r echo=FALSE}
diff_68_NoM_M_hc <- cbind(performance_68NoM_f.hc[,1:3],
                       abs(performance_68NoM_f.hc[,4:9] - performance_68M_f.hc[,4:9]))
diff_68_NoM_M_pat <- cbind(performance_68NoM_f.pat[,1:3],
                       abs(performance_68NoM_f.pat[,4:9] - performance_68M_f.pat[,4:9]))

ylim.corr <- c(min(c(diff_68_NoM_M_pat$corr, diff_68_NoM_M_hc$corr)),
               max(c(diff_68_NoM_M_pat$corr, diff_68_NoM_M_hc$corr)))
ylim.mae  <- c(min(c(diff_68_NoM_M_pat$MAE, diff_68_NoM_M_hc$MAE)),
               max(c(diff_68_NoM_M_pat$MAE, diff_68_NoM_M_hc$MAE)))
ylim.mse  <- c(min(c(diff_68_NoM_M_pat$MSE, diff_68_NoM_M_hc$MSE)),
               max(c(diff_68_NoM_M_pat$MSE, diff_68_NoM_M_hc$MSE)))
ylim.smse <- c(min(c(diff_68_NoM_M_pat$SMSE, diff_68_NoM_M_hc$SMSE)),
               max(c(diff_68_NoM_M_pat$SMSE, diff_68_NoM_M_hc$SMSE)))
ylim.smae <- c(min(c(diff_68_NoM_M_pat$SMAE, diff_68_NoM_M_hc$SMAE)),
               max(c(diff_68_NoM_M_pat$SMAE, diff_68_NoM_M_hc$SMAE)))
ylim.r2   <- c(min(c(diff_68_NoM_M_pat$R2, diff_68_NoM_M_hc$R2)),
               max(c(diff_68_NoM_M_pat$R2, diff_68_NoM_M_hc$R2)))
```


## Healthy controls:

```{r echo=FALSE, fig.width = 10, fig.height = 8}
plot_matrix(diff_68_NoM_M_hc, 68, ylim.corr, ylim.mae, ylim.mse, ylim.smse, ylim.smae, ylim.r2)
```

## Patients: 

```{r echo=FALSE, fig.width = 10, fig.height = 8}
plot_matrix(diff_68_NoM_M_pat, 68, ylim.corr, ylim.mae, ylim.mse, ylim.smse, ylim.smae, ylim.r2)
```


## 308 regions (NoM)

```{r include=FALSE}
performance_308NoM_f.hc  <- subset(performance_308NoM_f, diagnose=="control")
performance_308NoM_f.pat <- subset(performance_308NoM_f, diagnose=="patient")
```

```{r echo = FALSE}
#### Limits of the gradients ####
# CORR
ylim.corr <- c(min(c(performance_308NoM_f$corr, performance_308M_f$corr)),
               max(c(performance_308NoM_f$corr, performance_308M_f$corr)))
# MAE
ylim.mae <- c(min(c(performance_308NoM_f$MAE, performance_308M_f$MAE)),
              max(c(performance_308NoM_f$MAE, performance_308M_f$MAE)))
# MSE
ylim.mse <- c(min(c(performance_308NoM_f$MSE, performance_308M_f$MSE)),
              max(c(performance_308NoM_f$MSE, performance_308M_f$MSE)))
# SMSE
ylim.smse <- c(min(c(performance_308NoM_f$SMSE, performance_308M_f$SMSE)),
               max(c(performance_308NoM_f$SMSE, performance_308M_f$SMSE)))
# SMAE
ylim.smae <- c(min(c(performance_308NoM_f$SMAE, performance_308M_f$SMAE)),
               max(c(performance_308NoM_f$SMAE, performance_308M_f$SMAE)))
# R2
ylim.r2 <- c(min(c(performance_308NoM_f$R2, performance_68M_f$R2)),
             max(c(performance_308NoM_f$R2, performance_68M_f$R2)))
rm(performance_f)
```

### HEALTHY CONTROLS

```{r echo=FALSE, fig.width = 10, fig.height = 8}
plot_matrix(performance_308NoM_f.hc, 308, ylim.corr, ylim.mae, ylim.mse, 
            ylim.smse, ylim.smae, ylim.r2)
```

### PATIENTS

```{r echo=FALSE, fig.width = 10, fig.height = 8}
plot_matrix(performance_308NoM_f.pat, 308, ylim.corr, ylim.mae, ylim.mse, 
            ylim.smse, ylim.smae, ylim.r2)
```

## 308 regions (M)

```{r include=FALSE}
performance_308M_f.hc  <- subset(performance_308M_f, diagnose=="control")
performance_308M_f.pat <- subset(performance_308M_f, diagnose=="patient")
```

## HEALTHY CONTROLS

```{r echo=FALSE, fig.width = 10, fig.height = 8}
plot_matrix(performance_308M_f.hc, 308, ylim.corr, ylim.mae, ylim.mse, 
            ylim.smse, ylim.smae, ylim.r2)
```

## PATIENTS

```{r echo=FALSE, fig.width = 10, fig.height = 8}
plot_matrix(performance_308M_f.pat, 308, ylim.corr, ylim.mae, ylim.mse, 
            ylim.smse, ylim.smae, ylim.r2)
```

## Difference between NoM and M

```{r echo=FALSE, fig.width = 10, fig.height = 8}
diff_308_NoM_M_hc <- cbind(performance_308NoM_f.hc[,1:3],
                       abs(performance_308NoM_f.hc[,4:9] - performance_308M_f.hc[,4:9]))
diff_308_NoM_M_pat <- cbind(performance_308NoM_f.pat[,1:3],
                       abs(performance_308NoM_f.pat[,4:9] - performance_308M_f.pat[,4:9]))

ylim.corr <- c(min(c(diff_308_NoM_M_pat$corr, diff_308_NoM_M_hc$corr)),
               max(c(diff_308_NoM_M_pat$corr, diff_308_NoM_M_hc$corr)))
ylim.mae  <- c(min(c(diff_308_NoM_M_pat$MAE, diff_308_NoM_M_hc$MAE)),
               max(c(diff_308_NoM_M_pat$MAE, diff_308_NoM_M_hc$MAE)))
ylim.mse  <- c(min(c(diff_308_NoM_M_pat$MSE, diff_308_NoM_M_hc$MSE)),
               max(c(diff_308_NoM_M_pat$MSE, diff_308_NoM_M_hc$MSE)))
ylim.smse <- c(min(c(diff_308_NoM_M_pat$SMSE, diff_308_NoM_M_hc$SMSE)),
               max(c(diff_308_NoM_M_pat$SMSE, diff_308_NoM_M_hc$SMSE)))
ylim.smae <- c(min(c(diff_308_NoM_M_pat$SMAE, diff_308_NoM_M_hc$SMAE)),
               max(c(diff_308_NoM_M_pat$SMAE, diff_308_NoM_M_hc$SMAE)))
ylim.r2   <- c(min(c(diff_308_NoM_M_pat$R2, diff_308_NoM_M_hc$R2)),
               max(c(diff_308_NoM_M_pat$R2, diff_308_NoM_M_hc$R2)))
```

## Healthy controls:

```{r echo=FALSE, fig.width = 10, fig.height = 8}
plot_matrix(diff_308_NoM_M_hc, 308, ylim.corr, ylim.mae, ylim.mse, ylim.smse, ylim.smae, ylim.r2)
```

## Patients: 

```{r echo=FALSE, fig.width = 10, fig.height = 8}
plot_matrix(diff_308_NoM_M_pat, 308, ylim.corr, ylim.mae, ylim.mse, ylim.smse, ylim.smae, ylim.r2)
```


```{r include=FALSE}
rm(ylim.corr, ylim.mae, ylim.mse, ylim.smse, ylim.smae, ylim.r2, plot_matrix,
   performance_308M_f.pat, performance_68M_f.pat, performance_308NoM_f.pat, 
   performance_68NoM_f.pat, performance_308M_f.hc, performance_68M_f.hc, 
   performance_308NoM_f.hc, performance_68NoM_f.hc, performance_308M_f, 
   performance_68M_f, performance_308NoM_f, performance_68NoM_f, 
   plot_performance_mean_sd)
```



# SPECIAL CASE 1:

# SCATTERPLOT 68NoM frontalpole & lateroccipital (7th FOLD)

## Data used to train and test this region/fold

```{r echo=FALSE}
plot_scatterplot_train_test_2reg <- function(df, measure, regs, f) {
  reg_names <- colnames(df%>%dplyr::select(ends_with(measure))) # Get the names of all the regions
  reg_names <- sub(measure, "",reg_names) # Delete termination to get a cleaner name
  new.colnames <- sub(measure, "",colnames(df)) 
  colnames(df) <- new.colnames
  
  # We separate data from healthy subjects and patients:
  df_hc  <- df[df[,"dcode"]==0, ] 
  df_pat <- df[df[,"dcode"]==1, ] 
  
  # We get the unique identifiers:
  ids_hc  <- unique(df_hc$subID)
  ids_pat <- unique(df_pat$subID)
  
  num_folds <- 10
  
  # we create 10 folds with the IDs:
  set.seed(123) # seed for replicability
  folds_hc <- createFolds(ids_hc, k=num_folds, list=TRUE, returnTrain=TRUE)
  set.seed(123) # seed for replicability
  folds_pat <- createFolds(ids_pat, k=num_folds, list=TRUE, returnTrain=TRUE)
  
  train_ids_hc <- ids_hc[folds_hc[[f]]]
  test_ids_hc  <- ids_hc[-folds_hc[[f]]]

  var_names <- c("age", "scode", "subID", "euler", "timepoint", "dcode")
  
  df <- df[ , c(reg_names[regs], var_names)] # df with only reg_names[regs]
  df$dcode <- factor(df$dcode)
  reg_names <- reg_names[regs]

  df  <- subset(df, dcode==0) # Only HC data, not patients
  train_df <- subset(df, subID%in%train_ids_hc)
  test_df  <- subset(df, subID%in%test_ids_hc)
  train_df$partition <- "train"
  test_df$partition <- "test"
  df <- combine(train_df, test_df)

  # GRAPHICdf, 
  reg1 <- ggplot(df, aes_string(x="age", y=reg_names[1], 
                                group= "subID", color="partition")) +
    geom_line()+
    geom_point() +
    labs(color = "Partition\n") +
    ggtitle(reg_names[1])+
    ylim(1.6, 4.2) +
    theme(panel.grid.major = element_blank(),
          panel.grid.minor = element_blank(),
          panel.background = element_blank(),
          axis.line    = element_line(colour = "black"),
          plot.title   = element_text(hjust = 0.5),
          axis.title.x = element_blank(),
          axis.title.y = element_blank()) +
    scale_fill_discrete(name = "Partition", 
                        labels = c("Train data", "Test data")) +
    scale_colour_manual(name = " ",
                        labels = c("Test data", "Train data"), 
                        values = c("#FF0000CC", "#0000FF40"))
    
    
  reg2 <- ggplot(df, aes_string(x="age", y=reg_names[2], 
                                group= "subID", color="partition")) +
    geom_line()+
    geom_point() +
    labs(color = "Partition\n") +
    ggtitle(reg_names[2])+
    ylim(1.6, 4.2) +
    theme(panel.grid.major = element_blank(),
          panel.grid.minor = element_blank(),
          panel.background = element_blank(),
          axis.line    = element_line(colour = "black"),
          plot.title   = element_text(hjust = 0.5),
          axis.title.x = element_blank(),
          axis.title.y = element_blank()) +
    scale_fill_discrete(name = "Partition", 
                        labels = c("Train data", "Test data")) +
    scale_colour_manual(name = " ",
                        labels = c("Test data", "Train data"), 
                        values = c("#FF0000CC", "#0000FF40"))
        
  # Test 440154FF ---> 440154CC
  # Train B8DE29FF --> B8DE2940
  # Adjust transparency in HEX colors:
  # adjustcolor("red", alpha.f = 0.8) # Test
  # adjustcolor("blue", alpha.f = 0.25) # Train

  
  figure <- ggarrange(reg1, reg2,
                      ncol = 2, nrow = 1,
                      legend = "right",
                      common.legend = TRUE)
  
  annotate_figure(figure,
                  left = text_grob("Cortical thickness (mm)",
                                   rot = 90),
                  bottom = text_grob("Age (years)"),
                  fig.lab.face = "bold",
                  top = text_grob("Train vs Test data\n", 
                                  face = "bold", size = 15, color = "black"))
}
```


```{r include=FALSE}
df_68  <- getData(parc = "68")
df <- DataPreparation(df = df_68,
                      parc = "68",
                      harmonization = T,
                      match = F)
measure <- "_CT_freesurfer"

reg_names  <- colnames(df%>%dplyr::select(ends_with(measure)))
reg1 <- which(reg_names=="lh_frontalpole_CT_freesurfer", arr.ind = FALSE, useNames = TRUE) # REG MAL
reg2 <- which(reg_names=="lh_lateraloccipital_CT_freesurfer", arr.ind = FALSE, useNames = TRUE) # REG BIEN

regs <- c(reg1, reg2) 
f <- 7
```

```{r echo=FALSE}
plot_scatterplot_train_test_2reg(df, measure, regs, f)
```


```{r eval=F, echo = FALSE}
# To get the MSE and MAE values from both regions
performance_68NoM_f  <- read.csv("/data_J/Results/Files/performance_68NoM_f.csv" )
df <- performance_68NoM_f[performance_68NoM_f[,"fold"]==7,]
df <- df[df[,"diagnose"]=="control",]

which(reg_names=="lh_frontalpole_CT_freesurfer", arr.ind = FALSE, useNames = TRUE) # REG MAL
which(reg_names=="lh_lateraloccipital_CT_freesurfer", arr.ind = FALSE, useNames = TRUE) # REG BIEN
```

```{r echo=F}
rm(df, measure, reg_names, reg1, reg2, regs, f)
```

## Target data vs predicted data 

```{r echo=FALSE}
plot_scatterplot_pred_target_2reg <- function(df_orig, df_predictions, measure, regs, f) {
  
  # DF_PREDICTIONS Change region names rh_temporalpole_CT_freesurfer -> rh_temporalpole
  reg_names <- df_predictions$region
  new_reg_names <- sub(measure, "",reg_names) # REG NAMES ONLY # Delete termination to get a cleaner name
  df_predictions$region <- new_reg_names # Rename all the columns

  # DF_ORIGIN Change region names rh_temporalpole_CT_freesurfer -> rh_temporalpole
  reg_names <- colnames(df_orig%>%dplyr::select(ends_with(measure))) # Get the names of all the regions
  reg_names <- sub(measure, "",reg_names) # REG NAMES ONLY # Delete termination to get a cleaner name
  new.colnames <- sub(measure, "", colnames(df_orig)) # ALL COLNAMES # Delete termination to get a cleaner name
  colnames(df_orig) <- new.colnames # Rename all the columns
  
  # We separate data from healthy subjects and patients:
  df_hc  <- df_orig[df_orig[,"dcode"]==0, ] 
  df_pat <- df_orig[df_orig[,"dcode"]==1, ] 
  
  # We get the unique identifiers of healthy subjects and patients:
  ids_hc  <- unique(df_hc$subID)
  ids_pat <- unique(df_pat$subID)
  
  # we create 10 folds with the IDs:
  num_folds <- 10
  set.seed(123) # seed for replicability
  folds_hc <- createFolds(ids_hc, k=num_folds, list=TRUE, returnTrain=TRUE)
  set.seed(123) # seed for replicability
  folds_pat <- createFolds(ids_pat, k=num_folds, list=TRUE, returnTrain=TRUE)
  
  # We get the subID of the train-test healthy subjects and controls in this fold f
  train_ids_hc <- ids_hc[folds_hc[[f]]]
  test_ids_hc  <- ids_hc[-folds_hc[[f]]]
  train_ids_pat <- ids_pat[folds_pat[[f]]]
  test_ids_pat  <- ids_pat[-folds_pat[[f]]]
  
  ##### UNTIL HERE CROSS-VAL SUBJECTS IDENTIFICATION #####

  # DF_ORIG
  var_names <- c("age", "scode", "subID", "euler", "timepoint", "dcode")
  reg_names <- reg_names[regs]
  df_orig <- df_orig[ , c(reg_names, var_names)] # df_orig with only relevant data
  
  # ONLY HEALTHY CONTROLS
  df_orig$dcode <- factor(df_orig$dcode)
  df_orig  <- subset(df_orig, dcode==0) 
  # SEPARATE TRAIN AND TEST HEALTHY CONTROLS DATA FROM FOLD F
  df_orig_test  <- subset(df_orig, subID%in%test_ids_hc)
  df_orig_test$partition  <- "test"
  
  # DF_PREDICTIONS
  df_predictions   <- subset(df_predictions, fold==f) 
  df_predictions1  <- subset(df_predictions, region==reg_names[1]) 
  df_predictions2  <- subset(df_predictions, region==reg_names[2]) 
  df_predictions_m <- rbind(df_predictions1, df_predictions2)
  df_predictions_test <- subset(df_predictions_m, subID%in%test_ids_hc)
  df_predictions_test <- df_predictions_test %>%
    select("region", "subID", "timepoint", "y_true", "y_pred")
  
  df_predictions_test <- reshape(df_predictions_test, 
                                 idvar = c("subID", "timepoint"), 
                                 timevar = "region", direction = "wide")

  df_merged <- merge(df_orig_test, df_predictions_test, by=c("subID","timepoint"))
  df_merged <- df_merged %>%
    select("age","subID","timepoint","y_true.lh_frontalpole", 
           "y_pred.lh_frontalpole", "y_true.lh_lateraloccipital", 
           "y_pred.lh_lateraloccipital")
  
  df_to_plot_reg_1 <- df_merged %>%
    select("age","subID","timepoint","y_true.lh_frontalpole","y_pred.lh_frontalpole") %>%
    dplyr::arrange(subID)
  
  reg1_name <- sub("y_pred.", "",colnames(df_to_plot_reg_1)[5]) # Get region name
  colnames(df_to_plot_reg_1) <- c("age","subID","timepoint","y_true","y_pred")
  
  df_to_plot_reg_2 <- df_merged %>%
  select("age","subID","timepoint", "y_true.lh_lateraloccipital", 
         "y_pred.lh_lateraloccipital") %>%
    dplyr::arrange(subID)
  
  reg2_name <- sub("y_pred.", "",colnames(df_to_plot_reg_2)[5]) # Get region name
  colnames(df_to_plot_reg_2) <- c("age","subID","timepoint","y_true","y_pred")

  
  ylim.min <- min(c(df_to_plot_reg_1$y_true, df_to_plot_reg_1$y_pred, 
                    df_to_plot_reg_2$y_true, df_to_plot_reg_2$y_pred))
  
  ylim.max <- max(c(df_to_plot_reg_1$y_true, df_to_plot_reg_1$y_pred, 
                    df_to_plot_reg_2$y_true, df_to_plot_reg_2$y_pred))
  
  # GRAPHICS
  reg1 <- ggplot(df_to_plot_reg_1) +
      # PREDICTIONS
      geom_line(aes(x=age, y=y_pred, group= subID, color= "y_pred"), alpha=0.4)+
      geom_point(aes(x=age, y=y_pred, group= subID, color="y_pred"), alpha=0.4)+
      geom_text(data = df_to_plot_reg_1[df_to_plot_reg_1$timepoint==1, ], 
              aes(x=age, y=y_pred, label=paste0(subID)), check_overlap = F, size= 3) +
      # TRUE VALUES
      geom_line(aes(x=age, y=y_true, group= subID, color= "y_true"), alpha=0.4)+
      geom_point(aes(x=age, y=y_true, group= subID, color="y_true"), alpha=0.4)+
      geom_text(data = df_to_plot_reg_1[df_to_plot_reg_1$timepoint==1, ], 
            aes(x=age, y=y_true, label=paste0(subID)),check_overlap = F, size= 3) +
      ggtitle(reg1_name)+
      ylim(ylim.min, ylim.max) +
      labs(color = "Partition\n") +
      theme(panel.grid.major = element_blank(),
            panel.grid.minor = element_blank(),
            panel.background = element_blank(),
            axis.line    = element_line(colour = "black"),
            plot.title   = element_text(hjust = 0.5),
            axis.title.x = element_blank(),
            axis.title.y = element_blank()) +
      scale_colour_manual(name = " ",
                          values = c("y_pred"="red", "y_true"="blue"),
                          labels = c("Predicted values", "Target values"))
    
  reg2 <- ggplot(df_to_plot_reg_2) +
      # PREDICTIONS
      geom_line(aes(x=age, y=y_pred, group= subID, color= "y_pred"), alpha=0.4)+
      geom_point(aes(x=age, y=y_pred, group= subID, color="y_pred"), alpha=0.4)+
      geom_text(data = df_to_plot_reg_2[df_to_plot_reg_2$timepoint==1, ], 
              aes(x=age, y=y_pred, label=paste0(subID)),check_overlap = F, size= 3) +
      # TRUE VALUES
      geom_line(aes(x=age, y=y_true, group= subID, color= "y_true"), alpha=0.4)+
      geom_point(aes(x=age, y=y_true, group= subID, color="y_true"), alpha=0.4)+
      geom_text(data = df_to_plot_reg_2[df_to_plot_reg_2$timepoint==1, ], 
          aes(x=age, y=y_true, label=paste0(subID)), check_overlap = F, size= 3) +
      ggtitle(reg2_name)+
      ylim(ylim.min, ylim.max) +
      labs(color = "Partition\n") +
      theme(panel.grid.major = element_blank(),
            panel.grid.minor = element_blank(),
            panel.background = element_blank(),
            axis.line    = element_line(colour = "black"),
            plot.title   = element_text(hjust = 0.5),
            axis.title.x = element_blank(),
            axis.title.y = element_blank()) +
      scale_colour_manual(name = " ",
                          values = c("y_pred"="red", "y_true"="blue"),
                          labels = c("Predicted values", "Target values"))
      
  figure <- ggarrange(reg1, reg2,
                      ncol = 2, nrow = 1,
                      legend = "right",
                      common.legend = TRUE)
  
  annotate_figure(figure,
                  left = text_grob("Cortical thickness (mm)",
                                   rot = 90),
                  bottom = text_grob("Age (years)"),
                  fig.lab.face = "bold",
                  top = text_grob("Target vs Predicted data\n", 
                                  face = "bold", size = 15, color = "black"))
}
```

```{r include=FALSE}
measure <- "_CT_freesurfer"
df <- DataPreparation(df = df_68,
                      parc = "68",
                      harmonization = T,
                      match = F)

reg_names  <- colnames(df%>%dplyr::select(ends_with(measure)))

reg1 <- which(reg_names=="lh_frontalpole_CT_freesurfer", arr.ind = FALSE, useNames = TRUE)
reg2 <- which(reg_names=="lh_lateraloccipital_CT_freesurfer", arr.ind = FALSE, useNames = TRUE) 
regs <- c(reg1, reg2) 

f <- 7
```


```{r echo=FALSE}
plot_scatterplot_pred_target_2reg(df, predictions_68NoM, measure, regs, f)
```
```{r echo=F}
rm(df, measure, reg_names, reg1, reg2, regs, f)
```

## Difference between target data vs predicted data 

```{r echo=FALSE}
plot_scatterplot_pred_target_diff_2reg <- function(df_orig, df_predictions, measure, regs, f) {
  
  # DF_PREDICTIONS Change region names rh_temporalpole_CT_freesurfer -> rh_temporalpole
  reg_names <- df_predictions$region
  new_reg_names <- sub(measure, "",reg_names) # REG NAMES ONLY # Delete termination to get a cleaner name
  df_predictions$region <- new_reg_names # Rename all the columns

  # DF_ORIGIN Change region names rh_temporalpole_CT_freesurfer -> rh_temporalpole
  reg_names <- colnames(df_orig%>%dplyr::select(ends_with(measure))) # Get the names of all the regions
  reg_names <- sub(measure, "",reg_names) # REG NAMES ONLY # Delete termination to get a cleaner name
  new.colnames <- sub(measure, "", colnames(df_orig)) # ALL COLNAMES # Delete termination to get a cleaner name
  colnames(df_orig) <- new.colnames # Rename all the columns
  
  # We separate data from healthy subjects and patients:
  df_hc  <- df_orig[df_orig[,"dcode"]==0, ] 
  df_pat <- df_orig[df_orig[,"dcode"]==1, ] 
  
  # We get the unique identifiers of healthy subjects and patients:
  ids_hc  <- unique(df_hc$subID)
  ids_pat <- unique(df_pat$subID)
  
  # we create 10 folds with the IDs:
  num_folds <- 10
  set.seed(123) # seed for replicability
  folds_hc <- createFolds(ids_hc, k=num_folds, list=TRUE, returnTrain=TRUE)
  set.seed(123) # seed for replicability
  folds_pat <- createFolds(ids_pat, k=num_folds, list=TRUE, returnTrain=TRUE)
  
  # We get the subID of the train-test healthy subjects and controls in this fold f
  train_ids_hc <- ids_hc[folds_hc[[f]]]
  test_ids_hc  <- ids_hc[-folds_hc[[f]]]
  train_ids_pat <- ids_pat[folds_pat[[f]]]
  test_ids_pat  <- ids_pat[-folds_pat[[f]]]
  
  ##### UNTIL HERE CROSS-VAL SUBJECTS IDENTIFICATION #####

  # DF_ORIG
  var_names <- c("age", "scode", "subID", "euler", "timepoint", "dcode")
  reg_names <- reg_names[regs]
  df_orig <- df_orig[ , c(reg_names, var_names)] # df_orig with only relevant data
  # ONLY HEALTHY CONTROLS
  df_orig$dcode <- factor(df_orig$dcode)
  df_orig  <- subset(df_orig, dcode==0) 
  # SEPARATE TRAIN AND TEST HEALTHY CONTROLS DATA FROM FOLD F
  df_orig_test  <- subset(df_orig, subID%in%test_ids_hc)
  df_orig_test$partition  <- "test"
  
  
  # DF_PREDICTIONS
  df_predictions   <- subset(df_predictions, fold==f) 
  df_predictions1  <- subset(df_predictions, region==reg_names[1]) 
  df_predictions2  <- subset(df_predictions, region==reg_names[2]) 
  df_predictions_m <- rbind(df_predictions1, df_predictions2)
  df_predictions_test <- subset(df_predictions_m, subID%in%test_ids_hc)
  df_predictions_test <- df_predictions_test %>%
    select("region", "subID", "timepoint", "y_true", "y_pred")
  
  df_predictions_test <- reshape(df_predictions_test, 
                                 idvar = c("subID", "timepoint"), 
                                 timevar = "region", direction = "wide")

  df_merged <- merge(df_orig_test, df_predictions_test, by=c("subID","timepoint"))
  df_merged <- df_merged %>%
    select("age","subID","timepoint","y_true.lh_frontalpole", 
           "y_pred.lh_frontalpole", "y_true.lh_lateraloccipital", 
           "y_pred.lh_lateraloccipital")
  
  df_to_plot_reg_1 <- df_merged %>%
    select("age","subID","timepoint","y_true.lh_frontalpole","y_pred.lh_frontalpole") %>%
    dplyr::arrange(subID)
  
  reg1_name <- sub("y_pred.", "",colnames(df_to_plot_reg_1)[5]) # Get region name
  colnames(df_to_plot_reg_1) <- c("age","subID","timepoint","y_true","y_pred")
  
  df_to_plot_reg_2 <- df_merged %>%
  select("age","subID","timepoint", "y_true.lh_lateraloccipital", 
         "y_pred.lh_lateraloccipital") %>%
    dplyr::arrange(subID)
  
  reg2_name <- sub("y_pred.", "",colnames(df_to_plot_reg_2)[5]) # Get region name
  colnames(df_to_plot_reg_2) <- c("age","subID","timepoint","y_true","y_pred")

  df_to_plot_reg_1 <- df_to_plot_reg_1 %>%
    mutate(diff=abs(y_true-y_pred))
  
  df_to_plot_reg_2 <- df_to_plot_reg_2 %>%
    mutate(diff=abs(y_true-y_pred))

  # GRAPHICS
  reg1 <- ggplot(df_to_plot_reg_1) +
      # PREDICTIONS
      geom_line(aes(x=age, y=diff, group= subID), alpha=0.4)+
      geom_point(aes(x=age, y=diff, group= subID), alpha=0.4)+
      geom_text(data = df_to_plot_reg_1[df_to_plot_reg_1$timepoint==1, ], 
              aes(x=age, y=diff, label=paste0(subID)), check_overlap = F, size= 3) +
      ggtitle(reg1_name)+
      ylim(0, 0.7) +
      theme(panel.grid.major = element_blank(),
            panel.grid.minor = element_blank(),
            panel.background = element_blank(),
            axis.line    = element_line(colour = "black"),
            plot.title   = element_text(hjust = 0.5),
            axis.title.x = element_blank(),
            axis.title.y = element_blank())
  reg2 <- ggplot(df_to_plot_reg_2) +
      # PREDICTIONS
      geom_line(aes(x=age, y=diff, group= subID), alpha=0.4)+
      geom_point(aes(x=age, y=diff, group= subID), alpha=0.4)+
      geom_text(data = df_to_plot_reg_2[df_to_plot_reg_2$timepoint==1, ], 
              aes(x=age, y=diff, label=paste0(subID)),check_overlap = F, size= 3) +
      ggtitle(reg2_name)+
      ylim(0, 0.7) +
      labs(color = "Partition\n") +
      theme(panel.grid.major = element_blank(),
            panel.grid.minor = element_blank(),
            panel.background = element_blank(),
            axis.line    = element_line(colour = "black"),
            plot.title   = element_text(hjust = 0.5),
            axis.title.x = element_blank(),
            axis.title.y = element_blank())
      
  figure <- ggarrange(reg1, reg2,
                      ncol = 2, nrow = 1,
                      legend = "right",
                      common.legend = TRUE)
  
  annotate_figure(figure,
                  left = text_grob("Cortical thickness (mm)",
                                   rot = 90),
                  bottom = text_grob("Age (years)"),
                  fig.lab.face = "bold",
                  top = text_grob("Difference between target and predicted data\n", 
                                  face = "bold", size = 15, color = "black"))
}
```


```{r include=FALSE}
measure <- "_CT_freesurfer"
df <- DataPreparation(df = df_68,
                      parc = "68",
                      harmonization = T,
                      match = F)

reg_names  <- colnames(df%>%dplyr::select(ends_with(measure)))
reg1 <- which(reg_names=="lh_frontalpole_CT_freesurfer", arr.ind = FALSE, useNames = TRUE)      # REG MAL
reg2 <- which(reg_names=="lh_lateraloccipital_CT_freesurfer", arr.ind = FALSE, useNames = TRUE) # REG BIEN
regs <- c(reg1, reg2) 

f <- 7
```

```{r echo=FALSE}
plot_scatterplot_pred_target_diff_2reg(df, predictions_68NoM, measure, regs, f)
```
```{r echo=F}
rm(df, measure, reg_names, reg1, reg2, regs, f, df_68)
```

## Ordered regions by decreasing MSE

```{r include=F}
performance_68NoM  <- read.csv("/data_J/Results/Files/performance_68NoM.csv" )

RegsByMSE <- performance_68NoM %>%
  dplyr::filter(diagnose=="control")%>%
  dplyr::select(region, diagnose, MSE)

measure <- "_CT_freesurfer"
df <- performance_68NoM
reg_names <- df$region # Get the names of all the regions
new_reg_names <- sub(measure, "", reg_names) # Delete termination to get a cleaner name
df$region <- new_reg_names # Get the names of all the regions
```

```{r echo=F}
df %>%
  filter(diagnose=="control")%>% # only CONTROLS
  arrange(MSE) %>%               # ORDER by increasing value
  mutate(region=factor(region, levels=region)) %>%   # This trick update the factor levels
  ggplot( aes(x=region, y=MSE)) +
    geom_segment(aes(xend=region, yend=0)) +
    geom_point(size=2, color="black") +
    coord_flip() +
    theme_bw() +
    xlab(" ") +
    ylab("MSE") +
  ggtitle("Ordered regions by decreasing MSE")+
  theme(panel.grid.major = element_blank(),
      panel.grid.minor = element_blank(),
      panel.background = element_blank(),
      axis.line    = element_line(colour = "black"),
      axis.text    = element_text(size=8),
      plot.title = element_text(size = 12),
      legend.title = element_blank()) 
```

```{r include=F}
rm(df, RegsByMSE, measure, new_reg_names, reg_names)
```


## Ordered regions by decreasing MAE

```{r include=F}
RegsByMAE <- performance_68NoM %>%
  dplyr::filter(diagnose=="control")%>%
  dplyr::select(region, diagnose, MAE)

measure <- "_CT_freesurfer"
df <- performance_68NoM
reg_names <- df$region # Get the names of all the regions
new_reg_names <- sub(measure, "", reg_names) # Delete termination to get a cleaner name
df$region <- new_reg_names # Get the names of all the regions
```

```{r echo=F}
df %>%
  filter(diagnose=="control")%>% # only CONTROLS
  arrange(MAE) %>%               # ORDER by increasing value
  mutate(region=factor(region, levels=region)) %>%   # This trick update the factor levels
  ggplot( aes(x=region, y=MAE)) +
    geom_segment(aes(xend=region, yend=0)) +
    geom_point(size=2, color="black") +
    coord_flip() +
    theme_bw() +
    xlab(" ") +
    ylab("MAE") +
  ggtitle("Ordered regions by decreasing MAE")+
  theme(panel.grid.major = element_blank(),
      panel.grid.minor = element_blank(),
      panel.background = element_blank(),
      axis.line    = element_line(colour = "black"),
      axis.text    = element_text(size=8),
      plot.title = element_text(size = 12),
      legend.title = element_blank()) 
```

```{r include=F}
rm(df, RegsByMAE, measure, new_reg_names, reg_names, performance_68NoM)
```


# SPECIAL CASE 2:

# SCATTERPLOT 7, 8 and 9th FOLD, 68NoM (rh_precentral)

## Data used to train and test this region/fold


```{r echo=FALSE}
plot_scatterplot_train_test_1reg <- function(df_orig, measure, reg, folds) {
  
  reg_names <- colnames(df_orig%>%dplyr::select(ends_with(measure))) # Get the names of all the regions
  reg_names_short <- sub(measure, "", reg_names) # Delete termination to get a cleaner name
  region <- reg_names[reg]
  region_short <- reg_names_short[reg]
  rm(reg_names, reg_names_short, reg, measure)
  
  # We separate data from healthy subjects and patients:
  df_hc  <- df_orig[df_orig[,"dcode"]==0, ] 
  df_pat <- df_orig[df_orig[,"dcode"]==1, ] 
  
  # We get the unique identifiers:
  ids_hc  <- unique(df_hc$subID)
  ids_pat <- unique(df_pat$subID)
  
  num_folds <- 10
  
  # we create 10 folds with the IDs:
  set.seed(123) # seed for replicability
  folds_hc <- createFolds(ids_hc, k=num_folds, list=TRUE, returnTrain=TRUE)
  set.seed(123) # seed for replicability
  folds_pat <- createFolds(ids_pat, k=num_folds, list=TRUE, returnTrain=TRUE)
  
  # FIRST FOLD (6th)
  f <- folds[1]
  train_ids_hc <- ids_hc[folds_hc[[f]]]
  test_ids_hc  <- ids_hc[-folds_hc[[f]]]
  var_names <- c("age", "scode", "subID", "euler", "timepoint", "dcode")
  df <- df_orig[ , c(region, var_names)] # df with only reg_names[regs]
  df$dcode <- factor(df$dcode)
  df  <- subset(df, dcode==0)
  train_df <- subset(df, subID%in%train_ids_hc)
  test_df  <- subset(df, subID%in%test_ids_hc)
  train_df$partition <- "train"
  test_df$partition <- "test"
  df <- combine(train_df, test_df)
  colnames(df) <- c(region_short, var_names, "partition")

  # GRAPHIC
  fold1 <- ggplot(df, aes_string(x="age", y=region_short, 
                                group= "subID", color="partition")) +
    geom_line(alpha = 0.5)+
    ggtitle(paste0("FOLD ",f))+
    geom_point(alpha = 0.5) +
    labs(color = "Partition\n", 
         y = "Cortical thickness (mm)",
         x = "Age (years)") +
    theme(panel.grid.major = element_blank(),
          panel.grid.minor = element_blank(),
          panel.background = element_blank(),
          axis.title.x = element_blank(),
          axis.title.y = element_blank(),
          axis.line    = element_line(colour = "black"),
          plot.title   = element_text(hjust = 0.5)) +
    scale_fill_discrete(name = "Partition", labels = c("Train", "Test")) +
    scale_colour_manual(name = " ", 
                        labels = c("Test", "Train"), 
                        values = c("#FF0000CC", "#0000FF40"))
  
  # SECOND FOLD (7th)
  f <- folds[2]
  train_ids_hc <- ids_hc[folds_hc[[f]]]
  test_ids_hc  <- ids_hc[-folds_hc[[f]]]
  var_names <- c("age", "scode", "subID", "euler", "timepoint", "dcode")
  df <- df_orig[ , c(region, var_names)] # df with only reg_names[regs]
  df$dcode <- factor(df$dcode)
  df  <- subset(df, dcode==0)
  train_df <- subset(df, subID%in%train_ids_hc)
  test_df  <- subset(df, subID%in%test_ids_hc)
  train_df$partition <- "train"
  test_df$partition <- "test"
  df <- combine(train_df, test_df)
  colnames(df) <- c(region_short, var_names, "partition")

  # GRAPHIC
  fold2 <- ggplot(df, aes_string(x="age", y=region_short, 
                                group= "subID", color="partition")) +
    geom_line(alpha = 0.5)+
    ggtitle(paste0("FOLD ",f))+
    geom_point(alpha = 0.5) +
    labs(color = "Partition\n", 
         y = "Cortical thickness (mm)",
         x = "Age (years)") +
    theme(panel.grid.major = element_blank(),
          panel.grid.minor = element_blank(),
          panel.background = element_blank(),
          axis.title.x = element_blank(),
          axis.title.y = element_blank(),
          axis.line    = element_line(colour = "black"),
          plot.title   = element_text(hjust = 0.5)) +
    scale_fill_discrete(name = "Partition", labels = c("Train", "Test")) +
    scale_colour_manual(name = " ", 
                        labels = c("Test", "Train"), 
                        values = c("#FF0000CC", "#0000FF40"))
  
  # THIRD FOLD (8th)
  f <- folds[3]
  train_ids_hc <- ids_hc[folds_hc[[f]]]
  test_ids_hc  <- ids_hc[-folds_hc[[f]]]
  var_names <- c("age", "scode", "subID", "euler", "timepoint", "dcode")
  df <- df_orig[ , c(region, var_names)] # df with only reg_names[regs]
  df$dcode <- factor(df$dcode)
  df  <- subset(df, dcode==0)
  train_df <- subset(df, subID%in%train_ids_hc)
  test_df  <- subset(df, subID%in%test_ids_hc)
  train_df$partition <- "train"
  test_df$partition <- "test"
  df <- combine(train_df, test_df)
  colnames(df) <- c(region_short, var_names, "partition")

  # GRAPHIC
  fold3 <- ggplot(df, aes_string(x="age", y=region_short, 
                                group= "subID", color="partition")) +
    geom_line(alpha = 0.5)+
    ggtitle(paste0("FOLD ",f))+
    geom_point(alpha = 0.5) +
    labs(color = "Partition\n", 
         y = "Cortical thickness (mm)",
         x = "Age (years)") +
    theme(panel.grid.major = element_blank(),
          panel.grid.minor = element_blank(),
          panel.background = element_blank(),
          axis.title.x = element_blank(),
          axis.title.y = element_blank(),
          axis.line    = element_line(colour = "black"),
          plot.title   = element_text(hjust = 0.5)) +
    scale_fill_discrete(name = "Partition", labels = c("Train", "Test")) +
    scale_colour_manual(name = " ", 
                        labels = c("Test", "Train"), 
                        values = c("#FF0000CC", "#0000FF40"))
  
  
  figure <- ggarrange(fold1, fold2, fold3,
                      ncol = 3, nrow = 1,
                      legend = "right",
                      common.legend = TRUE)
  
  annotate_figure(figure,
                  left = text_grob("Cortical thickness (mm)",
                                   rot = 90),
                  bottom = text_grob("Age (years)"),
                  fig.lab.face = "bold",
                  top = text_grob(paste0("Train vs Test data (",region_short,")"), 
                                  face = "bold", size = 15, color = "black"))
}
```


```{r include=FALSE}
df_68  <- getData(parc = "68")
df <- DataPreparation(df = df_68,
                      parc = "68",
                      harmonization = T,
                      match = F)
measure <- "_CT_freesurfer"
reg_names  <- colnames(df%>%dplyr::select(ends_with(measure)))
reg <- which(reg_names=="rh_precentral_CT_freesurfer", arr.ind = FALSE, useNames = TRUE)
folds <- c(6,7,8)

performance_68NoM_f <- read.csv("/data_J/Results/Files/performance_68NoM_f.csv")
values <- performance_68NoM_f[performance_68NoM_f[,"region"]=="rh_precentral_CT_freesurfer", ]
values <- values[values[,"diagnose"]=="control", c("SMSE", "SMAE","fold")]
```

```{r echo=FALSE}
plot_scatterplot_train_test_1reg(df, measure, reg, folds)
rm(df_68, reg_names, df, folds, measure, reg)
```

## Target data vs predicted data

```{r echo=FALSE}
plot_scatterplot_pred_target_1reg <- function(df_orig, df_predictions, measure, reg, f) {
  
  # DF_PREDICTIONS (Change region names) 
  # rh_precentral_CT_freesurfer -> rh_precentral
  reg_names <- df_predictions$region
  new_reg_names <- sub(measure, "",reg_names) # REG NAMES ONLY # Delete termination to get a cleaner name
  df_predictions$region <- new_reg_names # Rename all the columns

  # DF_ORIGIN (Change region names) 
  reg_names <- colnames(df_orig%>%dplyr::select(ends_with(measure))) # Get the names of all the regions
  reg_names <- sub(measure, "",reg_names) # REG NAMES ONLY # Delete termination to get a cleaner name
  region_short <- reg_names[reg]

  new.colnames <- sub(measure, "", colnames(df_orig)) # ALL COLNAMES # Delete termination to get a cleaner name
  colnames(df_orig) <- new.colnames # Rename all the columns
  
  # We separate data from healthy subjects and patients:
  df_hc  <- df_orig[df_orig[,"dcode"]==0, ] 
  df_pat <- df_orig[df_orig[,"dcode"]==1, ] 
  
  # We get the unique identifiers of healthy subjects and patients:
  ids_hc  <- unique(df_hc$subID)
  ids_pat <- unique(df_pat$subID)
  
  # we create 10 folds with the IDs:
  num_folds <- 10
  set.seed(123) # seed for replicability
  folds_hc <- createFolds(ids_hc, k=num_folds, list=TRUE, returnTrain=TRUE)
  set.seed(123) # seed for replicability
  folds_pat <- createFolds(ids_pat, k=num_folds, list=TRUE, returnTrain=TRUE)
  
  # DF_ORIG
  var_names <- c("age", "scode", "subID", "euler", "timepoint", "dcode")
  reg_name <- reg_names[reg]
  df_orig <- df_orig[ , c(reg_name, var_names)] # df_orig with only relevant data
  # ONLY HEALTHY CONTROLS
  df_orig$dcode <- factor(df_orig$dcode)
  df_orig  <- subset(df_orig, dcode==0) 

  ylim.min <- min(c(subset(subset(df_predictions, fold==folds[1]),region==reg_name)$y_pred,
                    subset(subset(df_predictions, fold==folds[2]),region==reg_name)$y_pred,
                    subset(subset(df_predictions, fold==folds[3]),region==reg_name)$y_pred,
                    subset(subset(df_predictions, fold==folds[1]),region==reg_name)$y_true,
                    subset(subset(df_predictions, fold==folds[2]),region==reg_name)$y_true,
                    subset(subset(df_predictions, fold==folds[3]),region==reg_name)$y_true))
  
  ylim.max <- max(c(subset(subset(df_predictions, fold==folds[1]),region==reg_name)$y_pred,
                    subset(subset(df_predictions, fold==folds[2]),region==reg_name)$y_pred,
                    subset(subset(df_predictions, fold==folds[3]),region==reg_name)$y_pred,
                    subset(subset(df_predictions, fold==folds[1]),region==reg_name)$y_true,
                    subset(subset(df_predictions, fold==folds[2]),region==reg_name)$y_true,
                    subset(subset(df_predictions, fold==folds[3]),region==reg_name)$y_true))
  
  
  # FIRST FOLD (fold 6th)
  f <- folds[1]
  # We get the subID of the train-test healthy subjects and controls in this fold f
  train_ids_hc <- ids_hc[folds_hc[[f]]]
  test_ids_hc  <- ids_hc[-folds_hc[[f]]]
  train_ids_pat <- ids_pat[folds_pat[[f]]]
  test_ids_pat  <- ids_pat[-folds_pat[[f]]]
  
  # SEPARATE TRAIN AND TEST HEALTHY CONTROLS DATA FROM FOLD F
  df_orig_test  <- subset(df_orig, subID%in%test_ids_hc)
  df_orig_test$partition  <- "test"
  
  # DF_PREDICTIONS
  df_predictions_plot  <- subset(df_predictions, fold==f) 
  df_predictions_plot  <- subset(df_predictions_plot, region==reg_name) 
  df_predictions_test <- subset(df_predictions_plot, subID%in%test_ids_hc)
  df_predictions_test <- df_predictions_test %>%
    select("region", "subID", "timepoint", "y_true", "y_pred")
  
  df_predictions_test <- reshape(df_predictions_test, 
                               idvar = c("subID", "timepoint"), 
                               timevar = "region", direction = "wide")
  
  df_merged <- merge(df_orig_test, df_predictions_test, by=c("subID","timepoint"))
  df_merged <- df_merged %>%
    select("age","subID","timepoint",paste0("y_true.", reg_name), 
           paste0("y_pred.", reg_name))
  
  df_to_plot <- df_merged %>%
    select("age","subID","timepoint", 
           paste0("y_true.", reg_name), 
           paste0("y_pred.", reg_name)) %>%
    dplyr::arrange(subID)
  
  colnames(df_to_plot) <- c("age","subID","timepoint","y_true","y_pred")
  
  # GRAPHICS
  fold1 <- ggplot(df_to_plot) +
      ggtitle(paste0("FOLD ",f))+
      # PREDICTIONS
      geom_line(aes(x=age, y=y_pred, group= subID, color= "y_pred"), alpha=0.4)+
      geom_point(aes(x=age, y=y_pred, group= subID, color="y_pred"), alpha=0.4)+
      geom_text(data = df_to_plot[df_to_plot$timepoint==1, ], 
              aes(x=age, y=y_pred, label=paste0(subID)), check_overlap = F, size= 3) +
      # TRUE VALUES
      geom_line(aes(x=age, y=y_true, group= subID, color= "y_true"), alpha=0.4)+
      geom_point(aes(x=age, y=y_true, group= subID, color="y_true"), alpha=0.4)+
      geom_text(data = df_to_plot[df_to_plot$timepoint==1, ], 
            aes(x=age, y=y_true, label=paste0(subID)),check_overlap = F, size= 3) +
      ylim(ylim.min, ylim.max) +
      labs(x = "Age (years)",
           y = "Cortical thickness (mm)") +
      theme(panel.grid.major = element_blank(),
            panel.grid.minor = element_blank(),
            panel.background = element_blank(),
            axis.title.x = element_blank(),
            axis.title.y = element_blank(),
            axis.line    = element_line(colour = "black"),
            plot.title   = element_text(hjust = 0.5)) +
      scale_colour_manual(name = " ",
                          values = c("y_pred"="red", "y_true"="blue"),
                          labels = c("Predicted values", "Target values"))

  
  
  
  # SECOND FOLD (fold 7th)
  f <- folds[2]
  # We get the subID of the train-test healthy subjects and controls in this fold f
  train_ids_hc <- ids_hc[folds_hc[[f]]]
  test_ids_hc  <- ids_hc[-folds_hc[[f]]]
  train_ids_pat <- ids_pat[folds_pat[[f]]]
  test_ids_pat  <- ids_pat[-folds_pat[[f]]]
  
  # SEPARATE TRAIN AND TEST HEALTHY CONTROLS DATA FROM FOLD F
  df_orig_test  <- subset(df_orig, subID%in%test_ids_hc)
  df_orig_test$partition  <- "test"
  
  # DF_PREDICTIONS
  df_predictions_plot  <- subset(df_predictions, fold==f) 
  df_predictions_plot  <- subset(df_predictions_plot, region==reg_name) 
  df_predictions_test <- subset(df_predictions_plot, subID%in%test_ids_hc)
  df_predictions_test <- df_predictions_test %>%
    select("region", "subID", "timepoint", "y_true", "y_pred")
  
  df_predictions_test <- reshape(df_predictions_test, 
                               idvar = c("subID", "timepoint"), 
                               timevar = "region", direction = "wide")
  
  df_merged <- merge(df_orig_test, df_predictions_test, by=c("subID","timepoint"))
  df_merged <- df_merged %>%
    select("age","subID","timepoint",paste0("y_true.", reg_name), 
           paste0("y_pred.", reg_name))
  
  df_to_plot <- df_merged %>%
    select("age","subID","timepoint", 
           paste0("y_true.", reg_name), 
           paste0("y_pred.", reg_name)) %>%
    dplyr::arrange(subID)
  
  colnames(df_to_plot) <- c("age","subID","timepoint","y_true","y_pred")
  
  # GRAPHICS
  fold2 <- ggplot(df_to_plot) +
      ggtitle(paste0("FOLD ",f))+
      # PREDICTIONS
      geom_line(aes(x=age, y=y_pred, group= subID, color= "y_pred"), alpha=0.4)+
      geom_point(aes(x=age, y=y_pred, group= subID, color="y_pred"), alpha=0.4)+
      geom_text(data = df_to_plot[df_to_plot$timepoint==1, ], 
              aes(x=age, y=y_pred, label=paste0(subID)), check_overlap = F, size= 3) +
      # TRUE VALUES
      geom_line(aes(x=age, y=y_true, group= subID, color= "y_true"), alpha=0.4)+
      geom_point(aes(x=age, y=y_true, group= subID, color="y_true"), alpha=0.4)+
      geom_text(data = df_to_plot[df_to_plot$timepoint==1, ], 
            aes(x=age, y=y_true, label=paste0(subID)),check_overlap = F, size= 3) +
      ylim(ylim.min, ylim.max) +
      labs(x = "Age (years)",
           y = "Cortical thickness (mm)") +
      theme(panel.grid.major = element_blank(),
            panel.grid.minor = element_blank(),
            panel.background = element_blank(),
            axis.title.x = element_blank(),
            axis.title.y = element_blank(),
            axis.line    = element_line(colour = "black"),
            plot.title   = element_text(hjust = 0.5)) +
      scale_colour_manual(name = " ",
                          values = c("y_pred"="red", "y_true"="blue"),
                          labels = c("Predicted values", "Target values"))
  
  
  
  # THIRD FOLD (fold 8th)
  f <- folds[3]
  # We get the subID of the train-test healthy subjects and controls in this fold f
  train_ids_hc <- ids_hc[folds_hc[[f]]]
  test_ids_hc  <- ids_hc[-folds_hc[[f]]]
  train_ids_pat <- ids_pat[folds_pat[[f]]]
  test_ids_pat  <- ids_pat[-folds_pat[[f]]]
  
  # SEPARATE TRAIN AND TEST HEALTHY CONTROLS DATA FROM FOLD F
  df_orig_test  <- subset(df_orig, subID%in%test_ids_hc)
  df_orig_test$partition  <- "test"
  
  # DF_PREDICTIONS
  df_predictions_plot  <- subset(df_predictions, fold==f) 
  df_predictions_plot  <- subset(df_predictions_plot, region==reg_name) 
  df_predictions_test <- subset(df_predictions_plot, subID%in%test_ids_hc)
  df_predictions_test <- df_predictions_test %>%
    select("region", "subID", "timepoint", "y_true", "y_pred")
  
  df_predictions_test <- reshape(df_predictions_test, 
                               idvar = c("subID", "timepoint"), 
                               timevar = "region", direction = "wide")
  
  df_merged <- merge(df_orig_test, df_predictions_test, by=c("subID","timepoint"))
  df_merged <- df_merged %>%
    select("age","subID","timepoint",paste0("y_true.", reg_name), 
           paste0("y_pred.", reg_name))
  
  df_to_plot <- df_merged %>%
    select("age","subID","timepoint", 
           paste0("y_true.", reg_name), 
           paste0("y_pred.", reg_name)) %>%
    dplyr::arrange(subID)
  
  colnames(df_to_plot) <- c("age","subID","timepoint","y_true","y_pred")
  
  # GRAPHICS
  fold3 <- ggplot(df_to_plot) +
      ggtitle(paste0("FOLD ",f))+
      # PREDICTIONS
      geom_line(aes(x=age, y=y_pred, group= subID, color= "y_pred"), alpha=0.4)+
      geom_point(aes(x=age, y=y_pred, group= subID, color="y_pred"), alpha=0.4)+
      geom_text(data = df_to_plot[df_to_plot$timepoint==1, ], 
              aes(x=age, y=y_pred, label=paste0(subID)), check_overlap = F, size= 3) +
      # TRUE VALUES
      geom_line(aes(x=age, y=y_true, group= subID, color= "y_true"), alpha=0.4)+
      geom_point(aes(x=age, y=y_true, group= subID, color="y_true"), alpha=0.4)+
      geom_text(data = df_to_plot[df_to_plot$timepoint==1, ], 
            aes(x=age, y=y_true, label=paste0(subID)),check_overlap = F, size= 3) +
      ylim(ylim.min, ylim.max) +
      labs(x = "Age (years)",
           y = "Cortical thickness (mm)") +
      theme(panel.grid.major = element_blank(),
            panel.grid.minor = element_blank(),
            panel.background = element_blank(),
            axis.title.x = element_blank(),
            axis.title.y = element_blank(),
            axis.line    = element_line(colour = "black"),
            plot.title   = element_text(hjust = 0.5)) +
      scale_colour_manual(name = " ",
                          values = c("y_pred"="red", "y_true"="blue"),
                          labels = c("Predicted values", "Target values"))

  figure <- ggarrange(fold1, fold2, fold3,
                      ncol = 3, nrow = 1,
                      legend = "right",
                      common.legend = TRUE)
  
  annotate_figure(figure,
                  left = text_grob("Cortical thickness (mm)",
                                   rot = 90),
                  bottom = text_grob("Age (years)"),
                  fig.lab.face = "bold",
                  top = text_grob(paste0("Target vs Predicted data (",region_short,")"), 
                                  face = "bold", size = 15, color = "black"))
}
```


```{r include=FALSE}
df_68  <- getData(parc = "68")

df <- DataPreparation(df = df_68,
                      parc = "68",
                      harmonization = T,
                      match = F)
measure <- "_CT_freesurfer"

reg_names  <- colnames(df%>%dplyr::select(ends_with(measure)))
reg <- which(reg_names=="rh_precentral_CT_freesurfer",arr.ind = FALSE, useNames = TRUE) 
folds <- c(6,7,8)
```


```{r echo=FALSE}
plot_scatterplot_pred_target_1reg(df, predictions_68NoM, measure, reg, folds)
rm(folds, reg_names, reg, measure, df, df_68)
```


## Difference between target data vs predicted data 

```{r echo=FALSE}
plot_scatterplot_pred_target_diff_1reg <- function(df_orig, df_predictions, measure, reg, folds) {
  
  # DF_PREDICTIONS (Change region names)
  # rh_precentral_CT_freesurfer -> rh_precentral
  reg_names <- df_predictions$region
  new_reg_names <- sub(measure, "",reg_names) # REG NAMES ONLY # Delete termination to get a cleaner name
  df_predictions$region <- new_reg_names # Rename all the columns

  # DF_ORIGIN (Change region names) 
  reg_names <- colnames(df_orig%>%dplyr::select(ends_with(measure))) # Get the names of all the regions
  reg_names <- sub(measure, "",reg_names) # REG NAMES ONLY # Delete termination to get a cleaner name
  region_short <- reg_names[reg]
  new.colnames <- sub(measure, "", colnames(df_orig)) # ALL COLNAMES # Delete termination to get a cleaner name
  colnames(df_orig) <- new.colnames # Rename all the columns
  
  # We separate data from healthy subjects and patients:
  df_hc  <- df_orig[df_orig[,"dcode"]==0, ] 
  df_pat <- df_orig[df_orig[,"dcode"]==1, ] 
  
  # We get the unique identifiers of healthy subjects and patients:
  ids_hc  <- unique(df_hc$subID)
  ids_pat <- unique(df_pat$subID)
  
  # we create 10 folds with the IDs:
  num_folds <- 10
  set.seed(123) # seed for replicability
  folds_hc <- createFolds(ids_hc, k=num_folds, list=TRUE, returnTrain=TRUE)
  set.seed(123) # seed for replicability
  folds_pat <- createFolds(ids_pat, k=num_folds, list=TRUE, returnTrain=TRUE)
  
  # DF_ORIG
  var_names <- c("age", "scode", "subID", "euler", "timepoint", "dcode")
  reg_name <- reg_names[reg]
  df_orig <- df_orig[ , c(reg_name, var_names)] # df_orig with only relevant data
  # ONLY HEALTHY CONTROLS
  df_orig$dcode <- factor(df_orig$dcode)
  df_orig  <- subset(df_orig, dcode==0) 

  ylim.min <- min(c(subset(subset(df_predictions, fold==folds[1]),region==reg_name)$y_pred,
                    subset(subset(df_predictions, fold==folds[2]),region==reg_name)$y_pred,
                    subset(subset(df_predictions, fold==folds[3]),region==reg_name)$y_pred,
                    subset(subset(df_predictions, fold==folds[1]),region==reg_name)$y_true,
                    subset(subset(df_predictions, fold==folds[2]),region==reg_name)$y_true,
                    subset(subset(df_predictions, fold==folds[3]),region==reg_name)$y_true))
  
  ylim.max <- max(c(subset(subset(df_predictions, fold==folds[1]),region==reg_name)$y_pred,
                    subset(subset(df_predictions, fold==folds[2]),region==reg_name)$y_pred,
                    subset(subset(df_predictions, fold==folds[3]),region==reg_name)$y_pred,
                    subset(subset(df_predictions, fold==folds[1]),region==reg_name)$y_true,
                    subset(subset(df_predictions, fold==folds[2]),region==reg_name)$y_true,
                    subset(subset(df_predictions, fold==folds[3]),region==reg_name)$y_true))
  
  # FIRST FOLD (fold 6th)
  f <- folds[1]
  # We get the subID of the train-test healthy subjects and controls in this fold f
  train_ids_hc <- ids_hc[folds_hc[[f]]]
  test_ids_hc  <- ids_hc[-folds_hc[[f]]]
  train_ids_pat <- ids_pat[folds_pat[[f]]]
  test_ids_pat  <- ids_pat[-folds_pat[[f]]]
  
  # SEPARATE TRAIN AND TEST HEALTHY CONTROLS DATA FROM FOLD F
  df_orig_test  <- subset(df_orig, subID%in%test_ids_hc)
  df_orig_test$partition  <- "test"
  
  # DF_PREDICTIONS
  df_predictions_plot  <- subset(df_predictions, fold==f) 
  df_predictions_plot  <- subset(df_predictions_plot, region==reg_name) 
  df_predictions_test <- subset(df_predictions_plot, subID%in%test_ids_hc)
  df_predictions_test <- df_predictions_test %>%
    select("region", "subID", "timepoint", "y_true", "y_pred")
  
  df_predictions_test <- reshape(df_predictions_test, 
                               idvar = c("subID", "timepoint"), 
                               timevar = "region", direction = "wide")

  df_merged <- merge(df_orig_test, df_predictions_test, by=c("subID","timepoint"))
  df_merged <- df_merged %>%
    select("age","subID","timepoint",paste0("y_true.", reg_name), 
           paste0("y_pred.", reg_name))
  
  df_to_plot <- df_merged %>%
    select("age","subID","timepoint", 
           paste0("y_true.", reg_name), 
           paste0("y_pred.", reg_name)) %>%
    dplyr::arrange(subID)

  colnames(df_to_plot) <- c("age","subID","timepoint","y_true","y_pred")
  df_to_plot <- df_to_plot %>%
    mutate(diff=abs(y_true-y_pred))

  # GRAPHICS
  fold1 <- ggplot(df_to_plot) +
      ggtitle(paste0("FOLD ",f))+
      # PREDICTIONS
      geom_line(aes(x=age, y=diff, group= subID), alpha=0.4)+
      geom_point(aes(x=age, y=diff, group= subID), alpha=0.4)+
      geom_text(data = df_to_plot[df_to_plot$timepoint==1, ], 
              aes(x=age, y=diff, label=paste0(subID)), check_overlap = F, size= 3) +
      ylim(0, 0.4) +
      labs(x = "Age (years)",
           y = "Cortical thickness (mm)") +
      theme(panel.grid.major = element_blank(),
            panel.grid.minor = element_blank(),
            panel.background = element_blank(),
            axis.title.x = element_blank(),
            axis.title.y = element_blank(),
            axis.line    = element_line(colour = "black"),
            plot.title   = element_text(hjust = 0.5)) +
      scale_colour_manual(name = " ",
                          values = c("y_pred"="red", "y_true"="blue"),
                          labels = c("Predicted values", "Target values"))
  
  # SECOND FOLD (fold 7th)
  f <- folds[2]
  # We get the subID of the train-test healthy subjects and controls in this fold f
  train_ids_hc <- ids_hc[folds_hc[[f]]]
  test_ids_hc  <- ids_hc[-folds_hc[[f]]]
  train_ids_pat <- ids_pat[folds_pat[[f]]]
  test_ids_pat  <- ids_pat[-folds_pat[[f]]]
  
  # SEPARATE TRAIN AND TEST HEALTHY CONTROLS DATA FROM FOLD F
  df_orig_test  <- subset(df_orig, subID%in%test_ids_hc)
  df_orig_test$partition  <- "test"
  
  # DF_PREDICTIONS
  df_predictions_plot  <- subset(df_predictions, fold==f) 
  df_predictions_plot  <- subset(df_predictions_plot, region==reg_name) 
  df_predictions_test <- subset(df_predictions_plot, subID%in%test_ids_hc)
  df_predictions_test <- df_predictions_test %>%
    select("region", "subID", "timepoint", "y_true", "y_pred")
  
  df_predictions_test <- reshape(df_predictions_test, 
                               idvar = c("subID", "timepoint"), 
                               timevar = "region", direction = "wide")

  df_merged <- merge(df_orig_test, df_predictions_test, by=c("subID","timepoint"))
  df_merged <- df_merged %>%
    select("age","subID","timepoint",paste0("y_true.", reg_name), 
           paste0("y_pred.", reg_name))
  
  df_to_plot <- df_merged %>%
    select("age","subID","timepoint", 
           paste0("y_true.", reg_name), 
           paste0("y_pred.", reg_name)) %>%
    dplyr::arrange(subID)

  colnames(df_to_plot) <- c("age","subID","timepoint","y_true","y_pred")
  df_to_plot <- df_to_plot %>%
    mutate(diff=abs(y_true-y_pred))

  # GRAPHICS
  fold2 <- ggplot(df_to_plot) +
      ggtitle(paste0("FOLD ",f))+
      # PREDICTIONS
      geom_line(aes(x=age, y=diff, group= subID), alpha=0.4)+
      geom_point(aes(x=age, y=diff, group= subID), alpha=0.4)+
      geom_text(data = df_to_plot[df_to_plot$timepoint==1, ], 
              aes(x=age, y=diff, label=paste0(subID)), check_overlap = F, size= 3) +
      ylim(0, 0.4) +
      labs(x = "Age (years)",
           y = "Cortical thickness (mm)") +
      theme(panel.grid.major = element_blank(),
            panel.grid.minor = element_blank(),
            panel.background = element_blank(),
            axis.title.x = element_blank(),
            axis.title.y = element_blank(),
            axis.line    = element_line(colour = "black"),
            plot.title   = element_text(hjust = 0.5)) +
      scale_colour_manual(name = " ",
                          values = c("y_pred"="red", "y_true"="blue"),
                          labels = c("Predicted values", "Target values"))
  
  # THIRD FOLD (fold 8th)
  f <- folds[3]
  # We get the subID of the train-test healthy subjects and controls in this fold f
  train_ids_hc <- ids_hc[folds_hc[[f]]]
  test_ids_hc  <- ids_hc[-folds_hc[[f]]]
  train_ids_pat <- ids_pat[folds_pat[[f]]]
  test_ids_pat  <- ids_pat[-folds_pat[[f]]]
  
  # SEPARATE TRAIN AND TEST HEALTHY CONTROLS DATA FROM FOLD F
  df_orig_test  <- subset(df_orig, subID%in%test_ids_hc)
  df_orig_test$partition  <- "test"
  
  # DF_PREDICTIONS
  df_predictions_plot  <- subset(df_predictions, fold==f) 
  df_predictions_plot  <- subset(df_predictions_plot, region==reg_name) 
  df_predictions_test <- subset(df_predictions_plot, subID%in%test_ids_hc)
  df_predictions_test <- df_predictions_test %>%
    select("region", "subID", "timepoint", "y_true", "y_pred")
  
  df_predictions_test <- reshape(df_predictions_test, 
                               idvar = c("subID", "timepoint"), 
                               timevar = "region", direction = "wide")

  df_merged <- merge(df_orig_test, df_predictions_test, by=c("subID","timepoint"))
  df_merged <- df_merged %>%
    select("age","subID","timepoint",paste0("y_true.", reg_name), 
           paste0("y_pred.", reg_name))
  
  df_to_plot <- df_merged %>%
    select("age","subID","timepoint", 
           paste0("y_true.", reg_name), 
           paste0("y_pred.", reg_name)) %>%
    dplyr::arrange(subID)

  colnames(df_to_plot) <- c("age","subID","timepoint","y_true","y_pred")
  df_to_plot <- df_to_plot %>%
    mutate(diff=abs(y_true-y_pred))

  # GRAPHICS
  fold3 <- ggplot(df_to_plot) +
      ggtitle(paste0("FOLD ",f))+
      # PREDICTIONS
      geom_line(aes(x=age, y=diff, group= subID), alpha=0.4)+
      geom_point(aes(x=age, y=diff, group= subID), alpha=0.4)+
      geom_text(data = df_to_plot[df_to_plot$timepoint==1, ], 
              aes(x=age, y=diff, label=paste0(subID)), check_overlap = F, size= 3) +
      ylim(0, 0.4) +
      labs(x = "Age (years)",
           y = "Cortical thickness (mm)") +
      theme(panel.grid.major = element_blank(),
            panel.grid.minor = element_blank(),
            panel.background = element_blank(),
            axis.title.x = element_blank(),
            axis.title.y = element_blank(),
            axis.line    = element_line(colour = "black"),
            plot.title   = element_text(hjust = 0.5)) +
      scale_colour_manual(name = " ",
                          values = c("y_pred"="red", "y_true"="blue"),
                          labels = c("Predicted values", "Target values"))

  figure <- ggarrange(fold1, fold2, fold3,
                      ncol = 3, nrow = 1,
                      legend = "right",
                      common.legend = TRUE)
  
  annotate_figure(figure,
                  left = text_grob("Cortical thickness (mm)",
                                   rot = 90),
                  bottom = text_grob("Age (years)"),
                  fig.lab.face = "bold",
                  top = text_grob(paste0("Difference between target and predicted data (",
                                         region_short,")"), 
                                  face = "bold", size = 15, color = "black"))
}
```


```{r include=FALSE}
df_68  <- getData(parc = "68")
df <- DataPreparation(df = df_68,
                      parc = "68",
                      harmonization = T,
                      match = F)
measure <- "_CT_freesurfer"
reg_names  <- colnames(df%>%dplyr::select(ends_with(measure)))
reg <- which(reg_names=="rh_precentral_CT_freesurfer",arr.ind = FALSE, useNames = TRUE) 
folds <- c(6,7,8)
```


```{r echo=FALSE}
plot_scatterplot_pred_target_diff_1reg(df, predictions_68NoM, measure, reg, folds)
rm(folds, reg_names, reg, measure, df, df_68)
```



# SPECIAL CASE 3:

# SCATTERPLOT 8, 9 and 10th FOLD (308M): rh_postcentral_part1

## Data used to train and test this region/fold

```{r echo=FALSE}
plot_scatterplot_train_test_2reg <- function(df, measure, regs, f) {
  reg_names <- colnames(df%>%dplyr::select(ends_with(measure))) # Get the names of all the regions
  reg_names <- sub(measure, "",reg_names) # Delete termination to get a cleaner name
  new.colnames <- sub(measure, "",colnames(df)) 
  colnames(df) <- new.colnames
  
  # We separate data from healthy subjects and patients:
  df_hc  <- df[df[,"dcode"]==0, ] 
  df_pat <- df[df[,"dcode"]==1, ] 
  
  # We get the unique identifiers:
  ids_hc  <- unique(df_hc$subID)
  ids_pat <- unique(df_pat$subID)
  
  num_folds <- 10
  
  # we create 10 folds with the IDs:
  set.seed(123) # seed for replicability
  folds_hc <- createFolds(ids_hc, k=num_folds, list=TRUE, returnTrain=TRUE)
  set.seed(123) # seed for replicability
  folds_pat <- createFolds(ids_pat, k=num_folds, list=TRUE, returnTrain=TRUE)
  
  train_ids_hc <- ids_hc[folds_hc[[f]]]
  test_ids_hc  <- ids_hc[-folds_hc[[f]]]

  var_names <- c("age", "scode", "subID", "euler", "timepoint", "dcode")
  
  df <- df[ , c(reg_names[regs], var_names)] # df with only reg_names[regs]
  df$dcode <- factor(df$dcode)
  reg_names <- reg_names[regs]

  df  <- subset(df, dcode==0) # Only HC data, not patients
  train_df <- subset(df, subID%in%train_ids_hc)
  test_df  <- subset(df, subID%in%test_ids_hc)
  train_df$partition <- "train"
  test_df$partition <- "test"
  df <- combine(train_df, test_df)

  # GRAPHICdf, 
  reg1 <- ggplot(df, aes_string(x="age", y=reg_names[1], 
                                group= "subID", color="partition")) +
    geom_line()+
    geom_point() +
    labs(color = "Partition\n") +
    ggtitle(reg_names[1])+
    ylim(1.2, 3.5) +
    theme(panel.grid.major = element_blank(),
          panel.grid.minor = element_blank(),
          panel.background = element_blank(),
          axis.line    = element_line(colour = "black"),
          plot.title   = element_text(hjust = 0.5),
          axis.title.x = element_blank(),
          axis.title.y = element_blank()) +
    scale_fill_discrete(name = "Partition", 
                        labels = c("Train data", "Test data")) +
    scale_colour_manual(name = " ",
                        labels = c("Test data", "Train data"), 
                        values = c("#FF0000CC", "#0000FF40"))
    
    
  reg2 <- ggplot(df, aes_string(x="age", y=reg_names[2], 
                                group= "subID", color="partition")) +
    geom_line()+
    geom_point() +
    labs(color = "Partition\n") +
    ggtitle(reg_names[2])+
    ylim(1.2, 3.5) +
    theme(panel.grid.major = element_blank(),
          panel.grid.minor = element_blank(),
          panel.background = element_blank(),
          axis.line    = element_line(colour = "black"),
          plot.title   = element_text(hjust = 0.5),
          axis.title.x = element_blank(),
          axis.title.y = element_blank()) +
    scale_fill_discrete(name = "Partition", 
                        labels = c("Train data", "Test data")) +
    scale_colour_manual(name = " ",
                        labels = c("Test data", "Train data"), 
                        values = c("#FF0000CC", "#0000FF40"))
        
  # Test 440154FF ---> 440154CC
  # Train B8DE29FF --> B8DE2940
  # Adjust transparency in HEX colors:
  # adjustcolor("red", alpha.f = 0.8) # Test
  # adjustcolor("blue", alpha.f = 0.25) # Train

  
  figure <- ggarrange(reg1, reg2,
                      ncol = 2, nrow = 1,
                      legend = "right",
                      common.legend = TRUE)
  
  annotate_figure(figure,
                  left = text_grob("Cortical thickness (mm)",
                                   rot = 90),
                  bottom = text_grob("Age (years)"),
                  fig.lab.face = "bold",
                  top = text_grob("Train vs Test data\n", 
                                  face = "bold", size = 15, color = "black"))
}
```

```{r include=FALSE}
df_308  <- getData(parc = "308")
df <- DataPreparation(df = df_308,
                      parc = "308",
                      harmonization = T,
                      match = T)
measure <- "_thickness"
performance_308M_f <- read.csv("/data_J/Results/Files/performance_308M_f.csv")
# performance_308M_f <- performance_308M_f[performance_308M_f[,"fold"]==9, ]

reg_names  <- colnames(df%>%dplyr::select(ends_with(measure)))
reg <- which(reg_names=="rh_postcentral_part1_thickness", arr.ind = FALSE, useNames = TRUE) # Reg mal
regs <- c(reg, reg+1)

folds <- c(8, 9, 10)
f <- 9
```

```{r echo=FALSE, warning=FALSE}
plot_scatterplot_train_test_1reg(df, measure, reg, folds)
plot_scatterplot_train_test_2reg(df, measure, regs, f)
```


## Target data vs predicted data

```{r echo=FALSE}
plot_scatterplot_pred_target_2reg <- function(df_orig, df_predictions, measure, regs, f) {
  
  # DF_PREDICTIONS Change region names rh_temporalpole_CT_freesurfer -> rh_temporalpole
  reg_names <- df_predictions$region
  new_reg_names <- sub(measure, "",reg_names) # REG NAMES ONLY # Delete termination to get a cleaner name
  df_predictions$region <- new_reg_names # Rename all the columns

  # DF_ORIGIN Change region names rh_temporalpole_CT_freesurfer -> rh_temporalpole
  reg_names <- colnames(df_orig%>%dplyr::select(ends_with(measure))) # Get the names of all the regions
  reg_names <- sub(measure, "",reg_names) # REG NAMES ONLY # Delete termination to get a cleaner name
  new.colnames <- sub(measure, "", colnames(df_orig)) # ALL COLNAMES # Delete termination to get a cleaner name
  colnames(df_orig) <- new.colnames # Rename all the columns
  
  # We separate data from healthy subjects and patients:
  df_hc  <- df_orig[df_orig[,"dcode"]==0, ] 
  df_pat <- df_orig[df_orig[,"dcode"]==1, ] 
  
  # We get the unique identifiers of healthy subjects and patients:
  ids_hc  <- unique(df_hc$subID)
  ids_pat <- unique(df_pat$subID)
  
  # we create 10 folds with the IDs:
  num_folds <- 10
  set.seed(123) # seed for replicability
  folds_hc <- createFolds(ids_hc, k=num_folds, list=TRUE, returnTrain=TRUE)
  set.seed(123) # seed for replicability
  folds_pat <- createFolds(ids_pat, k=num_folds, list=TRUE, returnTrain=TRUE)
  
  # We get the subID of the train-test healthy subjects and controls in this fold f
  train_ids_hc <- ids_hc[folds_hc[[f]]]
  test_ids_hc  <- ids_hc[-folds_hc[[f]]]
  train_ids_pat <- ids_pat[folds_pat[[f]]]
  test_ids_pat  <- ids_pat[-folds_pat[[f]]]
  
  ##### UNTIL HERE CROSS-VAL SUBJECTS IDENTIFICATION #####

  # DF_ORIG
  var_names <- c("age", "scode", "subID", "euler", "timepoint", "dcode")
  reg_names <- reg_names[regs]
  df_orig <- df_orig[ , c(reg_names, var_names)] # df_orig with only relevant data
  
  # ONLY HEALTHY CONTROLS
  df_orig$dcode <- factor(df_orig$dcode)
  df_orig  <- subset(df_orig, dcode==0) 
  # SEPARATE TRAIN AND TEST HEALTHY CONTROLS DATA FROM FOLD F
  df_orig_test  <- subset(df_orig, subID%in%test_ids_hc)
  df_orig_test$partition  <- "test"
  
  # DF_PREDICTIONS
  df_predictions   <- subset(df_predictions, fold==f) 
  df_predictions1  <- subset(df_predictions, region==reg_names[1]) 
  df_predictions2  <- subset(df_predictions, region==reg_names[2]) 
  df_predictions_m <- rbind(df_predictions1, df_predictions2)
  df_predictions_test <- subset(df_predictions_m, subID%in%test_ids_hc)
  df_predictions_test <- df_predictions_test %>%
    select("region", "subID", "timepoint", "y_true", "y_pred")
  
  df_predictions_test <- reshape(df_predictions_test, 
                                 idvar = c("subID", "timepoint"), 
                                 timevar = "region", direction = "wide")

  df_merged <- merge(df_orig_test, df_predictions_test, by=c("subID","timepoint"))
  df_merged <- df_merged %>%
    select("age","subID","timepoint","y_true.rh_postcentral_part1", 
           "y_pred.rh_postcentral_part1", "y_true.rh_postcentral_part2", 
           "y_pred.rh_postcentral_part2")

  df_to_plot_reg_1 <- df_merged %>%
    select("age","subID","timepoint",
           "y_true.rh_postcentral_part1",
           "y_pred.rh_postcentral_part1") %>%
    dplyr::arrange(subID)
  
  reg1_name <- sub("y_pred.", "",colnames(df_to_plot_reg_1)[5]) # Get region name
  colnames(df_to_plot_reg_1) <- c("age","subID","timepoint","y_true","y_pred")
  
  df_to_plot_reg_2 <- df_merged %>%
  select("age","subID","timepoint", 
           "y_true.rh_postcentral_part2",
           "y_pred.rh_postcentral_part2") %>%
    dplyr::arrange(subID)
  
  reg2_name <- sub("y_pred.", "",colnames(df_to_plot_reg_2)[5]) # Get region name
  colnames(df_to_plot_reg_2) <- c("age","subID","timepoint","y_true","y_pred")

  
  ylim.min <- min(c(df_to_plot_reg_1$y_true, df_to_plot_reg_1$y_pred, 
                    df_to_plot_reg_2$y_true, df_to_plot_reg_2$y_pred))
  
  ylim.max <- max(c(df_to_plot_reg_1$y_true, df_to_plot_reg_1$y_pred, 
                    df_to_plot_reg_2$y_true, df_to_plot_reg_2$y_pred))
  
  # GRAPHICS
  reg1 <- ggplot(df_to_plot_reg_1) +
      # PREDICTIONS
      geom_line(aes(x=age, y=y_pred, group= subID, color= "y_pred"), alpha=0.4)+
      geom_point(aes(x=age, y=y_pred, group= subID, color="y_pred"), alpha=0.4)+
      geom_text(data = df_to_plot_reg_1[df_to_plot_reg_1$timepoint==1, ], 
              aes(x=age, y=y_pred, label=paste0(subID)), check_overlap = F, size= 3) +
      # TRUE VALUES
      geom_line(aes(x=age, y=y_true, group= subID, color= "y_true"), alpha=0.4)+
      geom_point(aes(x=age, y=y_true, group= subID, color="y_true"), alpha=0.4)+
      geom_text(data = df_to_plot_reg_1[df_to_plot_reg_1$timepoint==1, ], 
            aes(x=age, y=y_true, label=paste0(subID)),check_overlap = F, size= 3) +
      ggtitle(reg1_name)+
      ylim(ylim.min, ylim.max) +
      labs(color = "Partition\n") +
      theme(panel.grid.major = element_blank(),
            panel.grid.minor = element_blank(),
            panel.background = element_blank(),
            axis.line    = element_line(colour = "black"),
            plot.title   = element_text(hjust = 0.5),
            axis.title.x = element_blank(),
            axis.title.y = element_blank()) +
      scale_colour_manual(name = " ",
                          values = c("y_pred"="red", "y_true"="blue"),
                          labels = c("Predicted values", "Target values"))
    
  reg2 <- ggplot(df_to_plot_reg_2) +
      # PREDICTIONS
      geom_line(aes(x=age, y=y_pred, group= subID, color= "y_pred"), alpha=0.4)+
      geom_point(aes(x=age, y=y_pred, group= subID, color="y_pred"), alpha=0.4)+
      geom_text(data = df_to_plot_reg_2[df_to_plot_reg_2$timepoint==1, ], 
              aes(x=age, y=y_pred, label=paste0(subID)),check_overlap = F, size= 3) +
      # TRUE VALUES
      geom_line(aes(x=age, y=y_true, group= subID, color= "y_true"), alpha=0.4)+
      geom_point(aes(x=age, y=y_true, group= subID, color="y_true"), alpha=0.4)+
      geom_text(data = df_to_plot_reg_2[df_to_plot_reg_2$timepoint==1, ], 
          aes(x=age, y=y_true, label=paste0(subID)), check_overlap = F, size= 3) +
      ggtitle(reg2_name)+
      ylim(ylim.min, ylim.max) +
      labs(color = "Partition\n") +
      theme(panel.grid.major = element_blank(),
            panel.grid.minor = element_blank(),
            panel.background = element_blank(),
            axis.line    = element_line(colour = "black"),
            plot.title   = element_text(hjust = 0.5),
            axis.title.x = element_blank(),
            axis.title.y = element_blank()) +
      scale_colour_manual(name = " ",
                          values = c("y_pred"="red", "y_true"="blue"),
                          labels = c("Predicted values", "Target values"))
      
  figure <- ggarrange(reg1, reg2,
                      ncol = 2, nrow = 1,
                      legend = "right",
                      common.legend = TRUE)
  
  annotate_figure(figure,
                  left = text_grob("Cortical thickness (mm)",
                                   rot = 90),
                  bottom = text_grob("Age (years)"),
                  fig.lab.face = "bold",
                  top = text_grob("Target vs Predicted data\n", 
                                  face = "bold", size = 15, color = "black"))
}
```

```{r echo=FALSE}
plot_scatterplot_pred_target_1reg(df, predictions_308M, measure, reg, folds)
plot_scatterplot_pred_target_2reg(df, predictions_308M, measure, regs, f)
```


## Difference between target data vs predicted data 


```{r echo=FALSE}
plot_scatterplot_pred_target_diff_1reg <- function(df_orig, df_predictions, measure, reg, folds) {
  
  # DF_PREDICTIONS (Change region names) 
  # rh_precentral_CT_freesurfer -> rh_precentral
  reg_names <- df_predictions$region
  new_reg_names <- sub(measure, "",reg_names) # REG NAMES ONLY # Delete termination to get a cleaner name
  df_predictions$region <- new_reg_names # Rename all the columns

  # DF_ORIGIN (Change region names) 
  reg_names <- colnames(df_orig%>%dplyr::select(ends_with(measure))) # Get the names of all the regions
  reg_names <- sub(measure, "",reg_names) # REG NAMES ONLY # Delete termination to get a cleaner name
  region_short <- reg_names[reg]
  new.colnames <- sub(measure, "", colnames(df_orig)) # ALL COLNAMES # Delete termination to get a cleaner name
  colnames(df_orig) <- new.colnames # Rename all the columns
  
  # We separate data from healthy subjects and patients:
  df_hc  <- df_orig[df_orig[,"dcode"]==0, ] 
  df_pat <- df_orig[df_orig[,"dcode"]==1, ] 
  
  # We get the unique identifiers of healthy subjects and patients:
  ids_hc  <- unique(df_hc$subID)
  ids_pat <- unique(df_pat$subID)
  
  # we create 10 folds with the IDs:
  num_folds <- 10
  set.seed(123) # seed for replicability
  folds_hc <- createFolds(ids_hc, k=num_folds, list=TRUE, returnTrain=TRUE)
  set.seed(123) # seed for replicability
  folds_pat <- createFolds(ids_pat, k=num_folds, list=TRUE, returnTrain=TRUE)
  
  # DF_ORIG
  var_names <- c("age", "scode", "subID", "euler", "timepoint", "dcode")
  reg_name <- reg_names[reg]
  df_orig <- df_orig[ , c(reg_name, var_names)] # df_orig with only relevant data
  # ONLY HEALTHY CONTROLS
  df_orig$dcode <- factor(df_orig$dcode)
  df_orig  <- subset(df_orig, dcode==0) 

  # FIRST FOLD (fold 6th)
  f <- folds[1]
  # We get the subID of the train-test healthy subjects and controls in this fold f
  train_ids_hc <- ids_hc[folds_hc[[f]]]
  test_ids_hc  <- ids_hc[-folds_hc[[f]]]
  train_ids_pat <- ids_pat[folds_pat[[f]]]
  test_ids_pat  <- ids_pat[-folds_pat[[f]]]
  
  # SEPARATE TRAIN AND TEST HEALTHY CONTROLS DATA FROM FOLD F
  df_orig_test  <- subset(df_orig, subID%in%test_ids_hc)
  df_orig_test$partition  <- "test"
  
  # DF_PREDICTIONS
  df_predictions_plot  <- subset(df_predictions, fold==f) 
  df_predictions_plot  <- subset(df_predictions_plot, region==reg_name) 
  df_predictions_test <- subset(df_predictions_plot, subID%in%test_ids_hc)
  df_predictions_test <- df_predictions_test %>%
    select("region", "subID", "timepoint", "y_true", "y_pred")
  
  df_predictions_test <- reshape(df_predictions_test, 
                               idvar = c("subID", "timepoint"), 
                               timevar = "region", direction = "wide")

  df_merged <- merge(df_orig_test, df_predictions_test, by=c("subID","timepoint"))
  df_merged <- df_merged %>%
    select("age","subID","timepoint",paste0("y_true.", reg_name), 
           paste0("y_pred.", reg_name))
  
  df_to_plot <- df_merged %>%
    select("age","subID","timepoint", 
           paste0("y_true.", reg_name), 
           paste0("y_pred.", reg_name)) %>%
    dplyr::arrange(subID)

  colnames(df_to_plot) <- c("age","subID","timepoint","y_true","y_pred")
  df_to_plot <- df_to_plot %>%
    mutate(diff=abs(y_true-y_pred))

  # GRAPHICS
  fold1 <- ggplot(df_to_plot) +
      ggtitle(paste0("FOLD ",f))+
      # PREDICTIONS
      geom_line(aes(x=age, y=diff, group= subID), alpha=0.4)+
      geom_point(aes(x=age, y=diff, group= subID), alpha=0.4)+
      geom_text(data = df_to_plot[df_to_plot$timepoint==1, ], 
              aes(x=age, y=diff, label=paste0(subID)), check_overlap = F, size= 3) +
      ylim(0, 0.4) +
      labs(x = "Age (years)",
           y = "Cortical thickness (mm)") +
      theme(panel.grid.major = element_blank(),
            panel.grid.minor = element_blank(),
            panel.background = element_blank(),
            axis.title.x = element_blank(),
            axis.title.y = element_blank(),
            axis.line    = element_line(colour = "black"),
            plot.title   = element_text(hjust = 0.5)) +
      scale_colour_manual(name = " ",
                          values = c("y_pred"="red", "y_true"="blue"),
                          labels = c("Predicted values", "Target values"))
  
  # SECOND FOLD (fold 7th)
  f <- folds[2]
  # We get the subID of the train-test healthy subjects and controls in this fold f
  train_ids_hc <- ids_hc[folds_hc[[f]]]
  test_ids_hc  <- ids_hc[-folds_hc[[f]]]
  train_ids_pat <- ids_pat[folds_pat[[f]]]
  test_ids_pat  <- ids_pat[-folds_pat[[f]]]
  
  # SEPARATE TRAIN AND TEST HEALTHY CONTROLS DATA FROM FOLD F
  df_orig_test  <- subset(df_orig, subID%in%test_ids_hc)
  df_orig_test$partition  <- "test"
  
  # DF_PREDICTIONS
  df_predictions_plot  <- subset(df_predictions, fold==f) 
  df_predictions_plot  <- subset(df_predictions_plot, region==reg_name) 
  df_predictions_test <- subset(df_predictions_plot, subID%in%test_ids_hc)
  df_predictions_test <- df_predictions_test %>%
    select("region", "subID", "timepoint", "y_true", "y_pred")
  
  df_predictions_test <- reshape(df_predictions_test, 
                               idvar = c("subID", "timepoint"), 
                               timevar = "region", direction = "wide")

  df_merged <- merge(df_orig_test, df_predictions_test, by=c("subID","timepoint"))
  df_merged <- df_merged %>%
    select("age","subID","timepoint",paste0("y_true.", reg_name), 
           paste0("y_pred.", reg_name))
  
  df_to_plot <- df_merged %>%
    select("age","subID","timepoint", 
           paste0("y_true.", reg_name), 
           paste0("y_pred.", reg_name)) %>%
    dplyr::arrange(subID)

  colnames(df_to_plot) <- c("age","subID","timepoint","y_true","y_pred")
  df_to_plot <- df_to_plot %>%
    mutate(diff=abs(y_true-y_pred))

  # GRAPHICS
  fold2 <- ggplot(df_to_plot) +
      ggtitle(paste0("FOLD ",f))+
      # PREDICTIONS
      geom_line(aes(x=age, y=diff, group= subID), alpha=0.4)+
      geom_point(aes(x=age, y=diff, group= subID), alpha=0.4)+
      geom_text(data = df_to_plot[df_to_plot$timepoint==1, ], 
              aes(x=age, y=diff, label=paste0(subID)), check_overlap = F, size= 3) +
      ylim(0, 0.4) +
      labs(x = "Age (years)",
           y = "Cortical thickness (mm)") +
      theme(panel.grid.major = element_blank(),
            panel.grid.minor = element_blank(),
            panel.background = element_blank(),
            axis.title.x = element_blank(),
            axis.title.y = element_blank(),
            axis.line    = element_line(colour = "black"),
            plot.title   = element_text(hjust = 0.5)) +
      scale_colour_manual(name = " ",
                          values = c("y_pred"="red", "y_true"="blue"),
                          labels = c("Predicted values", "Target values"))
  
  # THIRD FOLD (fold 8th)
  f <- folds[3]
  # We get the subID of the train-test healthy subjects and controls in this fold f
  train_ids_hc <- ids_hc[folds_hc[[f]]]
  test_ids_hc  <- ids_hc[-folds_hc[[f]]]
  train_ids_pat <- ids_pat[folds_pat[[f]]]
  test_ids_pat  <- ids_pat[-folds_pat[[f]]]
  
  # SEPARATE TRAIN AND TEST HEALTHY CONTROLS DATA FROM FOLD F
  df_orig_test  <- subset(df_orig, subID%in%test_ids_hc)
  df_orig_test$partition  <- "test"
  
  # DF_PREDICTIONS
  df_predictions_plot  <- subset(df_predictions, fold==f) 
  df_predictions_plot  <- subset(df_predictions_plot, region==reg_name) 
  df_predictions_test <- subset(df_predictions_plot, subID%in%test_ids_hc)
  df_predictions_test <- df_predictions_test %>%
    select("region", "subID", "timepoint", "y_true", "y_pred")
  
  df_predictions_test <- reshape(df_predictions_test, 
                               idvar = c("subID", "timepoint"), 
                               timevar = "region", direction = "wide")

  df_merged <- merge(df_orig_test, df_predictions_test, by=c("subID","timepoint"))
  df_merged <- df_merged %>%
    select("age","subID","timepoint",paste0("y_true.", reg_name), 
           paste0("y_pred.", reg_name))
  
  df_to_plot <- df_merged %>%
    select("age","subID","timepoint", 
           paste0("y_true.", reg_name), 
           paste0("y_pred.", reg_name)) %>%
    dplyr::arrange(subID)

  colnames(df_to_plot) <- c("age","subID","timepoint","y_true","y_pred")
  df_to_plot <- df_to_plot %>%
    mutate(diff=abs(y_true-y_pred))

  # GRAPHICS
  fold3 <- ggplot(df_to_plot) +
      ggtitle(paste0("FOLD ",f))+
      # PREDICTIONS
      geom_line(aes(x=age, y=diff, group= subID), alpha=0.4)+
      geom_point(aes(x=age, y=diff, group= subID), alpha=0.4)+
      geom_text(data = df_to_plot[df_to_plot$timepoint==1, ], 
              aes(x=age, y=diff, label=paste0(subID)), check_overlap = F, size= 3) +
      ylim(0, 0.4) +
      labs(x = "Age (years)",
           y = "Cortical thickness (mm)") +
      theme(panel.grid.major = element_blank(),
            panel.grid.minor = element_blank(),
            panel.background = element_blank(),
            axis.title.x = element_blank(),
            axis.title.y = element_blank(),
            axis.line    = element_line(colour = "black"),
            plot.title   = element_text(hjust = 0.5)) +
      scale_colour_manual(name = " ",
                          values = c("y_pred"="red", "y_true"="blue"),
                          labels = c("Predicted values", "Target values"))

  figure <- ggarrange(fold1, fold2, fold3,
                      ncol = 3, nrow = 1,
                      legend = "right",
                      common.legend = TRUE)
  
  annotate_figure(figure,
                  left = text_grob("Cortical thickness (mm)",
                                   rot = 90),
                  bottom = text_grob("Age (years)"),
                  fig.lab.face = "bold",
                  top = text_grob(paste0("Difference between target and predicted data (",
                                         region_short,")"), 
                                  face = "bold", size = 15, color = "black"))
}
```


```{r echo=FALSE}
plot_scatterplot_pred_target_diff_2reg <- function(df_orig, df_predictions, measure, regs, f) {
  
  # DF_PREDICTIONS Change region names rh_temporalpole_CT_freesurfer -> rh_temporalpole
  reg_names <- df_predictions$region
  new_reg_names <- sub(measure, "",reg_names) # REG NAMES ONLY # Delete termination to get a cleaner name
  df_predictions$region <- new_reg_names # Rename all the columns

  # DF_ORIGIN Change region names rh_temporalpole_CT_freesurfer -> rh_temporalpole
  reg_names <- colnames(df_orig%>%dplyr::select(ends_with(measure))) # Get the names of all the regions
  reg_names <- sub(measure, "",reg_names) # REG NAMES ONLY # Delete termination to get a cleaner name
  new.colnames <- sub(measure, "", colnames(df_orig)) # ALL COLNAMES # Delete termination to get a cleaner name
  colnames(df_orig) <- new.colnames # Rename all the columns
  
  # We separate data from healthy subjects and patients:
  df_hc  <- df_orig[df_orig[,"dcode"]==0, ] 
  df_pat <- df_orig[df_orig[,"dcode"]==1, ] 
  
  # We get the unique identifiers of healthy subjects and patients:
  ids_hc  <- unique(df_hc$subID)
  ids_pat <- unique(df_pat$subID)
  
  # we create 10 folds with the IDs:
  num_folds <- 10
  set.seed(123) # seed for replicability
  folds_hc <- createFolds(ids_hc, k=num_folds, list=TRUE, returnTrain=TRUE)
  set.seed(123) # seed for replicability
  folds_pat <- createFolds(ids_pat, k=num_folds, list=TRUE, returnTrain=TRUE)
  
  # We get the subID of the train-test healthy subjects and controls in this fold f
  train_ids_hc <- ids_hc[folds_hc[[f]]]
  test_ids_hc  <- ids_hc[-folds_hc[[f]]]
  train_ids_pat <- ids_pat[folds_pat[[f]]]
  test_ids_pat  <- ids_pat[-folds_pat[[f]]]
  
  ##### UNTIL HERE CROSS-VAL SUBJECTS IDENTIFICATION #####

  # DF_ORIG
  var_names <- c("age", "scode", "subID", "euler", "timepoint", "dcode")
  reg_names <- reg_names[regs]
  df_orig <- df_orig[ , c(reg_names, var_names)] # df_orig with only relevant data
  # ONLY HEALTHY CONTROLS
  df_orig$dcode <- factor(df_orig$dcode)
  df_orig  <- subset(df_orig, dcode==0) 
  # SEPARATE TRAIN AND TEST HEALTHY CONTROLS DATA FROM FOLD F
  df_orig_test  <- subset(df_orig, subID%in%test_ids_hc)
  df_orig_test$partition  <- "test"
  
  
  # DF_PREDICTIONS
  df_predictions   <- subset(df_predictions, fold==f) 
  df_predictions1  <- subset(df_predictions, region==reg_names[1]) 
  df_predictions2  <- subset(df_predictions, region==reg_names[2]) 
  df_predictions_m <- rbind(df_predictions1, df_predictions2)
  df_predictions_test <- subset(df_predictions_m, subID%in%test_ids_hc)
  df_predictions_test <- df_predictions_test %>%
    select("region", "subID", "timepoint", "y_true", "y_pred")
  
  df_predictions_test <- reshape(df_predictions_test, 
                                 idvar = c("subID", "timepoint"), 
                                 timevar = "region", direction = "wide")

  df_merged <- merge(df_orig_test, df_predictions_test, by=c("subID","timepoint"))
  df_merged <- df_merged %>%
    select("age","subID","timepoint","y_true.rh_postcentral_part1", 
           "y_pred.rh_postcentral_part1", "y_true.rh_postcentral_part2", 
           "y_pred.rh_postcentral_part2")
  
  df_to_plot_reg_1 <- df_merged %>%
    select("age","subID","timepoint",
           "y_true.rh_postcentral_part1",
           "y_pred.rh_postcentral_part1") %>%
    dplyr::arrange(subID)
  
  reg1_name <- sub("y_pred.", "",colnames(df_to_plot_reg_1)[5]) # Get region name
  colnames(df_to_plot_reg_1) <- c("age","subID","timepoint","y_true","y_pred")
  
  df_to_plot_reg_2 <- df_merged %>%
  select("age","subID","timepoint", 
           "y_true.rh_postcentral_part2",
           "y_pred.rh_postcentral_part2") %>%
    dplyr::arrange(subID)
  
  reg2_name <- sub("y_pred.", "",colnames(df_to_plot_reg_2)[5]) # Get region name
  colnames(df_to_plot_reg_2) <- c("age","subID","timepoint","y_true","y_pred")

  df_to_plot_reg_1 <- df_to_plot_reg_1 %>%
    mutate(diff=abs(y_true-y_pred))
  
  df_to_plot_reg_2 <- df_to_plot_reg_2 %>%
    mutate(diff=abs(y_true-y_pred))

  # GRAPHICS
  reg1 <- ggplot(df_to_plot_reg_1) +
      # PREDICTIONS
      geom_line(aes(x=age, y=diff, group= subID), alpha=0.4)+
      geom_point(aes(x=age, y=diff, group= subID), alpha=0.4)+
      geom_text(data = df_to_plot_reg_1[df_to_plot_reg_1$timepoint==1, ], 
              aes(x=age, y=diff, label=paste0(subID)), check_overlap = F, size= 3) +
      ggtitle(reg1_name)+
      ylim(0, 0.4) +
      theme(panel.grid.major = element_blank(),
            panel.grid.minor = element_blank(),
            panel.background = element_blank(),
            axis.line    = element_line(colour = "black"),
            plot.title   = element_text(hjust = 0.5),
            axis.title.x = element_blank(),
            axis.title.y = element_blank())
  reg2 <- ggplot(df_to_plot_reg_2) +
      # PREDICTIONS
      geom_line(aes(x=age, y=diff, group= subID), alpha=0.4)+
      geom_point(aes(x=age, y=diff, group= subID), alpha=0.4)+
      geom_text(data = df_to_plot_reg_2[df_to_plot_reg_2$timepoint==1, ], 
              aes(x=age, y=diff, label=paste0(subID)),check_overlap = F, size= 3) +
      ggtitle(reg2_name)+
      ylim(0, 0.4) +
      labs(color = "Partition\n") +
      theme(panel.grid.major = element_blank(),
            panel.grid.minor = element_blank(),
            panel.background = element_blank(),
            axis.line    = element_line(colour = "black"),
            plot.title   = element_text(hjust = 0.5),
            axis.title.x = element_blank(),
            axis.title.y = element_blank())
      
  figure <- ggarrange(reg1, reg2,
                      ncol = 2, nrow = 1,
                      legend = "right",
                      common.legend = TRUE)
  
  annotate_figure(figure,
                  left = text_grob("Cortical thickness (mm)",
                                   rot = 90),
                  bottom = text_grob("Age (years)"),
                  fig.lab.face = "bold",
                  top = text_grob("Difference between target and predicted data\n", 
                                  face = "bold", size = 15, color = "black"))
}
```

```{r echo=FALSE}
plot_scatterplot_pred_target_diff_1reg(df, predictions_308M, measure, reg, folds)
plot_scatterplot_pred_target_diff_2reg(df, predictions_308M, measure, regs, f)
```


```{r eval=FALSE, include=FALSE}
# Tabla presentación SIRS: SMSE, SMAE, R2. Mean performance of the models
performance_68NoM  <- read.csv("/data_J/Results/Files/performance_68NoM.csv" )
table_performance_68NoM <- performance_68NoM %>%
  # dplyr::group_by(diagnose)%>%
  dplyr::summarise(SMSEm=round(mean(SMSE),2),
                   SMSEs=round(sd(SMSE),2),
                   SMAEm=round(mean(SMAE),2),
                   SMAEs=round(sd(SMAE),2),
                   R2m=round(mean(R2),2),
                   R2s=round(sd(R2),2))
```




